---
title: "RAVE Data Tools"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
ravepipeline::pipeline_setup_rmd("compatibility_rave1")
```


```{rave load_subject_instance, language = "R", export = "subject"}
# Use strict=FALSE in case the subject is invalid
subject <- raveio::RAVESubject$new(
  project_name = project_name,
  subject_code = subject_code,
  strict = FALSE)
```



## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-compatibility_rave1.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-compatibility_rave1.R")
```


Once the pipeline script `make-compatibility_rave1.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
Sys.setenv("RAVE_PIPELINE" = normalizePath("."))
try({
  ravepipeline::pipeline_visualize()
}, silent = TRUE)
```







