---
title: "RAVE Pipeline - Reference"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
ravepipeline::pipeline_setup_rmd("reference_module")
options("raveio.debug" = TRUE)
```



```{rave load_subject, language = "R", export = "subject", cue = "always", format = "rave-subject"}
subject <- raveio::RAVESubject$new(
  project_name = project_name, 
  subject_code = subject_code
)
if(!all(subject$preprocess_settings$notch_filtered)) {
  stop("Please run Notch filter module first.")
}
```

```{rave obtain_previous_preprocessing, export = "preprocessing_history", cue = "always"}
# try to get previous reference pipeline
previous_pipeline_path <- file.path(subject$pipeline_path, "reference_module")
previous_data <- NULL
if(dir.exists(previous_pipeline_path)) {
  try(silent = TRUE, {
    previous_pipeline <- ravepipeline::pipeline(pipeline_name = "reference_module", paths = subject$pipeline_path, temporary = TRUE)
    previous_data <- previous_pipeline$read("preprocessing_history")
    if(is.list(previous_data)) {
      previous_data <- previous_data$current
    }
  })
}
current <- list(
  notch_filtered = subject$notch_filtered,
  notch_params = subject$preprocess_settings$notch_params,
  has_wavelet = subject$has_wavelet,
  wavelet_params = subject$preprocess_settings$wavelet_params
)
use_cache <- TRUE
if(length(previous_data) != length(current)) {
  use_cache <- FALSE
} else {
  for(nm in names(current)) {
    a <- previous_data[[nm]]
    b <- current[[nm]]
    a <- unlist(a)
    b <- unlist(b)
    if(length(a) != length(b)) {
      use_cache <- FALSE
      break
    }
    tryCatch({
      if(length(a) > 0 && any(a != b)) {
        use_cache <- FALSE
      }
    }, error = function(e) {
      use_cache <<- FALSE
    })
    if(!use_cache) { break }
  }
}

preprocessing_history <- list(
  current = current,
  previous = previous_data,
  use_cache = use_cache
)
```

Loads preset reference table, and generate a reference file called `_unsaved`. The reference table will be saved to this file before exported.

```{rave load_presets, language = "R", export = "reference_table_initial", cue = "always"}
if(isTRUE(reference_name %in% subject$reference_names)) {
  tryCatch({
    reference_table_initial <- subject$get_reference(reference_name, simplify = FALSE)
    
    reference_table_initial <- reference_table_initial[,c(
      "Electrode", "Group", "Reference", "Type"
    )]
    
  }, error = function(e){
    
    # log
    ravedash::logger("Unable to load reference [", reference_name, "]", level = "error")
    ravedash::logger_error_condition(e)
    stop("Unable to load reference [", reference_name, "]. Please check your reference file or simply start with a blank reference profile.")
  })
  
} else {
  # get electrode file
  electrode_table <- subject$get_electrode_table(reference_name = reference_name)
  
  # group by Label prefix
  str_electrode_group <- gsub("[0-9]+$", "", electrode_table$Label)
  electrode_table$Group <- trimws(str_electrode_group)
  
  if(!"LocationType" %in% names(electrode_table)) {
    electrode_table$LocationType <- "iEEG"
  } else {
    electrode_table$LocationType[!electrode_table$LocationType %in% raveio::LOCATION_TYPES] <- "iEEG"
  }
  if(length(subject$electrode_types) == nrow(electrode_table)) {
    electrode_table$SignalType <- subject$electrode_types
  } else if(!"SignalType" %in% names(electrode_table)) {
    electrode_table$SignalType <- "LFP"
  } else {
    electrode_table$SignalType[!electrode_table$SignalType %in% raveio::SIGNAL_TYPES] <- "LFP"
  }
  
  splits <- split(electrode_table, electrode_table$Group)
  
  
  subs <- lapply(splits, function(sub) {
    ltype <- sub$LocationType
    refs <- rep("noref", nrow(sub))
    ref_type <- rep("No Reference", nrow(sub))
    seeg <- which(ltype == 'sEEG')
    if(length(seeg) >= 2) {
      last_idx <- seeg[[length(seeg)]]
      refs[seeg[-length(seeg)]] <- sprintf("ref_%d", sub$Electrode[seeg[-1]])
      ref_type[seeg[-length(seeg)]] <- "Bipolar Reference"
      refs[[last_idx]] <- "noref"
      sub$Group[[last_idx]] <- "Bipolar-last-electrode"
    }
    sub$Reference <- refs
    sub$Type <- ref_type
    sub[, c("Electrode", "Group", "Reference", "Type")]
  })
  reference_table_initial <- do.call("rbind", unname(subs))
  
  # reference_table_initial <- data.frame(
  #   Electrode = subject$electrodes,
  #   Group = "Default",
  #   Reference = "noref",
  #   Type = "No Reference"
  # )
}
# save to subject's meta folder with reference name "_unsaved"
unsaved_meta <- file.path(subject$meta_path, "reference__unsaved.csv")
utils::write.csv(reference_table_initial, unsaved_meta)

```

```{rave load_voltage_data, language = "R", export = "voltage_data", cue = "always"}
# need to 

electrodes <- subject$electrodes
is_lfp <- subject$electrode_types %in% "LFP"
lfp_channels <- electrodes[is_lfp]

if(!length(lfp_channels)) {
  stop("There is no LFP/macro channel for this subject")
}

blocks <- subject$blocks
use_cache <- preprocessing_history$use_cache
has_wavelet <- all(preprocessing_history$current$has_wavelet[is_lfp])

cache_root <- file.path(subject$cache_path, "rave2", "voltage")
raveio::dir_create2(cache_root)

notch_params <- subject$preprocess_settings$notch_params

first_e <- electrodes[is_lfp][[1]]
first_inst <- raveio::new_electrode(subject = subject, 
                                    number = first_e)

progress <- dipsaus::progress2("Check cache data", max = length(blocks), shiny_auto_close = TRUE)

voltage_signals <- structure(
  names = blocks,
  lapply(blocks, function(block) {
    
    # block <- blocks[[1]]
    
    progress$inc(sprintf("%s", block))
    
    if( has_wavelet ) {
      sample_signal <- raveio::load_h5(first_inst$voltage_file, name = sprintf("/raw/voltage/%s", block), ram = FALSE)
    } else {
      sample_signal <- raveio::load_h5(first_inst$preprocess_file, name = sprintf("/notch/%s", block), ram = FALSE)
    }
    
    
    signal_length <- length(sample_signal)
    
    block_path <- file.path(cache_root, block)
    exists <- TRUE
    
    arr <- tryCatch({
      if( !use_cache ) { stop("Do not use cache") }
      filearray::filearray_checkload(
        filebase = block_path,
        mode = "readwrite", 
        symlink_ok = FALSE, 
        subject_id = subject$subject_id,
        blocks = blocks,
        electrodes = electrodes,
        electrode_is_lfp = is_lfp,
        notch_params = notch_params,
        sample_rates = subject$raw_sample_rates,
        signal_length = as.integer(signal_length),
        staged = TRUE
      )
    }, error = function(e){
      unlink(block_path, recursive = TRUE)
      arr <- filearray::filearray_create(
        filebase = block_path, 
        dimension = c(signal_length, sum(is_lfp)), 
        type = "double", partition_size = 1L
      )
      arr$.header$subject_id <- subject$subject_id
      arr$.header$blocks <- blocks
      arr$.header$electrodes <- electrodes
      arr$.header$electrode_is_lfp <- is_lfp
      arr$.header$notch_params <- notch_params
      arr$.header$sample_rates <- subject$raw_sample_rates
      arr$.header$signal_length <- as.integer(signal_length)
      dimnames(arr) <- list(NULL, Electrode = lfp_channels)
      arr$.save_header()
      exists <<- FALSE
      arr
    })
    
    list(
      exists = exists,
      array = arr
    )
    
  })
)

exists <- vapply(voltage_signals, '[[', FALSE, "exists")
missing_blocks <- blocks[!exists]

subject_id <- subject$subject_id


if(length(missing_blocks)) {
  
  raveio::lapply_async(seq_along(lfp_channels), function(ii){
    e <- lfp_channels[[ii]]
    inst <- raveio::new_electrode(subject = subject_id, number = e)
    if( has_wavelet ) {
      voltage_file <- inst$voltage_file
      for(block in missing_blocks) {
        s <- raveio::load_h5(voltage_file, sprintf("/raw/voltage/%s", block), ram = TRUE)
        voltage_signals[[block]]$array[, ii] <- s
      }
    } else {
      voltage_file <- inst$preprocess_file
      for(block in missing_blocks) {
        s <- raveio::load_h5(voltage_file, sprintf("/notch/%s", block), ram = TRUE)
        voltage_signals[[block]]$array[, ii] <- s
      }
    }
    return()
  }, callback = function(ii){
    sprintf("Creating cache|Electrode %s", electrodes[[ii]])
  })
  
}

voltage_data <- list(
  data = structure(lapply(voltage_signals, function(item){
    if(!item$exists) {
      item$array$set_header("staged", TRUE)
    }
    item$array$.mode <- "readonly"
    item$array
  }), names = blocks),
  electrodes = lfp_channels
)

# save pipeline
if( !isTRUE(getOption("raveio.debug", FALSE)) ) {
  previous_pipeline_path <- file.path(subject$pipeline_path, "reference_module")
  ravepipeline::pipeline_fork(
    dest = previous_pipeline_path, 
    activate = FALSE
  )
}
voltage_data
```


```{rave validate_electrode_groups, language = "R", export = "reference_group"}

ngroups <- length(electrode_group)

group_names <- ""
electrodes <- NULL

reference_group <- reference_table_initial
reference_group$GroupID <- 0

lfp_channels <- subject$electrodes[subject$electrode_types %in% c("LFP")]

not_lfp <- !reference_group$Electrode %in% lfp_channels
if(any(not_lfp)) {
  electrodes <- reference_group$Electrode[not_lfp]
  reference_group$Group[not_lfp] <- ""
  reference_group$Reference[not_lfp] <- ""
  reference_group$Type[not_lfp] <- "No Reference"
}


id <- 1
for(x in electrode_group) {
  e <- dipsaus::parse_svec(x$electrodes)
  if(length(e)){
    e <- unique(e)
    if(length(x$name) != 1 || !is.character(x$name)) {
      stop("Each electrode group must have a unique name")
    }
    
    x$name <- trimws(x$name)
    
    if(x$name %in% group_names) {
      stop("Electrode groups must have unique names (violation: ", x$name, ")")
    }
    group_names <- c(group_names, x$name)
    
    emissing <- e[!e %in% lfp_channels]
    if(length(emissing)) {
      stop("Channel ", dipsaus::deparse_svec(emissing), " are not declared/imported or LFP channels (e.g. microwires, auxiliary, ...). Please remove from group [", x$name, "]")
    }
    
    edup <- e[e %in% electrodes]
    if(length(edup)) {
      stop("Electrodes ", dipsaus::deparse_svec(edup), " appear in multiple groups. Please fix this issue by ensuring that each of channel only appears in one group at a time.")
    }
    electrodes <- c(electrodes, e)
    
    sel <- reference_group$Electrode %in% e
    reference_group$Group[sel] <- x$name
    reference_group$GroupID[sel] <- id
    
  }
  id <- id + 1
}

head(reference_group)


```

```{rave validate_and_apply_changes, language = "R", export = "reference_updated", cue = "always"}
reference_choices <- c(
  "No Reference", "Common Average Reference",
  "White-matter Reference", "Bipolar Reference"
)

for(item in changes) {
  
  evec <- dipsaus::parse_svec(item$electrodes)
  sel <- reference_group$Electrode %in% evec
    
  
  if(!any(sel)) { next }
  if(length(item$reference_type) != 1) {
    stop("Reference type is missing for electrode ", dipsaus::deparse_svec(evec))
  }
  
  reference_group$Type[sel] <- item$reference_type
  if(item$reference_type == reference_choices[[1]]) {
    reference_group$Reference[sel] <- "noref"
  } else if(
    item$reference_type %in% reference_choices[c(2,3)]
  ) {
    if(length(item$reference_signal) != 1) {
      stop("Reference signal must be the same within the group if the group reference type is common average or white-matter reference")
    }
    reference_group$Reference[sel] <- item$reference_signal
  } else if(item$reference_type == reference_choices[[4]]) {
    
    if(length(item$reference_signal) != sum(sel)) {
      stop("For Bipolar reference, `reference_signal` must have the same size as the number of electrodes")
    }
    reference_group$Reference[sel] <- item$reference_signal
  }
  
}

reference_updated <- reference_group
unsaved_meta <- file.path(subject$meta_path, "reference__unsaved.csv")
utils::write.csv(reference_updated, unsaved_meta)

```

## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-reference_module.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-reference_module.R")
```


Once the pipeline script `make-reference_module.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
Sys.setenv("RAVE_PIPELINE" = normalizePath("."))
ravepipeline::pipeline_visualize()
```

