---
title: "RAVE Pipeline Markdown Template"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
raveio::pipeline_setup_rmd("fooof_module")
rpymat::ensure_rpymat()
```

<!-- Begin: pipeline code -->

Generate some random data

```{python generate_input_data, use_rave = TRUE, deps = c("sample_size", "random_generator"), export = "input_data"}
# sample size as integer
sample_size = int(sample_size)

if sample_size <= 0:
  raise Exception(f"Sample size should be positive")

# get random number generator
if random_generator == "randn":
  generator = np.random.randn
elif random_generator == "randint":
  generator = np.random.randint
elif random_generator == "rand":
  generator = np.random.rand
else:
  raise Exception(f"Unknown random number generator { generator_name }")


log_info(f"Generating sample data with function np.random.{ random_generator } and sample size {sample_size}")

input_data = {
  'x' : generator(sample_size),
  'y' : generator(sample_size)
}
```

Calculate the correlation coefficients

```{python calculate_correlation, use_rave = TRUE, deps = "input_data", export = "correlation"}
correlation = np.corrcoef(input_data['x'], input_data['y'])
log_info(f"Calculating correlation: { correlation }")
```

<!-- End: pipeline code -->

## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-fooof_module.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-fooof_module.R")
```


Once the pipeline script `make-fooof_module.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
# Fixed usage, show pipeline graph
try({
  asNamespace("raveio")$pipeline_dependency_graph(
    pipeline_path = ".", glimpse = TRUE)
}, silent = TRUE)
```







