---
title: "RAVE Custom 3D Viewer (Native Brain)"
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
format:
  html: 
    max-width: "1600px"
    width: 1500
    page-layout: full
    embed-resources: true
---

```{r setup, include = FALSE}
# Default for RAVE pipeline 2.0. Please do NOT remove this chunk
ravepipeline::pipeline_setup_rmd(module_id = "custom_3d_viewer")
set.seed(100)
```

## 1. Pre-requisites

Loading a RAVE 3D brain on a native single patient requires 3 types of data:

1.  (Mandatory) `FreeSurfer` reconstruction: please copy and rename the folder to `<rave_dir>/raw_dir/<subject>/rave-imaging/fs`
2.  (Mandatory for iEEG cases) Electrode coordinates in `tkrRAS` coordinate space. If you use RAVE electrode localization, this file will be automatically loaded. For more details on how to transform from scanner-RAS or MNI coordinates to `tkrRAS`, please see [this documentation](https://surfer.nmr.mgh.harvard.edu/fswiki/CoordinateSystems), or [Github issue](https://github.com/dipterix/threeBrain/issues/32).
3.  (Optional) Electrode value table in `CSV` format.

The electrode table should look like this:

```{r, echo=FALSE, results='asis'}
knitr::kable(data.frame(
  Electrode = 1:5,
  Coord_x = rnorm(5, sd = 20),
  Coord_y = rnorm(5, sd = 20),
  Coord_z = rnorm(5, sd = 20),
  Label = sprintf("G%s", 1:5)
), digits = 2)
```

## 1. Create a blank brain viewer

To generate 3D viewer, first you need to create a RAVE brain object, then you can simply use `plot` method:

-   Inputs: `project_name`, `subject_code`

-   Outputs: RAVE brain object `brain` and RAVE 3D viewer

``` {.r eval="FALSE"}
# Subject
subject <- sprintf("%s/%s", project_name, subject_code)

# Brain object
brain <- ravecore::rave_brain(subject)

# Generate 3D viewer
brain$plot()
```

```{rave get_valid_project_name, language = "R", export = "loaded_brain", cue = "always", collapse=FALSE}
#| code-fold: true
#| code-summary: "Show a complicated implementation"

loaded_brain <- load_brain_from_subject_code(
  subject_code = subject_code, 
  project_name = project_name,
  
  overlay_types = overlay_types,
  surface_types = surface_types,
  annot_types = annot_types,
  
  use_spheres = use_spheres,
  override_radius = override_radius,
  
  coordinate_sys = coordinate_sys,
  use_template = use_template
)
```

```{rave render_initial_viewer, language = "R", export = "initial_brain_widget", collapse=TRUE, cue = "always"}
#| code-fold: true
#| code-summary: "Show a complicated implementation"

force(shiny_outputId)
controllers <- as.list(controllers)
main_camera <- as.list(main_camera)

background <- controllers[["Background Color"]]
if(length(background) != 1) {
  background <- "#FFFFFF"
}

zoom_level <- main_camera$zoom
if(length(zoom_level) != 1 || zoom_level <= 0) {
  zoom_level <- 1
}

position <- as.numeric(unname(unlist(main_camera$position)))
up <- as.numeric(unname(unlist(main_camera$up)))
if(length(position) != 3 || length(up) != 3 ||
   all(position == 0) || all(up == 0) ||
   any(is.na(position)) || any(is.na(up))) {
  position <- c(0, 0, 500)
  up <- c(0, 1, 0)
} else {
  position <- position / sqrt(sum(position^2)) * 500
  up <- up / sqrt(sum(up^2))
}

if(!isTRUE(controllers[["Show Panels"]])) {
  controllers[["Show Panels"]] <- FALSE
}
    
initial_brain_widget <- loaded_brain$brain$plot(
  show_modal = FALSE,
  background = background,
  controllers = controllers,
  start_zoom = zoom_level,
  # send signals to update parameters such as camera, zoom-level...
  custom_javascript = glue::glue(
    '
    // Remove the focus box
    if( canvas.focus_box ) {
      canvas.focus_box.visible = false;
    }
    
    // set camera
    canvas.mainCamera.position.set(
      {{ position[[1]] }} , 
      {{ position[[2]] }} , 
      {{ position[[3]] }}
    );
    canvas.mainCamera.up.set(
      {{ up[[1]] }} , 
      {{ up[[2]] }} , 
      {{ up[[3]] }}
    )
    canvas.mainCamera.updateProjectionMatrix();

    // Let shiny know the viewer is ready
    if( window.Shiny ) {
      window.Shiny.setInputValue("{{ shiny_outputId }}", "{{Sys.time()}}");
    }

    // Force render one frame (update the canvas)
    canvas.needsUpdate = true;
    ',
    .open = "{{", .close = "}}"
  )
)

```

```{r, echo=FALSE, out.width="100%", out.height="500px"}
loaded_brain$brain$plot()
```

## 2. Render electrodes with values and colors

To assign the electrodes with values, you will need data table that looks like this:

```{r, echo=FALSE}
data.frame(
  Electrode = 1:5,
  PValue = runif(5),
  Value2 = letters[1:5]
)
```

The first column must be `Electrode`. The other column names will be the electrode value names. The electrode values can be numeric (continuous), or factors (categorical). If your data is time series, you can add an additional column `Time` (see data table example below).

To set electrode values, use

``` {.r eval="FALSE"}
brain$set_electrode_values(<your data frame, or path to the csv>)
```

In this RAVE module, users can load electrode value table from input choices:

-   `Uploads`: user uploads `csv/fst` table to the subject imaging folder. Under this mode, the input `uploaded_source` must be specified.

-   `Saved pipelines/modules`: get from previously saved pipeline (under construction); under this mode, the pipeline ID and inner target name must be specified

The detailed implementations are folded (too much coding)

```{rave find_data_path, language = "R", export = "path_datatable", cue = "always", collapse=TRUE}
#| code-fold: true
#| code-summary: "Show the implementation (how to find data path)"

if(!length(data_source)) { data_source <- "None" }
path_datatable <- switch(
  data_source,
  "Uploads" = {
    subject <- get_brain_subject(loaded_brain)
    get_subject_imaging_datapath(
      uploaded_source,
      subject_code = subject$subject_code,
      project_name = subject$project_name,
      type = "uploads"
    )
  }, 
  "Saved pipelines/modules" = {
    project_name <- data_source_project
    saved_pipeline <- data_source_pipeline
    saved_target <- data_source_pipeline_target
    
    if(!length(project_name)) {
      stop("Trying to get saved pipeline, but no project name has been given. Please assign a valid [data_source_project] variable. If you are running in RAVE's web interface, make sure the project name is set correctly")
    }
    if(!length(saved_pipeline) || !length(saved_target)) {
      stop("Trying to get saved pipeline, but no pipeline name nor target has been given. Please assign a valid [data_source_pipeline] & [data_source_pipeline_target] variable. If you are running in RAVE's web interface, make sure the pipeline is set with no errors.")
    }
    
    pipepath <- get_subject_imaging_datapath(
      saved_pipeline, subject_code = loaded_brain$subject_code,
      project_name = project_name, type = "pipeline"
    )
    if(!length(pipepath) || is.na(pipepath) || !dir.exists(pipepath)) {
      stop("Cannot find saved pipeline under the subject [",
           project_name, "/", loaded_brain$subject_code, "]: ",
           saved_pipeline)
    }
    
    structure(
      pipepath, 
      target = saved_target
    )
    
    # local({
    #   raveio:::activate_pipeline(pipepath)
    #   targets::tar_path(name = saved_target)
    # })
    
  },
  {
    NULL
  }
)
```

```{rave load_data_table, language = "R", export = "brain_with_data", cue = "always", collapse=TRUE}
#| code-fold: true
#| code-summary: "Load the data into brain"

loaded_datatable <- NULL

if(length(path_datatable) == 1) {
  if(!length(data_source) || is.na(path_datatable) || !file.exists(path_datatable)) {
    data_source <- "None"
  }
  switch(
    data_source,
    "Uploads" = {
      if(grepl("\\.fst$", path_datatable, ignore.case = TRUE)) {
        loaded_datatable <- ieegio::io_read_fst(path_datatable, method = "data_table")
      }
    },
    "Saved pipelines/modules" = {
      
      var <- ravepipeline::pipeline_read(
        var_names = attr(path_datatable, "target"),
        pipe_dir = path_datatable,
        ifnotfound = NULL
      )
      
      if(length(var)) {
        try({
          
          if("Electrode" %in% names(var)) {
            
            if(!is.data.frame(var)) {
              var <- as.data.frame(var)
            }
            loaded_datatable <- var
          }
          
        })
      }
      
    },
    {
      # none
      path_datatable <- NULL
    }
  )
}


nms <- names(loaded_datatable)

if(!"Electrode" %in% nms && length(path_datatable)) {
  if(isTRUE(data_source %in% c("Uploads", "Saved pipelines/modules"))) {
    stop("Cannot set electrode values. Please make sure the data is a named table, and one of the table names must be [Electrode] (case-sensitive).")
  }
} 
  

if(is.data.frame(loaded_datatable) && "Electrode" %in% nms) {
  
  if(!data.table::is.data.table(loaded_datatable)) {
    loaded_datatable <- data.table::as.data.table(loaded_datatable)
  }
  
  # subset if Subject is contained
  if("Subject" %in% nms) {
    template_subject <- ravepipeline::raveio_getopt("threeBrain_template_subject", default = "N27")
    
    if(!identical(loaded_brain$brain$subject_code, 
                  template_subject)) {
      loaded_datatable <- loaded_datatable[loaded_datatable$Subject %in% loaded_brain$brain$subject_code, ]
    }
  }
  
  if("Time" %in% names(loaded_datatable)) {
    
    # Need to make sure each time-component has only one value
    fct <- sprintf(
      "%.2f__%.0f", 
      loaded_datatable$Time,
      loaded_datatable$Electrode)
    
    # Remove names that don't name sense to collapse
    # Can't care less about others
    nms <- nms[!nms %in% c("Time", "Electrode", "Trial", "Frequency", "Block", "Subject")]
    
    coltypes <- sapply(nms, function(nm) {
      is.numeric(loaded_datatable[[nm]])
    }, simplify = FALSE, USE.NAMES = TRUE)
    
    
    new_table <- lapply(split(loaded_datatable, fct), function(sub) {
      sub <- as.data.frame(sub)
      if(nrow(sub) == 1) {
        return(sub[, c(nms, "Electrode", "Time"), drop = FALSE])
      }
      re <- sapply(nms, function(nm){
        v <- sub[[nm]]
        if(coltypes[[nm]]) {
          v <- v[!is.na(v)]
          if(!length(v)) { return(NA_real_) }
          return(mean(v))
        } else {
          v <- table(v)
          v <- v[!is.na(v)]
          if(!length(v)) { return(NA) }
          v <- names(v)[v == max(v)]
          if(length(v) > 1) { return(NA) }
          return(v)
        }
      }, simplify = FALSE, USE.NAMES = TRUE)
      re$Electrode <- sub$Electrode[[1]]
      re$Time <- sub$Time[[1]]
      as.data.frame(re)
    })
    
    loaded_datatable <- data.table::rbindlist(new_table, use.names = TRUE)
  }
  nms <- names(loaded_datatable)
  invalids <- vapply(nms, function(nm) {
    all(is.na(loaded_datatable[[nm]]))
  }, FALSE)
  nms <- nms[!invalids]
  # loaded_datatable <- loaded_datatable[, !invalids, with = FALSE]
  
  if(nrow(loaded_datatable)) {
    loaded_brain$brain$set_electrode_values(loaded_datatable)
  } else {
    nms <- NULL
  }
}
  
brain_with_data <- list(
  brain = loaded_brain$brain,
  variables = nms
)
```

Here is a preview of value table (max 1000 rows) if you choose `Uploads`. This table has column `Time`.

```{r, echo = FALSE, collapse=TRUE}
loaded_datatable <- NULL
if(identical(data_source, "Uploads")) {
  if(grepl("\\.fst$", path_datatable, ignore.case = TRUE)) {
    tbl <- fst::fst(path_datatable)
    if( nrow(tbl) > 1000 ) {
      loaded_datatable <- tbl[1:1000, ]
    } else {
      loaded_datatable <- tbl[]
    }
  }
}

if(is.data.frame(loaded_datatable)) {
  DT::datatable(loaded_datatable)
}
```

The render results:

```{rave render_viewer, language = "R", export = "brain_widget", cue = "always", collapse=TRUE}
#| code-fold: true
#| code-summary: "A fine-tuned 3D viewer that remembers the user inputs"

force(shiny_outputId)
controllers <- as.list(controllers)
main_camera <- as.list(main_camera)

background <- controllers[["Background Color"]]
if(length(background) != 1) {
  background <- "#FFFFFF"
}

zoom_level <- main_camera$zoom
if(length(zoom_level) != 1 || zoom_level <= 0) {
  zoom_level <- 1
}

position <- as.numeric(unname(unlist(main_camera$position)))
up <- as.numeric(unname(unlist(main_camera$up)))
if(length(position) != 3 || length(up) != 3 ||
   all(position == 0) || all(up == 0) ||
   any(is.na(position)) || any(is.na(up))) {
  position <- c(0, 0, 500)
  up <- c(0, 1, 0)
} else {
  position <- position / sqrt(sum(position^2)) * 500
  up <- up / sqrt(sum(up^2))
}

# find valid names
dnames <- brain_with_data$variables
dnames <- dnames[!dnames %in% c("Project", "Subject", "Electrode", "Time", "Label")]

dname <- controllers[["Display Data"]] %OF% dnames

if(!identical(controllers[["Display Data"]], dname) && length(dname)) {
  controllers[["Display Data"]] <- dname
  controllers[["Display Range"]] <- ""
}

if(!isTRUE(controllers[["Show Panels"]])) {
  controllers[["Show Panels"]] <- FALSE
}
    
brain_widget <- brain_with_data$brain$plot(
  show_modal = FALSE,
  background = background,
  controllers = controllers,
  start_zoom = zoom_level,
  # send signals to update parameters such as camera, zoom-level...
  custom_javascript = glue::glue(
    '
    // Remove the focus box
    if( canvas.focus_box ) {
      canvas.focus_box.visible = false;
    }
    
    // set camera
    canvas.mainCamera.position.set(
      {{ position[[1]] }} , 
      {{ position[[2]] }} , 
      {{ position[[3]] }}
    );
    canvas.mainCamera.up.set(
      {{ up[[1]] }} , 
      {{ up[[2]] }} , 
      {{ up[[3]] }}
    )
    canvas.mainCamera.updateProjectionMatrix();

    // Let shiny know the viewer is ready
    if( window.Shiny ) {
       window.Shiny.setInputValue("{{ shiny_outputId }}", "{{Sys.time()}}");
    }

    // Force render one frame (update the canvas)
    canvas.needsUpdate = true;
    ',
    .open = "{{", .close = "}}"
  )
)

```

## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-custom_3d_viewer.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-custom_3d_viewer.R")
```

Once the pipeline script `make-custom_3d_viewer.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
Sys.setenv("RAVE_PIPELINE" = normalizePath("."))
try({
  ravepipeline::pipeline_visualize()
}, silent = TRUE)
```
