---
title: "RAVE Project Overview"
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
ravepipeline::pipeline_setup_rmd("project_overview")
```


## Phase 1 — Validation & Configuration

```{rave validate_project, language = "R", export = "project", cue = "always"}
all_projects <- ravecore::get_projects(refresh = TRUE)
if (!length(project_name) || !nzchar(project_name) || !project_name %in% all_projects) {
  stop("Invalid project_name: ", sQuote(project_name),
       ". Available: ", paste(all_projects, collapse = ", "))
}
project <- ravecore::as_rave_project(project_name, strict = FALSE)
```

```{rave collect_subject_info, language = "R", export = "subject_summary", cue = "always"}
available_subjects <- project$subjects()
if (!length(available_subjects)) {
  stop("Project ", sQuote(project$name), " has no subjects.")
}

subject_summary <- do.call("rbind", lapply(available_subjects, function(sc) {
  subject <- ravecore::RAVESubject$new(
    project_name = project$name,
    subject_code = sc,
    strict = FALSE
  )
  preproc <- subject$preprocess_settings

  data_imported <- all(preproc$data_imported)
  notch_filtered <- all(preproc$notch_filtered)
  has_wavelet <- all(preproc$has_wavelet)

  etable <- tryCatch(subject$meta_data("electrodes"), error = function(e) data.frame())
  localized <- nrow(etable) > 0 &&
    all(c("Electrode", "Coord_x", "Coord_y", "Coord_z", "Label") %in% names(etable)) &&
    any(etable$Coord_x^2 + etable$Coord_y^2 + etable$Coord_z^2 > 0, na.rm = TRUE)

  n_electrodes <- length(subject$electrodes)
  blocks <- tryCatch(subject$blocks, error = function(e) character(0))
  n_epochs <- length(subject$epoch_names)
  n_references <- length(subject$reference_names)

  data.frame(
    Subject = sc,
    Electrodes = n_electrodes,
    Imported = data_imported,
    Notch = notch_filtered,
    Wavelet = has_wavelet,
    Localized = localized,
    Blocks = paste(blocks, collapse = ", "),
    Epoch_tables = n_epochs,
    Reference_tables = n_references,
    stringsAsFactors = FALSE
  )
}))
head(subject_summary)
```

```{rave ensure_template_brain, language = "R", export = "template_subject_ensured", cue = "always"}
template_root <- threeBrain::default_template_directory()
installed_templates <- list.dirs(template_root, full.names = FALSE, recursive = FALSE)
installed_templates <- installed_templates[grepl("^[a-zA-Z]", installed_templates)]
installed_templates <- installed_templates[
  !installed_templates %in% c("templates", "prototypes")]

if (!isTRUE(template_subject %in% installed_templates)) {
  downloadable <- names(threeBrain::available_templates())
  if (!isTRUE(template_subject %in% downloadable)) {
    stop("Template brain not available. Choose from: ",
         paste(unique(c(downloadable, installed_templates)), collapse = ", "))
  }
  threeBrain::download_template_subject(template_subject)
}
template_subject_ensured <- template_subject
```

```{rave resolve_subjects, language = "R", export = "resolved_subjects", cue = "always"}
# subject_codes from settings.yaml — NULL or empty means all subjects
if (is.null(subject_codes) || !length(subject_codes)) {
  resolved_subjects <- subject_summary$Subject
} else {
  resolved_subjects <- subject_codes[subject_codes %in% subject_summary$Subject]
  if (!length(resolved_subjects)) {
    stop("None of the requested subjects exist. Available: ",
         paste(subject_summary$Subject, collapse = ", "))
  }
}

resolved_subjects <- sort(resolved_subjects)
```


## Phase 2 — Group-Level Targets

```{rave generate_group_subject_summary, language = "R", export = "snapshot_group_subject_summary"}
snapshot_group_subject_summary <- subject_summary[
  subject_summary$Subject %in% resolved_subjects, , drop = FALSE
]
```

```{rave generate_group_brain, language = "R", export = "snapshot_group_brain"}
pname <- project$name

# Collect one brain per subject (skip subjects without surface data)
brain_list <- lapply(resolved_subjects, function(sc) {
  subject <- ravecore::new_rave_subject(
    project_name = pname,
    subject_code = sc,
    strict = FALSE
  )
  tryCatch(
    ravecore::rave_brain(subject),
    error = function(e) {
      NULL
    }
  )
})

snapshot_group_brain <- threeBrain::merge_brain(
  .list = brain_list,
  template_surface_types = c("inflated", "sphere.reg"),
  template_subject = template_subject_ensured,
  electrode_priority = "sphere"
)

# snapshot_group_brain$plot() to view the template brain with electrodes from all subjects
```

```{rave generate_group_electrode_coverage, language = "R", export = "snapshot_group_electrode_coverage"}
pname <- project$name

# Gather electrode atlas labels from every subject
pieces <- lapply(resolved_subjects, function(sc) {
  subject <- ravecore::new_rave_subject(
    project_name = pname,
    subject_code = sc,
    strict = FALSE
  )
  etable <- tryCatch(
    subject$meta_data("electrodes"),
    error = function(e) NULL
  )
  if (!is.data.frame(etable) || !nrow(etable) || !length(etable$FSLabel)) {
    return(data.frame(FSLabel = "Unknown", Subject = sc, stringsAsFactors = FALSE))
  }
  if (!length(etable$FSLabel)) { return(NULL) }

  labels <- etable$FSLabel
  labels[is.na(labels) | !nzchar(labels)] <- "Unknown"
  data.frame(FSLabel = labels, Subject = sc, stringsAsFactors = FALSE)
})
pieces <- do.call("rbind", pieces)


if (!length(pieces)) {
  snapshot_group_electrode_coverage <- data.frame(
    FSLabel = character(0), Total = integer(0),
    stringsAsFactors = FALSE)
} else {

  # Pivot to wide: rows = FSLabel, columns = subject codes, values = count
  wide <- reshape2::dcast(pieces, FSLabel ~ Subject,
                          fun.aggregate = length,
                          value.var = "FSLabel", fill = 0L)

  wide <- wide[wide$FSLabel != "Unknown", , drop = FALSE]

  # Add Total as second column
  subject_cols <- setdiff(names(wide), "FSLabel")
  wide$Total <- rowSums(wide[, subject_cols, drop = FALSE])
  wide <- wide[, c("FSLabel", "Total", subject_cols), drop = FALSE]

  snapshot_group_electrode_coverage <- wide

  rownames(snapshot_group_electrode_coverage) <- NULL
}
head(snapshot_group_electrode_coverage)
```


## Phase 3 — Subject-Level Targets

Each target returns a **named list** keyed by subject code.
The UI indexes by the currently selected subject.
Pipeline discovers ALL data; section toggles and `module_filter` are
applied in the UI so the pipeline cache stays stable.

```{rave generate_subject_module_reports, language = "R", export = "snapshot_subject_module_reports"}
pname <- project$name

# Report directories follow the pattern:
#   report-{name}_datetime-{YYMMDDTHHMMSS}_{module}/report.html
report_dir_pattern <- "^report-(.+)_datetime-([0-9]{6}T[0-9]{6})_(.+)$"

results <- structure(
  names = resolved_subjects,
  lapply(resolved_subjects, function(sc) {
    subject <- ravecore::new_rave_subject(
      project_name = pname, subject_code = sc, strict = FALSE)
    rpath <- subject$report_path

    empty <- data.frame(
      report_name = character(0), module = character(0),
      timestamp = character(0), dir_name = character(0),
      file_path = character(0),
      stringsAsFactors = FALSE)

    if (!length(rpath) || !dir.exists(rpath)) { return(empty) }

    dirs <- list.dirs(rpath, recursive = FALSE, full.names = FALSE)
    matched <- grepl(report_dir_pattern, dirs)
    dirs <- dirs[matched]
    if (!length(dirs)) { return(empty) }

    parsed <- regmatches(dirs, regexec(report_dir_pattern, dirs))
    rname <- vapply(parsed, `[[`, "", 2)
    tstamp <- vapply(parsed, `[[`, "", 3)
    module <- vapply(parsed, `[[`, "", 4)
    fpath <- file.path(rpath, dirs, "report.html")
    exists <- file.exists(fpath)

    df <- data.frame(
      report_name = rname, module = module,
      timestamp = tstamp, dir_name = dirs,
      file_path = fpath,
      stringsAsFactors = FALSE)
    df <- df[exists, , drop = FALSE]

    # Apply module_filter from settings if specified
    if (length(module_filter)) {
      df <- df[df$module %in% module_filter, , drop = FALSE]
    }

    # Sort newest first
    if (nrow(df)) {
      df <- df[order(df$timestamp, decreasing = TRUE), , drop = FALSE]
      rownames(df) <- NULL
    }
    df
  })
)

snapshot_subject_module_reports <- results
head(snapshot_subject_module_reports)
```

```{rave generate_subject_electrode_tables, language = "R", export = "snapshot_subject_electrode_tables"}
pname <- project$name

snapshot_subject_electrode_tables <- structure(
  names = resolved_subjects,
  lapply(resolved_subjects, function(sc) {
    subject <- ravecore::new_rave_subject(
      project_name = pname, subject_code = sc, strict = FALSE)
    tryCatch(
      subject$meta_data("electrodes"),
      error = function(e) data.frame()
    )
  })
)
head(snapshot_subject_electrode_tables)
```

```{rave generate_subject_meta_summary, language = "R", export = "snapshot_subject_meta_summary"}
pname <- project$name

snapshot_subject_meta_summary <- structure(
  names = resolved_subjects,
  lapply(resolved_subjects, function(sc) {
    subject <- ravecore::new_rave_subject(
      project_name = pname, subject_code = sc, strict = FALSE)

    # Epochs
    epoch_rows <- lapply(subject$epoch_names, function(en) {
      etable <- tryCatch(
        subject$meta_data(meta_type = "epoch", meta_name = en),
        error = function(e) NULL
      )
      n_trials <- if (is.data.frame(etable)) nrow(etable) else 0L
      conditions <- if (is.data.frame(etable) &&
        "Condition" %in% names(etable)) {
        paste(unique(etable$Condition), collapse = ", ")
      } else {
        ""
      }

      data.frame(
        Type = "Epoch", Name = en,
        Trials = n_trials, Conditions = conditions,
        stringsAsFactors = FALSE
      )
    })

    # References
    ref_rows <- lapply(subject$reference_names, function(rn) {
      data.frame(
        Type = "Reference", Name = rn,
        Trials = NA_integer_, Conditions = "",
        stringsAsFactors = FALSE
      )
    })

    do.call(rbind, c(epoch_rows, ref_rows))
  })
)
head(snapshot_subject_meta_summary)
```

```{rave generate_subject_3d_viewers, language = "R", export = "snapshot_subject_3d_viewers"}
pname <- project$name

# Store viewer HTML files under project group_path so standalone_report
# can serve them
snapshot_root <- file.path(
  project$group_path("project_overview"), "snapshot", "subjects")

snapshot_subject_3d_viewers <- structure(
  names = resolved_subjects,
  lapply(resolved_subjects, function(sc) {
    subject <- ravecore::new_rave_subject(
      project_name = pname, subject_code = sc, strict = FALSE)
    brain <- ravecore::rave_brain(subject)
    brain
  })
)
```

```{rave generate_subject_validation, language = "R", export = "snapshot_subject_validation"}
pname <- project$name

snapshot_subject_validation <- lapply(resolved_subjects, function(sc) {
  subject <- ravecore::new_rave_subject(
    project_name = pname, subject_code = sc, strict = FALSE)
  results <- tryCatch(
    ravecore::validate_subject(
      subject = subject, method = "normal", verbose = FALSE),
    error = function(e) { NULL }
  )
  if (is.null(results)) {
    return(data.frame(
      Subject = sc,
      Section = "Error", Check = "validate_subject",
      Valid = FALSE, Message = "Validation failed to run",
      stringsAsFactors = FALSE
    ))
  }
  # results is a fastmap2 with sections: paths, preprocess, meta,
  # voltage_data, power_phase_data, epoch_tables, reference_tables
  # Each section is also a fastmap2 of validate_result items
  section_names <- names(results)
  rows <- lapply(section_names, function(sname) {
    section <- results[[sname]]
    if (!inherits(section, "fastmap2")) { return(NULL) }
    item_names <- names(section)
    do.call(rbind, lapply(item_names, function(iname) {
      item <- section[[iname]]
      if (!is.list(item) || is.null(item$valid)) { return(NULL) }
      valid <- item$valid
      msg <- if (isTRUE(valid)) {
        "OK"
      } else if (is.na(valid)) {
        item$message %||% "Skipped"
      } else {
        item$message %||% "Failed"
      }
      data.frame(
        Subject = sc,
        Section = sname,
        Check = item$name %||% iname,
        Valid = isTRUE(valid),
        Message = msg,
        stringsAsFactors = FALSE
      )
    }))
  })
  do.call(rbind, rows)
})
names(snapshot_subject_validation) <- resolved_subjects
head(snapshot_subject_validation)
```


## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-project_overview.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-project_overview.R")
```


Once the pipeline script `make-project_overview.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
# Fixed usage, show pipeline graph
try({
  asNamespace("ravepipeline")$pipeline_dependency_graph(
    pipeline_path = ".", glimpse = TRUE)
}, silent = TRUE)
```



