---
title: "RAVE Project Overview"
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
ravepipeline::pipeline_setup_rmd("project_overview")
```

```{rave obtain_project_names, language = "R", export = "project_names_cleaned"}
all_projects <- raveio::get_projects(refresh = TRUE)
if(length(project_names)) {
  project_names_cleaned <- sort(unique(unlist(project_names)))
  project_names_cleaned <- project_names_cleaned[project_names_cleaned %in% all_projects]
} else {
  project_names_cleaned <- all_projects
}
if(!length(project_names_cleaned)) {
  stop("No valid project found.")
}
```

```{rave ensure_template_brain, language = "R", export = "template_info", cue = "always"}
template_info <- ensure_brain_template(template_subject = template_subject)
```

```{rave generate_project_overview, language = "R", export = "project_overview", cue = "always"}
if( nzchar(Sys.getenv("RAVE_PIPELINE_ACTIVE", unset = "")) ) {
  force(template_info)
  project_overview <- generate_website(project_names_cleaned)
} else {
  project_overview <- NULL
}
```


## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-project_overview.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-project_overview.R")
```


Once the pipeline script `make-project_overview.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
# Fixed usage, show pipeline graph
try({
  asNamespace("ravepipeline")$pipeline_dependency_graph(
    pipeline_path = ".", glimpse = TRUE)
}, silent = TRUE)
```



