---
title: "Project Report"
format: html
---

```{r setup, include=FALSE}
source("./columns.R")

project_name <- "{{PROJECT_NAME}}"

reading_errors <- list()
print_error <- function(err_text) {
    reading_errors <<- c(reading_errors, err_text)
}

get_cache_file <- function(file_name) {
    file_path <- glue::glue("cache/{project_name}/{file_name}")
    if (!dir.exists(dirname(file_path))) {
        dir.create(dirname(file_path), recursive = TRUE)
    }
    list(
        exists = file.exists(file_path),
        write_path = file_path,
        link_tag = function(text) {
            glue::glue(
                # "<a class=\"nowrap\" href=\"../cache/{project_name}/{file_name}?t={as.numeric(Sys.time())}\" target=\"viewer_iframe\" onclick=\"showIframeDrawer()\">{text}</a>"
              "<a class=\"nowrap\" href=\"../cache/{project_name}/{file_name}?t={as.numeric(Sys.time())}\" target=\"_blank\">{text}</a>"
            )
        }
    )
}

get_subject_cache_file <- function(file_name, subject) {
    subject_code <- subject$subject_code
    get_cache_file(glue::glue("{subject_code}/{file_name}"))
}

project <- raveio::as_rave_project(project_name)
subjects_codes <- project$subjects()

number_of_subjects <- length(subjects_codes)
```

### `r project_name` (`r number_of_subjects` subjects)

```{r, echo=FALSE, results='asis', warning=FALSE}
#| column: screen-inset-right

group_level_viewer_cache_file <- get_cache_file("group_viewer.html")
if (!group_level_viewer_cache_file$exists) {
    tryCatch(
        {
            brain_list <- lapply(subjects_codes, function(subject_code) {
                subject <- raveio::RAVESubject$new(project_name = project$name, subject_code = subject_code)
                brain <- raveio::rave_brain(subject)
                if (length(brain)) {
                    brain$set_electrode_values()
                }
                brain
            })
            template_brain <- threeBrain::merge_brain(.list = brain_list, template_subject = "fsaverage")
            viewer <- template_brain$plot()
            threeBrain::save_brain(viewer, path = group_level_viewer_cache_file$write_path)
        },
        error = function(e) {
            print_error(paste0("Error reading electrodes meta file: ", e$message))
        }
    )
}

group_level_viewer_cache_file$link_tag("Group Level 3D Viewer")
```


#### Electrodes Table

```{r, echo=FALSE, warning=FALSE}
#| column: screen-inset-right
subjects_label_counts <- list()
all_labels <- list()
for (subject_code in subjects_codes) {
    tryCatch(
        {
            subject <- raveio::RAVESubject$new(project_name = project$name, subject_code = subject_code)
            electrode_labels <- subject$get_electrode_table()$FSLabel
            if (!is.null(electrode_labels)) {
                subjects_label_counts[[subject_code]] <- as.list(table(electrode_labels))
                all_labels <- unique(c(all_labels, electrode_labels))
            }
        },
        error = function(e) {
            print_error(
                glue::glue("Could not get electrodes of {subject_code}: {e$message}")
            )
        }
    )
}

electrodes_rows <- lapply(all_labels, function(label) {
    if (is.null(label) || is.na(label) || label == "") {
        return(NULL)
    }
    result <- list("FS Label" = label)
    for (subject_code in subjects_codes) {
        value <- subjects_label_counts[[subject_code]][[label]]
        result[[subject_code]] <- if (is.null(value)) 0 else value
    }
    result
})

# electrodes_df <- dplyr::bind_rows(electrodes_rows)
electrodes_df <- data.table::rbindlist(electrodes_rows)
DT::datatable(
    electrodes_df,
    rownames = FALSE,
    options = list(
        fixedColumns = list(leftColumns = 1),
        scrollX = TRUE,
        width = "100%"
    )
)
```


#### Subjects Table

```{r, echo=FALSE, warning=FALSE}
#| column: screen-inset-right
subjects_data <- lapply(subjects_codes, function(subject_name) {
    subject_id <- paste0(project_name, "/", subject_name)
    subject <- raveio::as_rave_subject(subject_id)

    lapply(
        subjects_columns,
        function(column) {
            column(subject)
        }
    )
})

# subjects_df <- dplyr::bind_rows(subjects_data)
subjects_df <- data.table::rbindlist(subjects_data)
DT::datatable(subjects_df, escape = FALSE)
```

#### Validations

```{r, echo=FALSE, results='asis', warning=FALSE}
#| column: screen-inset-right

errors <- list()
check_error <- function(subject_code, error_name, rave_validation_object) {
    if (!isTRUE(rave_validation_object$valid)) {
        errors <<- append(errors, list(list(
            Name = error_name,
            Subject = subject_code,
            Description = rave_validation_object$description,
            "Error Message" = rave_validation_object$message
        )))
    }
}

for (subject_code in subjects_codes) {
    subject_id <- paste0(project_name, "/", subject_code)
    subject <- raveio::as_rave_subject(subject_id)
    validation_cache = get_subject_cache_file("validation", subject)
    if (validation_cache$exists) {
      subject_validation <- readRDS(validation_cache$write_path)
    }
    else {
      subject_validation <- raveio::validate_subject(
          subject_id,
          verbose = FALSE, method = "normal"
      )
      saveRDS(subject_validation, file=validation_cache$write_path)
    } 
    for (ref_name in subject$reference_names) {
        check_error(subject_code, paste0("Reference ", ref_name), subject_validation$reference_tables[[ref_name]])
    }
    for (epoch_name in subject$epoch_names) {
        check_error(subject_code, paste0("Reference ", epoch_name), subject_validation$epoch_tables[[epoch_name]])
    }
    check_error(subject_code, "Electrodes Preprocess", subject_validation$preprocess$electrodes_set)
    check_error(subject_code, "Blocks Preprocess", subject_validation$preprocess$blocks_set)
    check_error(subject_code, "Metadata", subject_validation$meta$meta_data_valid)
}

errors_df <- data.table::rbindlist(errors)
knitr::kable(errors_df, format = "simple")
```

#### Report Generation Errors

```{r, echo=FALSE, results='asis', warning=FALSE}
#| column: screen-inset-right
if (length(reading_errors) > 0) {
    cat(paste0(lapply(reading_errors, function(error) {
        glue::glue("<li> {error} </li>")
    })))
    cat("</ul>")
} else {
    cat("None")
}
```

<style>
  .drawer {
    height: 100%;
    width: 95vw;
    position: fixed;
    top: 0;
    right: -95vw;
    background-color: #ffffff;
    transition: 0.4s ease-out;
    padding: 20px;
    padding-top: 40px;
    z-index: 999;
  }

  .drawer.open {
    right: 0;
    box-shadow: 2px 0 20px rgba(0,0,0,0.5);
  }

  .close-drawer-btn {
    position: absolute;
    top: 5px;
    left: 5px;
    border-radius: 5px;
    width: 26px;
    height: 26px;
    line-height: 0;
    box-sizing: border-box;
    border: solid 2px #b4b4b4;
    background: #e6e6e6;
    display: grid;
    place-items: center;
    padding: 0;
    padding-bottom: 2px;
    color: #474747;
  }

  .nowrap {
    white-space: nowrap;
  }
</style>

<div id="iframe-drawer" class="drawer">
  <button class="close-drawer-btn" onclick="closeIframeDrawer()"> x </button>
  <p style="height: 100%">
    <iframe name="viewer_iframe" style="width: 100%; height: 100%"></iframe>
  </p>
</div>

<script>
  function showIframeDrawer() {
    const $drawer = document.getElementById('iframe-drawer');
    let drawerHeight = parseInt(document.body.getAttribute('wrapper-height'));
    if( isFinite(drawerHeight) && drawerHeight > 100 ) {
      $drawer.style.maxHeight = `${drawerHeight}px`;
    } else {
      $drawer.style.maxHeight = `100vh`;
    }
    $drawer.classList.add('open');
  }
  function closeIframeDrawer() {
    document.getElementById('iframe-drawer').classList.remove('open');
  }

  document.addEventListener('keydown', function(event) {
    if (event.key === "Escape") {
      closeIframeDrawer();
    }
  });
</script>
