---
title: "RAVE Pipeline Markdown Template"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
ravepipeline::pipeline_setup_rmd("voltage_explorer")
```


```{rave load_subject, language = "R", export = "subject"}
subject <- ravecore::new_rave_subject(
  project_name = project_name, 
  subject_code = subject_code
)
print(subject)

# List subject details
subject$epoch_names
subject$reference_names
subject$blocks
subject$electrodes
```


```{rave prepare_data_repository, language = "R", export = "repository", cue = "always", format = "rave_prepare_subject_voltage_with_epoch"}
repository <- ravecore::prepare_subject_voltage_with_epochs(
  subject = subject,
  electrodes = loaded_electrodes,
  epoch_name = epoch_choice,
  time_windows = c(epoch_choice__trial_starts, epoch_choice__trial_ends),
  reference_name = reference_name
)
```

`analysis_channels_clean` is the cleaned analysis channels. Compared to the input `analysis_channels`, the cleaned version

* Not empty
* Electrode channel data must be loaded
* Sorted integer, from smallest to largest


```{rave clean_analysis_channels, language = "R", export = "analysis_channels_clean"}
available_channels <- repository$electrode_list
analysis_channels_clean <- dipsaus::parse_svec(unlist(analysis_channels))
analysis_channels_clean <- analysis_channels_clean[analysis_channels_clean %in% available_channels]
if(!length(analysis_channels_clean)) {
  stop("No channels selected for analysis. Please specify the electrode channels from the following loaded: ",
       dipsaus::deparse_svec(available_channels))
}
analysis_channels_clean <- as.integer(sort(analysis_channels_clean))
```

```{rave prepare_pre_analysis_filters, language = "R", export = "filtered_array"}
filtered_array <- prepare_filtered_data(
  data_path = "data/filtered_voltage",
  repository = repository,
  filter_configurations = filter_configurations
)

# Electrodes to be filtered
# lapply(analysis_channels_clean, function(ch) {
#   sel <- repository$electrode_list %in% ch
#   source_array <- repository$voltage$data_list[[which(sel)]]
#   signals <- source_array[reshape = dim(source_array)[c(1, 2)]]
#   
#   # filtered signals
#   filtered <- apply_filters_to_signals(
#     signals = signals, 
#     filter_configs = config
#   )
# })

filtered_array <- ravepipeline::RAVEFileArray$new(filtered_array)

ravepipeline::with_rave_parallel({
  ravepipeline::lapply_jobs(analysis_channels_clean, function(ch) {
    sel <- repository$electrode_list %in% ch
    source_array <- repository$voltage$data_list[[which(sel)]]
    signals <- source_array[reshape = dim(source_array)[c(1, 2)]]
    
    # Get filter inputs
    filtered_array_impl <- filtered_array$`@impl`
    filter_configs <- filtered_array_impl$get_header("filter_configurations")
    
    # filtered signals
    filtered <- apply_filters_to_signals(signals = signals, 
                                         filter_configs = filter_configs)
    
    # write to disk via filearray
    filtered_array_impl$.mode <- "readwrite"
    filtered_array_impl[, , sel] <- filtered
    
    return(ch)
  }, .globals = list(
    repository = repository,
    filtered_array = filtered_array,
    apply_filters_to_signals = apply_filters_to_signals,
    apply_filter = apply_filter,
    ALLOWED_FILTER_TYPES = ALLOWED_FILTER_TYPES,
    `%?<-%` = `%?<-%`
  ), callback = function(ch) {
    sprintf("Filtering channel|%d", ch)
  })
})

filtered_array$`@impl`
```

```{rave get_electrode_coordinate_table, export = "analysis_electrode_coordinates"}
analysis_electrode_coordinates <- subject$get_electrode_table(
  electrodes = analysis_channels_clean,
  reference_name = repository$reference_name,
  subset = TRUE
)
labels <- analysis_electrode_coordinates$Label
if (!length(analysis_electrode_coordinates$LabelPrefix)) {
  analysis_electrode_coordinates$LabelPrefix <- gsub("[0-9]+", "", labels)
}
label_prefix <- analysis_electrode_coordinates$LabelPrefix

label_prefix_lag1 <- c("", label_prefix[-length(label_prefix)])
is_lead_channel <- label_prefix != label_prefix_lag1
analysis_electrode_coordinates$ShortLabel <- ifelse(
  !is_lead_channel,
  gsub("^[a-zA-Z_-]+", "", labels), labels
)
analysis_electrode_coordinates$LeadChannel <- is_lead_channel
```

## Clean condition groups

`condition_groupings_clean` is a list with two elements:

* `n`: number of valid condition groups after cleaning;
* `groups`: unnamed list of cleaned group items, each containing `label`
  (auto-filled when missing), `group_index` (original position, used to
  derive a stable color), and `conditions` (unique, in input order).

Groups with empty labels are auto-named (`Group<index>`); groups whose
conditions are empty or do not appear in the epoch are dropped.

```{rave clean_condition_groupings, language = "R", export = "condition_groupings_clean"}
condition_groupings_clean <- ravecore::validate_condition_groupings(
  condition_groupings = condition_groupings,
  epoch = repository$epoch
)
if (!isTRUE(condition_groupings_clean$n > 0)) {
  stop("No valid condition group specified. Please check the condition groupings input.")
}
```


Combine `condition_groupings_clean` and `filtered_array` to prepare plot data

```{rave prepare_plot_data_placeholder, export = "data_placeholder"}
data_placeholder <- condition_groupings_clean

if (inherits(filtered_array, "RAVEFileArray")) {
  # unwrap the filtered_array
  filtered_array_impl <- filtered_array$`@impl`
} else {
  filtered_array_impl <- filtered_array
}
dnames <- dimnames(filtered_array_impl)

# Sample rate
data_placeholder$sample_rate <- filtered_array_impl$get_header("sample_rate")

# electrode coordinate table
data_placeholder$coord_table <- analysis_electrode_coordinates

# time points
data_placeholder$time_points <- dnames$Time
```


## Prepare data

Variables: condition group (of trials), channel

Visualizations

- By-channel plot
  - plot ERP for each condition group (time x channel x condition)
  - plot ERP for each trial, grouped by condition group (time x channel x condition*trial) <- needs to think about collapsing... maybe inter-trial phase coherence
- By-condition plot
  - plot each channel (collapse trials) (time x channel x condition)
  - collapse channel - each cond. group is a line
  - plot each trial - collapse channels

### `data_by_channel_condition`

For each channel, condition group, collapse over trials

```{rave prepare_voltage_over_channel_and_condition_by_collapsing_trials, language = "R", export = "data_by_channel_condition"}
if (inherits(filtered_array, "RAVEFileArray")) {
  # unwrap the filtered_array
  filtered_array_impl <- filtered_array$`@impl`
} else {
  filtered_array_impl <- filtered_array
}

group_data <- lapply(data_placeholder$groups, function(group) {
  # group <- data_placeholder$groups[[1]]
  sub_array <- subset(
    filtered_array_impl,
    Electrode ~ Electrode %in% analysis_channels_clean,
    Trial ~ Trial %in% group$trials_included,
    drop = FALSE
  )
  # Drop dimnames to speed up
  dimnames(sub_array) <- NULL
  
  # Collapse over trial
  ravetools::collapse(x = sub_array,
                      keep = c(1L, 3L),
                      average = TRUE)
})

# Time x Channel x Group
group_data <- simplify2array(group_data)

data_by_channel_condition <- data_placeholder
data_by_channel_condition$data <- group_data
class(data_by_channel_condition) <- "data_by_channel_condition"
```

Visualization:

- By-channel plot
  - plot ERP for each condition group
- By-condition plot
  - plot each channel (collapse trials)

```{r}
plot(data_by_channel_condition,
     group_by = "channel",
     channel_annotation = "full")

plot(data_by_channel_condition,
     group_by = "condition",
     channel_annotation = "short")

# plot_by_channel_condition(
#   data_by_channel_condition = data_by_channel_condition,
#   group_by = "channel",
#   channel_annotation = "full"
# )
# 
# plot_by_channel_condition(
#   data_by_channel_condition = data_by_channel_condition,
#   group_by = "condition",
#   channel_annotation = "short"
# )
```

### Collapse channels

- By-condition plot
  - plot each trial - collapse channels

```{rave prepare_voltage_collapsed_over_channels_per_condition, export = "data_by_trial_per_condition"}
if (inherits(filtered_array, "RAVEFileArray")) {
  # unwrap the filtered_array
  filtered_array_impl <- filtered_array$`@impl`
} else {
  filtered_array_impl <- filtered_array
}

dnames <- dimnames(filtered_array_impl)
trial_numbers <- dnames$Trial

group_data <- lapply(data_placeholder$groups, function(group) {
  # group <- data_placeholder$groups[[1]]
  sub_array <- subset(
    filtered_array_impl,
    Electrode ~ Electrode %in% analysis_channels_clean,
    Trial ~ match(group$trials_included, trial_numbers),
    drop = FALSE
  )
  # Drop dimnames to speed up
  dimnames(sub_array) <- NULL
  
  # Collapse over trial (the trial is sorted by stimuli names)
  voltage_by_trial <- ravetools::collapse(x = sub_array,
                                          keep = c(1L, 2L),
                                          average = TRUE)
  return(voltage_by_trial)
})

data_by_trial_per_condition <- data_placeholder
data_by_trial_per_condition$data <- group_data
class(data_by_trial_per_condition) <- "data_by_trial_per_condition"
```

```{r}
# or plot(...)
plot_by_trial_per_condition(
  data_by_trial_per_condition, space = 0.9)
```

- By-condition plot
  - collapse channel - each cond. group is a line

```{rave prepare_collapsed_voltage_per_condition, export = "data_collapse_by_condition"}
data_collapse_by_condition <- data_by_trial_per_condition

time_points <- data_collapse_by_condition$time_points
sample_rate <- data_collapse_by_condition$sample_rate 

time_range <- range(time_points)
crp_time_begin <- 0.01
if (crp_time_begin > time_range[[2]]) {
  crp_time_begin <- 0
}
crp_time_end <- time_range[[2]]
crp_time_step <- max(floor(sample_rate / 50), 5)

# make sure CRP time points have at least 11 time-points
if ((crp_time_end - crp_time_begin) * sample_rate <= 10) {
  crp_enabled <- FALSE
} else {
  crp_enabled <- TRUE
}


group_data <- lapply(seq_along(data_collapse_by_condition$groups), function(ii) {
  # ii = 2
  group <- data_collapse_by_condition$groups[[ii]]
  voltage_by_trial <- data_collapse_by_condition$data[[ii]]
  
  if (crp_enabled) {
    crp_result <- ravetools::crp(
      voltage_by_trial,
      time = time_points,
      t_start = crp_time_begin,
      t_end = crp_time_end,
      time_step = crp_time_step,
      threshold_quantile = 0.98,
      artifact_interval = "tR",
      remove_artifacts = FALSE
    )
  } else {
    crp_result <- NULL
  }
  
  # Mean and se of mean
  if (length(crp_result$bad_trials)) {
    voltage_by_trial <- voltage_by_trial[, - crp_result$bad_trials, drop = FALSE]
  }
  
  n_samples <- ncol(voltage_by_trial)
  
  mean_erp <- rowMeans(voltage_by_trial)
  
  return(list(
    mean = mean_erp,
    bad_trials = group$trials_included[crp_result$bad_trials], 
    tau_r = c(crp_result$tau_R_lower, crp_result$tau_R, crp_result$tau_R_upper)
  ))
})

mean_erp <- simplify2array(lapply(group_data, "[[", "mean"))
bad_trials <- lapply(group_data, "[[", "bad_trials")
crp_tau <- lapply(group_data, "[[", "tau_r")


data_collapse_by_condition$data <- list(
  mean_erp = mean_erp,
  bad_trials = bad_trials,
  crp_enabled = crp_enabled,
  crp_time_range = c(crp_time_begin, crp_time_end),
  crp_tau = crp_tau
)
class(data_collapse_by_condition) <- "data_collapse_by_condition"
```

```{r}
# or plot(...)
plot_collapse_by_condition(data_collapse_by_condition, time_range = c(-0.5, 1), flip_y = TRUE)
```

### Spectrogram analyses

I decide to hide this part. Users can still use the `ravepipeline` infrastructure to run the analysis by loading the shared environment. However, calculating the spectrogram can be slow, hence I prefer to offloading the analysis to the interactive UI and report system, rather than making them stay in the pipeline

```
env <- pipeline$shared_env()
spectrogram <- env$calculate_spectrogram(
  repository = repository,
  condition_groupings = condition_groupings,
  channel = analysis_channels_clean[[1]]
)

# ITPC
image(
  z = spectrogram$data$itpc[, , 2],
  zlim = c(0, 1),
  x = spectrogram$time_points,
  y = spectrogram$frequencies,
  log = "y"
)

# Power
hmap <- colorRampPalette(ravebuiltins::get_heatmap_palette("BlueWhiteRed"))(101)
plim <- max(abs(range(spectrogram$data$power)))
image(
  z = spectrogram$data$power[, , 2],
  zlim = c(-1, 1) * plim,
  x = spectrogram$time_points,
  y = spectrogram$frequencies,
  col = hmap
)
```


## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-voltage_explorer.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-voltage_explorer.R")
```


Once the pipeline script `make-voltage_explorer.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
# Fixed usage, show pipeline graph
try({
  asNamespace("ravepipeline")$pipeline_dependency_graph(
    pipeline_path = ".", glimpse = TRUE)
}, silent = TRUE)
```



