---
title: "RAVE Pipeline Markdown Template"
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: inline
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
ravepipeline::pipeline_setup_rmd("voltage_explorer")
```


```{r load_subject, engine='rave', language = "R", export = "subject"}
subject <- ravecore::new_rave_subject(
  project_name = project_name, 
  subject_code = subject_code
)
print(subject)

# List subject details
subject$epoch_names
subject$reference_names
subject$blocks
subject$electrodes
```


```{r prepare_data_repository, engine='rave', language = "R", export = "repository"}
repository <- ravecore::prepare_subject_voltage_with_epochs(
  subject = subject,
  electrodes = loaded_electrodes,
  epoch_name = epoch_choice,
  time_windows = c(epoch_choice__trial_starts, epoch_choice__trial_ends),
  reference_name = reference_name,
  stitch_events = c(
    epoch_choice__trial_starts_rel_to_event,
    epoch_choice__trial_ends_rel_to_event
  ), 
  quiet = TRUE
)
```

`analysis_electrodes_clean` is the cleaned analysis channels. Compared to the input `analysis_electrodes`, the cleaned version

* Not empty
* Electrode channel data must be loaded
* Sorted integer, from smallest to largest


```{r clean_analysis_electrodes, engine='rave', language = "R", export = "analysis_electrodes_clean"}
available_channels <- repository$electrode_list
analysis_electrodes_clean <- dipsaus::parse_svec(unlist(analysis_electrodes))
analysis_electrodes_clean <- analysis_electrodes_clean[analysis_electrodes_clean %in% available_channels]
if (!length(analysis_electrodes_clean)) {
  stop("No channels selected for analysis. Please specify the electrode channels from the following loaded: ",
       dipsaus::deparse_svec(available_channels))
}
analysis_electrodes_clean <- as.integer(sort(analysis_electrodes_clean))
```

```{r clean_analysis_event, engine='rave', language = "R", export = "analysis_event_colname"}
analysis_event_colname <- repository$epoch$get_event_colname(
  event = analysis_event, missing = "warning")
```

```{r diagnose_filters, engine='rave', language="R", export = "filter_freqz"}
# Pre-calculate each frequency filter so its frequency response can be plotted.
# Meta steps (detrend, demean, decimate, baseline) are not filter objects but
# advance the tracked effective sample rate / timepoint count accordingly.
sample_rate <- repository$sample_rate
time_points <- repository$voltage$dimnames$Time

start_time <- min(time_points, na.rm = TRUE)
n_timepoints <- length(time_points)
new_srate <- sample_rate

configs <- as.list(filter_configurations)

filter <- list()
pre_filter_decimate <- 1L
post_filter_decimate <- 1L
found_frequency_filter <- FALSE
freqz_n <- 2^(floor(log2(n_timepoints / 2)) + 1)

xlim <- c(0, 10)

for (cfg in configs) {
  type <- cfg$type %||% ""

  # -- Meta steps: update tracked state but produce no filter object ----------
  if (type %in% c("detrend", "demean", "baseline")) {
    next
  }

  if (type == "decimate") {
    by <- max(1L, as.integer(cfg$by %||% 1L))
    if (!found_frequency_filter) {
      # Pre-filter decimation: accumulate before first frequency filter
      pre_filter_decimate <- pre_filter_decimate * by
      new_srate <- new_srate / by
      n_timepoints <- ceiling(n_timepoints / by)
    } else {
      # Post-filter decimation: accumulate after frequency filters
      post_filter_decimate <- post_filter_decimate * by
    }
    next
  }

  # -- Normalize type aliases -------------------------------------------------
  if (type == "fir") { type <- "fir_kaiser" }
  if (type == "iir") { type <- "butter" }

  # -- Design the filter and capture coefficients for plotting ----------------
  f <- tryCatch({
    ravetools::design_filter(
      sample_rate          = new_srate,
      filter_order         = NA,
      data_size            = n_timepoints,
      high_pass_freq       = cfg$high_pass_freq       %||% NA,
      high_pass_trans_freq = cfg$high_pass_trans_freq %||% NA,
      low_pass_freq        = cfg$low_pass_freq        %||% NA,
      low_pass_trans_freq  = cfg$low_pass_trans_freq  %||% NA,
      passband_ripple      = cfg$passband_ripple      %||% 0.1,
      stopband_attenuation = cfg$stopband_attenuation %||% 40,
      scale                = TRUE,
      method               = type
    )
  }, error = function(e) {
    stop("Could not design filter (type=",
         type,
         "): ",
         conditionMessage(e))
    NULL
  })

  if (!is.null(f)) {
    found_frequency_filter <- TRUE
    freqz <- ravetools::freqz2(
      b = f$b,
      a = f$a,
      fs = new_srate,
      n = freqz_n,
      whole = FALSE
    )

    filter[[length(filter) + 1L]] <- list(
      config      = cfg,
      type        = type,
      sample_rate = new_srate,
      b           = f$b,
      a           = f$a,
      frequency   = freqz$w,
      response    = freqz$h
    )
    
    xlim <- range(c(
      xlim,
      c(f$parameters$stopband, f$parameters$passband) * new_srate / 2
    ), na.rm = TRUE)
  }
}

# -- Combined frequency response on the pre-decimated sample-rate axis --
if (length(filter)) {
  # All FIR/IIR filters see the same sample_rate (new_srate), so they're all
  # on the same frequency grid. Multiply responses directly.
  combined_freq <- seq(0, new_srate / 2, length.out = freqz_n)
  combined_response <- rep(1 + 0i, length(combined_freq))
  
  for (item in filter) {
    # All filters are at the same sample rate, so responses align on same grid.
    # Just multiply the complex responses directly.
    combined_response <- combined_response * item$response
  }
  
  filter_freqz <- structure(
    class = c("ravetools-freqz2", "ravetools-printable"),
    list(
      w = combined_freq, # Hz, on the pre-decimated sample rate
      h = combined_response, # complex; Mod() = amplitude, Arg() = phase
      f = combined_freq, # Hz, redundant with w, but more intuitive to associate with h
      u = "Hz",
      srate = new_srate, # sample rate at the input to the FIR/IIR filters
      pre_filter_decimate = pre_filter_decimate,
      post_filter_decimate = post_filter_decimate,
      original_srate = sample_rate,
      n = freqz_n,
      xlim = xlim
    )
  )
} else {
  filter_freqz <- NULL
}
# plot(filter_freqz, xlim = xlim)
```

```{r}
if (!is.null(filter_freqz)) {
  plot(filter_freqz, xlim = filter_freqz$xlim)
}
```

```{r prepare_pre_analysis_filters, engine='rave', language = "R", export = "filtered_array"}
filtered_array <- prepare_filtered_data(
  array_type = "filtered_voltage",
  repository = repository,
  filter_configurations = filter_configurations
)

filtered_array <- ravepipeline::RAVEFileArray$new(filtered_array)

# electrodes_to_filter <- analysis_electrodes_clean
electrodes_to_filter <- repository$electrode_list

invisible(
  # ravepipeline::with_rave_parallel({
    ravepipeline::lapply_jobs(electrodes_to_filter, function(ch) {
      sel <- repository$electrode_list %in% ch
      source_array <- repository$voltage$data_list[[which(sel)]]
      signals <- source_array[reshape = dim(source_array)[c(1, 2)]]
      
      # Get filter inputs
      filtered_array_impl <- filtered_array$`@impl`
      filter_configs <- filtered_array_impl$get_header("filter_configurations")
      
      # filtered signals
      filtered <- apply_filters_to_signals(signals = signals, filter_configs = filter_configs)
      
      # write to disk via filearray
      filtered_array_impl$.mode <- "readwrite"
      filtered_array_impl[, , sel] <- filtered
      
      return(ch)
    }, .globals = list(
      repository = repository,
      filtered_array = filtered_array,
      apply_filters_to_signals = apply_filters_to_signals,
      apply_filter = apply_filter,
      ALLOWED_FILTER_TYPES = ALLOWED_FILTER_TYPES,
      `%?<-%` = `%?<-%`
    ), callback = function(ch) {
      sprintf("Filtering channel|%d", ch)
    })
  # })
)

filtered_array$`@impl`
```

```{r align_to_analysis_event, engine='rave', language = "R", export = "aligned_array"}
aligned_array <- align_trials(filtered_array, analysis_event_colname)
```

```{r get_coordinate_table, engine='rave', export = "electrode_coordinates"}
electrode_coordinates <- subject$get_electrode_table(
  electrodes = repository$electrode_list,
  reference_name = repository$reference_name,
  subset = TRUE
)
labels <- electrode_coordinates$Label
if (!length(electrode_coordinates$LabelPrefix)) {
  electrode_coordinates$LabelPrefix <- gsub("[0-9]+", "", labels)
}
label_prefix <- electrode_coordinates$LabelPrefix

label_prefix_lag1 <- c("", label_prefix[-length(label_prefix)])
is_lead_channel <- label_prefix != label_prefix_lag1
electrode_coordinates$ShortLabel <- ifelse(
  !is_lead_channel,
  gsub("^[a-zA-Z_-]+", "", labels), labels
)
electrode_coordinates$LeadChannel <- is_lead_channel
```

```{r get_electrode_coordinate_table, engine='rave', export = "analysis_electrode_coordinates"}
analysis_electrode_coordinates <- electrode_coordinates[electrode_coordinates$Electrode %in% analysis_electrodes_clean, ]
```

## Clean condition groups

`condition_groups_clean` is a list with two elements:

* `n`: number of valid condition groups after cleaning;
* `groups`: unnamed list of cleaned group items, each containing `label`
  (auto-filled when missing), `group_index` (original position, used to
  derive a stable color), and `conditions` (unique, in input order).

Groups with empty labels are auto-named (`Group<index>`); groups whose
conditions are empty or do not appear in the epoch are dropped.

```{r clean_condition_groups, engine='rave', language = "R", export = "condition_groups_clean"}
condition_groups_clean <- ravecore::validate_condition_groupings(
  condition_groups,
  epoch = repository$epoch
)
if (!isTRUE(condition_groups_clean$n > 0)) {
  stop("No valid condition group specified. Please check the condition groupings input.")
}
```


Combine `condition_groups_clean` and `aligned_array` to prepare plot data

```{r prepare_plot_data_placeholder, engine='rave', export = "data_placeholder", cue = "always"}
data_placeholder <- condition_groups_clean

# unwrap the aligned_array
aligned_array_impl <- aligned_array$`@impl`
dnames <- dimnames(aligned_array_impl)

# Sample rate
data_placeholder$sample_rate <- aligned_array_impl$get_header("sample_rate")

# electrode coordinate table
data_placeholder$coord_table <- analysis_electrode_coordinates

# time points
data_placeholder$time_points <- dnames$Time

# Force the data to update if the array changes
attr(data_placeholder, "signature") <- aligned_array_impl$get_header("signature_filters")
```



```{r prepare_crp_settings, engine='rave', language = "R", export = "crp_settings"}
filtered_array_impl <- filtered_array$`@impl`

sample_rate <- filtered_array_impl$get_header("sample_rate")
time_range <- filtered_array_impl$get_header("valid_time_range")

# CRP detection window (t_start, t_end); either entry may be NA (or missing):
# t_start falls back to 0.01, t_end falls back to the max available time.
crp_detection_window <- suppressWarnings(as.numeric(unlist(crp_detection_window)))
crp_detection_window <- crp_detection_window[seq_len(2)]
crp_time_begin <- crp_detection_window[[1]]
if (!isTRUE(is.finite(crp_time_begin))) { crp_time_begin <- 0.01 }
if (crp_time_begin > time_range[[2]]) {
  crp_time_begin <- 0
}
crp_time_end <- crp_detection_window[[2]]
if (!isTRUE(is.finite(crp_time_end))) { crp_time_end <- time_range[[2]] }

# CRP sweeping step (in samples)
crp_time_step <- as.integer(crp_time_step)
if (!isTRUE(crp_time_step >= 1)) { crp_time_step <- 5L }

# CRP duration-uncertainty threshold (percent -> fraction)
crp_threshold_quantile <- as.numeric(crp_threshold_quantile)
if (!isTRUE(crp_threshold_quantile >= 1 && crp_threshold_quantile <= 100)) {
  crp_threshold_quantile <- 98
}

# Onset detection: border controls whether to estimate onset and how far back
# the scan may reach (see `ravetools::crp`)
detect_onset <- !identical(crp_onset_border, "disabled")
# "earliest_possible" -> earliest available time (clamped into [min(time), t_end]
# by `crp`); "disabled" leaves it NULL since onset is not estimated.
onset_search_start <- switch(
  crp_onset_border,
  "event_onset" = 0,
  "t_start" = crp_time_begin,
  "earliest_possible" = time_range[[1]],
  NULL
)

# CRP needs at least 11 time-points within the detection window
crp_enabled <- isTRUE((crp_time_end - crp_time_begin) * sample_rate > 10)

# Shared arguments for `ravetools::crp()`; reused by every crp() call below.
# Each call supplies its own `x` and `time` via do.call().
crp_settings <- list(
  enabled = crp_enabled,
  args = list(
    t_start = crp_time_begin,
    t_end = crp_time_end,
    time_step = crp_time_step,
    threshold_quantile = crp_threshold_quantile / 100,
    artifact_interval = "tR",
    remove_artifacts = TRUE,
    detect_onset = detect_onset,
    onset_search_start = onset_search_start
  )
)
```



```{r calculating_erp_durations, engine='rave', language = "R", export = "crp_results"}
aligned_array_impl <- aligned_array$`@impl`
dnames <- dimnames(aligned_array_impl)

if (isTRUE(crp_settings$enabled)) {

  cond_groups <- condition_groups_clean$groups

  # ravepipeline::with_rave_parallel({
    crp_results <- ravepipeline::lapply_jobs(dnames$Electrode, function(electrode) {

      aligned_array_impl <- aligned_array$`@impl`

      group_data <- lapply(cond_groups, function(group) {
        # group <- cond_groups[[1]]
        # electrode <- dnames$Electrode[[1]]
        sub_array <- aligned_array_impl[, match(group$trials_included, dnames$Trial),
                                         dnames$Electrode == electrode,
                                         dimnames = NULL, drop = FALSE]
        dm <- dim(sub_array)
        dim(sub_array) <- dm[c(1, 2)]

        crp_result <- do.call(ravetools::crp, c(
          list(x = sub_array, time = dnames$Time),
          crp_settings$args
        ))
        
        # Trim
        crp_result$projections$S_all <- NULL
        crp_result$.data$V <- NULL
        crp_result$parameters$ep <- NULL
        crp_result$parameters$V_tR <- NULL
        
        crp_result$group_index <- group$index
        crp_result$electrode <- electrode
        
        return(crp_result)
        
        # data.frame(
        #   index = group$index,
        #   Electrode = electrode,
        #   # tau = crp_result$tau_R,
        #   Time = crp_result$parameters$params_times,
        #   C = crp_result$parameters$C
        # )
      })
      
      # data.table::rbindlist(group_data)
      
      return(group_data)
    }, .globals = list(
      cond_groups = cond_groups,
      aligned_array = ravepipeline::RAVEFileArray$new(aligned_array_impl),
      dnames = dnames,
      crp_settings = crp_settings
    ), callback = function(e) {
      sprintf("Calculating ERP duration | %s", e)
    })
  # })
  
  # crp_results <- do.call("rbind", crp_results)
} else {
  crp_results <- NULL
}
```

```{r prepare_erp_duration_for_viewer, engine='rave', language = "R", export = "erp_results_for_viewer"}
erp_results_for_viewer <- crp_results
if (length(crp_results)) {
  
  group_indexes <- condition_groups_clean$group_indexes
  group_labels <- condition_groups_clean$group_labels
  
  crp_tbl <- lapply(crp_results, function(group_results) {
    # group_results <- crp_results[[1]]
    # group_result <- group_results[[1]]
    
    group_tbl <- lapply(group_results, function(group_result) {
      label <- group_labels[group_indexes == group_result$group_index]
      data.frame(
        Electrode = group_result$electrode,
        vname = sprintf("%s (%s)", c("t_val", "resp_strength", "var_explain", "tau", "onset"), label),
        value = c(
          group_result$projections$t_value_tR,
          # group_result$projections$p_value_tR,
          mean(abs(group_result$parameters$al_p)),
          mean(group_result$parameters$expl_var),
          group_result$tau_R,
          group_result$tau_onset
        )
      )
    })
    
    data.table::rbindlist(group_tbl)
  })
  crp_tbl <- data.table::rbindlist(crp_tbl)
  
  erp_results_for_viewer <- data.table::dcast(crp_tbl, Electrode ~ vname, value.var = "value")
  erp_results_for_viewer$Subject <- subject$subject_code
}
```

For debug use: show the results on brain

```{r, eval = FALSE}
brain <- ravecore::rave_brain(subject)
brain$set_electrode_values(erp_results_for_viewer)
brain$plot()
```

## Prepare data

Variables: condition group (of trials), channel

Visualizations

- By-channel plot
  - plot ERP for each condition group (time x channel x condition)
  - plot ERP for each trial, grouped by condition group (time x channel x condition*trial) <- needs to think about collapsing... maybe inter-trial phase coherence
- By-condition plot
  - plot each channel (collapse trials) (time x channel x condition)
  - collapse channel - each cond. group is a line
  - plot each trial - collapse channels

### CRP plots by channel

```{r prepare_CRP_response, engine='rave', language = "R", export = "crp_by_channel"}

time_points <- data_placeholder$time_points
samp <- rep(NA_real_, length(time_points))

# Dimension is time x groups x channel
group_data <- lapply(crp_results, function(group_results) {
  
  sapply(group_results, function(group_result) {
    
    samp[time_points %in% group_result$.data$time] <- group_result$parameters$C_full

    # tau_onset is absent when onset detection is disabled
    c(group_result$tau_onset %||% NA_real_,
      group_result$tau_R %||% NA_real_,
      samp)
  })
  
})

group_data <- simplify2array(group_data, higher = TRUE)

# Time, channel, condition group
group_data <- aperm(group_data, c(1, 3, 2))

tau <- group_data[c(1, 2), , , drop = FALSE]
group_data <- group_data[-c(1, 2), , , drop = FALSE]

crp_by_channel <- ravepipeline::pipeline_plot_data(
  x = data_placeholder, name = "crp_by_channel"
)
crp_by_channel$coord_table <- electrode_coordinates
# Electrodes selected for analysis (subset of all loaded channels); used to
# highlight the corresponding channels in the CRP-by-channel plots.
crp_by_channel$analysis_electrodes <- data_placeholder$coord_table$Electrode
crp_by_channel$data <- list(
  canonical = group_data,
  onset = tau[1, , , drop = FALSE],
  offset = tau[2, , , drop = FALSE]
)
```

### `data_by_channel_condition`

For each channel, condition group, collapse over trials

```{r prepare_voltage_over_channel_and_condition_by_collapsing_trials, engine='rave', language = "R", export = "data_by_channel_condition"}
# unwrap the aligned_array
aligned_array_impl <- aligned_array$`@impl`

group_data <- lapply(data_placeholder$groups, function(group) {
  # group <- data_placeholder$groups[[1]]
  sub_array <- subset(
    aligned_array_impl,
    Electrode ~ Electrode %in% analysis_electrodes_clean,
    Trial ~ Trial %in% group$trials_included,
    drop = FALSE
  )
  # Drop dimnames to speed up
  dimnames(sub_array) <- NULL
  
  # # Collapse over trial
  ravetools::collapse(x = sub_array,
                      keep = c(1L, 3L),
                      average = TRUE)
})

# Time x Channel x Group
group_data <- simplify2array(group_data)

data_by_channel_condition <- ravepipeline::pipeline_plot_data(
  x = data_placeholder, name = "data_by_channel_condition"
)
data_by_channel_condition$data <- group_data
```

Visualization:

- ERP collapsed over trials & channels, by condition
- ERP collapsed over trials by channels, per condition

Here "by" means each plot has lines by the variable, and per means different variable are in the different sub-figures. For example, "ERP collapsed over trials by channels, per condition" means the plot is ERP collapsed over trials for each combination of channels and conditions. The number of sub-figures equal to the number of conditions, and each sub-figure has numbers of lines that each line is a channel.

```{r}
# Plot data collapsed over trials & channels, by condition
plot(data_by_channel_condition,
     group_by = "channel",
     channel_annotation = "full")

# Plot data collapsed over trials by channels, per condition
plot(data_by_channel_condition,
     group_by = "condition",
     channel_annotation = "short")

# plot_by_channel_condition(
#   data_by_channel_condition = data_by_channel_condition,
#   group_by = "channel",
#   channel_annotation = "full"
# )
# 
# plot_by_channel_condition(
#   data_by_channel_condition = data_by_channel_condition,
#   group_by = "condition",
#   channel_annotation = "short"
# )
```

### Collapse channels

- By-condition plot
  - plot each trial - collapse channels

```{rave prepare_voltage_collapsed_over_channels_per_condition, export = "data_by_trial_channel_condition"}
# unwrap the aligned_array
aligned_array_impl <- aligned_array$`@impl`

dnames <- dimnames(aligned_array_impl)
trial_numbers <- dnames$Trial

time_points <- data_placeholder$time_points

group_data <- lapply(data_placeholder$groups, function(group) {
  # group <- data_placeholder$groups[[1]]
  sub_array <- subset(
    aligned_array_impl,
    Electrode ~ Electrode %in% analysis_electrodes_clean,
    Trial ~ match(group$trials_included, trial_numbers),
    drop = FALSE
  )
  # Drop dimnames to speed up
  dimnames(sub_array) <- NULL
  
  # Collapse over trial (the trial is sorted by stimuli names)
  voltage_by_trial <- ravetools::collapse(x = sub_array,
                                          keep = c(1L, 2L),
                                          average = TRUE)
  
  if (isTRUE(crp_settings$enabled)) {
    crp_result <- do.call(ravetools::crp, c(
      list(x = voltage_by_trial, time = time_points),
      crp_settings$args
    ))
  } else {
    crp_result <- NULL
  }
  
  # Mean and se of mean
  if (length(crp_result$bad_trials)) {
    bad_trials_index <- crp_result$bad_trials
    bad_trials <- as.integer(group$trials_included[bad_trials_index])
    mean_erp <- rowMeans(voltage_by_trial[, - bad_trials_index, drop = FALSE])
  } else {
    bad_trials <- integer(0L)
    mean_erp <- rowMeans(voltage_by_trial)
  }
  
  return(list(
    voltage = voltage_by_trial,
    mean = mean_erp,
    bad_trials = bad_trials, 
    crp_result = crp_result
  ))
  # return(voltage_by_trial)
})

data_by_trial_channel_condition <- ravepipeline::pipeline_plot_data(
  x = data_placeholder, name = "data_by_trial_channel_condition"
)

data_by_trial_channel_condition$crp_enabled <- isTRUE(crp_settings$enabled)
data_by_trial_channel_condition$data <- group_data
```

```{r}
# or plot(...)
plot(data_by_trial_channel_condition, type = "collapse_trial", cex = 0.9)
plot(data_by_trial_channel_condition, type = "by_trial_line", cex = 0.9)
plot(data_by_trial_channel_condition, type = "by_trial_heatmap", cex = 0.9)
```


### Spectrogram analyses

I decide to hide this part. Users can still use the `ravepipeline` infrastructure to run the analysis by loading the shared environment. However, calculating the spectrogram can be slow, hence I prefer to offloading the analysis to the interactive UI and report system, rather than making them stay in the pipeline

```
env <- pipeline$shared_env()
spectrogram <- env$calculate_spectrogram(
  repository = repository,
  condition_groups = condition_groups,
  channel = analysis_electrodes_clean[[1]]
)

# ITPC
image(
  z = spectrogram$data$itpc[, , 2],
  zlim = c(0, 1),
  x = spectrogram$time_points,
  y = spectrogram$frequencies,
  log = "y"
)

# Power
hmap <- colorRampPalette(ravebuiltins::get_heatmap_palette("BlueWhiteRed"))(101)
plim <- max(abs(range(spectrogram$data$power)))
image(
  z = spectrogram$data$power[, , 2],
  zlim = c(-1, 1) * plim,
  x = spectrogram$time_points,
  y = spectrogram$frequencies,
  col = hmap
)
```


## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-voltage_explorer.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-voltage_explorer.R")
```


Once the pipeline script `make-voltage_explorer.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
# Fixed usage, show pipeline graph
try({
  asNamespace("ravepipeline")$pipeline_dependency_graph(
    pipeline_path = ".", glimpse = TRUE)
}, silent = TRUE)
```



