---
title: "RAVE Pipeline Markdown Template"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
raveio::pipeline_setup_rmd("voltage_explorer")
```


```{rave load_subject, language = "R", export = "subject"}
subject <- raveio::RAVESubject$new(
  project_name = project_name, 
  subject_code = subject_code
)
print(subject)

# List subject details
subject$epoch_names
subject$reference_names
subject$blocks
subject$electrodes
```


```{rave prepare_data_repository, language = "R", export = "repository", cue = "always", format = "rave_prepare_subject_voltage_with_epoch"}
repository <- raveio::prepare_subject_voltage_with_epoch(
  subject = subject,
  electrodes = loaded_electrodes,
  epoch_name = epoch_choice,
  time_windows = c(epoch_choice__trial_starts, epoch_choice__trial_ends),
  reference_name = reference_name
)
```

```{rave clean_analysis_channels, language = "R", export = "analysis_channels_clean"}
available_channels <- repository$electrode_list
analysis_channels_clean <- dipsaus::parse_svec(unlist(analysis_channels))
analysis_channels_clean <- analysis_channels_clean[analysis_channels_clean %in% available_channels]
if(!length(analysis_channels_clean)) {
  stop("No channels selected for analysis. Please specify the electrode channels from the following loaded: ",
       dipsaus::deparse_svec(available_channels))
}
analysis_channels_clean <- sort(analysis_channels_clean)
```

```{rave prepare_pre_analysis_filters, language = "R", export = "pre_analysis_filter_array", format = "filearray", cue = "always"}
pre_analysis_filter_array <- prepare_filtered_data(
  data_path = "data/pre_analysis_filtered_voltage",
  repository = repository,
  filter_configurations = filter_configurations
)
```


```{rave filter_data_for_analysis, language = "R", export = "filtered_array", format = "filearray", cue = "always"}
filtered_channels <- pre_analysis_filter_array$get_header("filtered_channels")
sel <- (
  # User want channels to be analyzed
  repository$electrode_list %in% analysis_channels_clean
) & (
  # Skip cached
  !repository$electrode_list %in% filtered_channels
)

if(any(sel)) {
  # To save time, use filearray's builtin loader to avoid serializing the large arrays
  array_path <- pre_analysis_filter_array$.filebase
  file_info_list <- lapply(repository$voltage$data_list[sel], function(arr) {
    channel <- as.integer(dimnames(arr)$Electrode)
    list(
      channel = channel,
      path = arr$.filebase
    )
  })
  
  raveio::lapply_async(
    x = file_info_list, 
    FUN = function(file_info) {
      # voltage data comes from here
      source_array <- filearray::filearray_load(file_info$path, mode = "readonly")
      
      # save filtered signals to
      target_array <- filearray::filearray_load(array_path, mode = "readwrite")
      
      # filters
      configs <- target_array$get_header("filter_configurations")
      
      # where to save
      channel <- file_info$channel
      idx <- dimnames(target_array)$Electrode == channel
      
      # source dimension
      slice_dim <- dim(source_array)[c(1, 2)]
      
      # source signals
      signals <- source_array[reshape = slice_dim]
      
      # filtered signals
      filtered <- apply_filters_to_signals(
        signals = signals,
        filter_configs = configs
      )
      
      target_array[, , idx] <- filtered
      return(NULL)
    }, 
    callback = function(file_info) {
      sprintf("Applying filter|Channel %s", file_info$channel)
    }
  )
  filtered_channels <- sort(unique(unlist(c(repository$electrode_list[sel], filtered_channels))))
  pre_analysis_filter_array$.mode <- "readwrite"
  pre_analysis_filter_array$set_header("filtered_channels", filtered_channels)
  pre_analysis_filter_array$.mode <- "readonly"
}

filtered_array <- pre_analysis_filter_array
```


```{rave analyze_data, language = "R", export = "analysis_results"}
analysis_ranges <- build_analysis_ranges(repository, analysis_settings)
condition_groups <- build_condition_groups(repository, condition_groupings)
parameter_grid <- build_parameter_grid(condition_groups, analysis_ranges)
parameter_grid$validate()

lapply(parameter_grid$condition_groups, function(condition_group) {
  # condition_group <- parameter_grid$condition_groups[[1]]
  voltage_over_time_per_channel <- prepare_voltage_over_time_per_channel(
    filtered_array = filtered_array,
    condition_group = condition_group,
    channels = analysis_channels_clean
  )
  
  
  
  list(
    voltage_over_time_per_channel = voltage_over_time_per_channel
  )
})


```

## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-voltage_explorer.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-voltage_explorer.R")
```


Once the pipeline script `make-voltage_explorer.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
# Fixed usage, show pipeline graph
try({
  asNamespace("raveio")$pipeline_dependency_graph(
    pipeline_path = ".", glimpse = TRUE)
}, silent = TRUE)
```



