---
title: "RAVE Pipeline Markdown Template"
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: inline
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
ravepipeline::pipeline_setup_rmd("voltage_explorer")
options("rave.debug" = TRUE)
```


## Load data

Initialize subject

```{r load_subject, engine='rave', language = "R", export = "subject"}
subject <- ravecore::new_rave_subject(
  project_name = project_name, 
  subject_code = subject_code
)
print(subject)

# List subject details
subject$epoch_names
subject$reference_names
subject$blocks
dipsaus::deparse_svec(subject$electrodes)
```
Load repository - referenced voltage with trial epochs

```{r prepare_data_repository, engine='rave', language = "R", export = "repository"}
repository <- ravecore::prepare_subject_voltage_with_epochs(
  subject = subject,
  electrodes = loaded_electrodes,
  epoch_name = epoch_choice,
  time_windows = c(epoch_choice__trial_starts, epoch_choice__trial_ends),
  reference_name = reference_name,
  stitch_events = c(
    epoch_choice__trial_starts_rel_to_event,
    epoch_choice__trial_ends_rel_to_event
  ), 
  quiet = TRUE
)
```

Clean the electrode table and subset only loaded channels

```{r get_coordinate_table, engine='rave', export = "electrode_coordinates"}
electrode_coordinates <- load_electrode_coordinates_cleaned(repository)
```

Keeps a copy of loaded LFP channels for future reference

```{r get_loaded_electrodes, engine='rave', export = "loaded_electrodes_clean"}
loaded_electrodes_clean <- filter_electrodes(repository)
```

and the electrode table for LFP channels only (removing auxiliary and micro-wire channels)

```{r get_loaded_electrode_coordinate_table, engine='rave', export = "loaded_electrode_coordinates"}
loaded_electrode_coordinates <- load_electrode_coordinates_cleaned(
  repository = repository,
  electrodes = loaded_electrodes_clean
)
```

Load epoch event column for future data alignment (see target `aligned_array`)

```{r clean_analysis_event, engine='rave', language = "R", export = "analysis_event_colname"}
analysis_event_colname <- repository$epoch$get_event_colname(
  event = analysis_event, missing = "warning")
analysis_event_colname
```


## Signal filters

For visualization purposes, generate the filter in frequency domain. 

```{r diagnose_filters, engine='rave', language="R", export = "filter_freqz"}
# Pre-calculate each frequency filter so its frequency response can be plotted.
# Meta steps (detrend, demean, decimate, baseline) are not filter objects but
# advance the tracked effective sample rate / timepoint count accordingly.
filter_freqz <- get_filter_freqz(
  repository = repository,
  filter_configurations = filter_configurations
)
```

For local debug only: plot the filter in frequency domain

```{r}
if (!is.null(filter_freqz)) {
  plot(filter_freqz, xlim = filter_freqz$xlim)
}
```

Apply the filters

```{r prepare_pre_analysis_filters, engine='rave', language = "R", export = "filtered_array"}
filtered_array <- filter_repository(repository, filter_configurations)
```

Align the arrays by event. When `analysis_event_colname="Time"`, the array needs no shift and the filtered array is aligned array's core, or a new array will be created.

```{r align_to_analysis_event, engine='rave', language = "R", export = "aligned_array"}
aligned_array <- align_trials(filtered_array, analysis_event_colname)
```


## Clean condition groups & generate output placeholder

`condition_groups_clean` is a list with two elements:

* `n`: number of valid condition groups after cleaning;
* `groups`: unnamed list of cleaned group items, each containing `label`
  (auto-filled when missing), `group_index` (original position, used to
  derive a stable color), and `conditions` (unique, in input order).

Groups with empty labels are auto-named (`Group<index>`); groups whose
conditions are empty or do not appear in the epoch are dropped.

```{r clean_condition_groups, engine='rave', language = "R", export = "condition_groups_clean"}
condition_groups_clean <- ravecore::validate_condition_groupings(
  condition_groups,
  epoch = repository$epoch
)
if (!isTRUE(condition_groups_clean$n > 0)) {
  stop("No valid condition group specified. Please check the condition groupings input.")
}
```

Combine `condition_groups_clean` and `aligned_array` to prepare plot data for all channels. If you want to plot single channel results, might need some tweaks

```{r prepare_plot_data_placeholder, engine='rave', export = "data_placeholder", cue = "always"}
data_placeholder <- condition_groups_clean

# unwrap the aligned_array
aligned_array_impl <- aligned_array$`@impl`
dnames <- dimnames(aligned_array_impl)

# Sample rate
data_placeholder$sample_rate <- aligned_array_impl$get_header("sample_rate")

# electrode coordinate table
data_placeholder$loaded_lectrodes <- loaded_electrodes_clean
data_placeholder$coord_table <- loaded_electrode_coordinates

# time points
data_placeholder$time_points <- dnames$Time

# unit
data_placeholder$unit <- NA

# electrodes to plot
data_placeholder$electrode_mask <- loaded_electrodes_clean

# Force the data to update if the array changes
attr(data_placeholder, "signature") <- aligned_array_impl$get_header("signature_filters")
```


## CRP Analysis

Gather CRP analysis parameters

```{r prepare_crp_settings, engine='rave', language = "R", export = "crp_settings"}
crp_settings <- prepare_crp_settings(
  filtered_array = filtered_array,
  crp_detection_window = crp_detection_window,
  crp_time_step = crp_time_step,
  crp_threshold_quantile = crp_threshold_quantile,
  crp_onset_border = crp_onset_border
)
```

Run CRP on all electrodes to parameterize the voltage, estimate canonical shape, and the signal cutoff time points

```{r calculating_erp_durations, engine='rave', language = "R", export = "crp_results"}
crp_results <- run_crp_on_channels(
  aligned_array = aligned_array,
  crp_settings = crp_settings,
  condition_groups_clean = condition_groups_clean
)
```

`crp_results` is hard to organize, use `data.table` to store and manipulate the results

```{r prepare_crp_results_as_table, engine='rave', language = "R", export = "crp_df"}
if (length(crp_results)) {
  crp_df <- crp_results_to_df(crp_results)
} else {
  crp_df <- NULL
}
```

Summarize `crp_df` into an array of channel by condition by statistics

```{r prepare_erp_duration_for_viewer, engine='rave', language = "R", export = "erp_results_for_viewer"}
erp_results_for_viewer <- crp_df
if (length(crp_df)) {
  sub_table <- crp_df[, c(
    "electrode", "group_index", "tau_R", "t_value_tR", "tau_onset",
    "al_mean", "al_p_mean", "snr_mean", "expl_var_mean")]
  
  sub_table$group_index <- condition_groups_clean$group_labels[match(sub_table$group_index, condition_groups_clean$group_indexes)]
  
  
  sub_table <- data.table::melt(sub_table, c("electrode", "group_index"), value.name = "value")
  sub_table <- sub_table[complete.cases(sub_table), ]
  sub_table <- data.table::data.table(
    Electrode = sub_table$electrode,
    vname = sprintf("%s (%s)", sub_table$variable, sub_table$group_index),
    value = sub_table$value
  )
  
  erp_results_for_viewer <- data.table::dcast(sub_table, Electrode ~ vname, value.var = "value")
  erp_results_for_viewer$Subject <- subject$subject_code
}
```

For debug use: show the results on brain

```{r, eval = FALSE}
brain <- ravecore::rave_brain(subject)
brain$set_electrode_values(erp_results_for_viewer)
brain$plot()
```

### CRP parameter per channel x trial

1. coefficient (`alpha`)

```{r prepare_crp_param_alpha, engine='rave', export = "crp_param_alpha"}
crp_param_alpha <- extract_crp_param_per_trial_by_channel(
  crp_df = crp_df,
  name = "al",
  data_placeholder = data_placeholder
)
```


2. fitted amplitude (`alpha_prime`)

```{r prepare_crp_param_alpha, engine='rave', export = "crp_param_alpha"}
crp_param_alpha <- extract_crp_param_per_trial_by_channel(
  crp_df = crp_df,
  name = "al",
  data_placeholder = data_placeholder
)
```



Variables: condition group (of trials), channel

Visualizations

- By-channel plot
  - plot ERP for each condition group (time x channel x condition)
  - plot ERP for each trial, grouped by condition group (time x channel x condition*trial) <- needs to think about collapsing... maybe inter-trial phase coherence
- By-condition plot
  - plot each channel (collapse trials) (time x channel x condition)
  - collapse channel - each cond. group is a line
  - plot each trial - collapse channels

### CRP plots by channel

```{r prepare_CRP_response, engine='rave', language = "R", export = "crp_by_channel"}
crp_by_channel <- prepare_data_crp_by_channel(
  crp_df = crp_results,
  data_placeholder = data_placeholder
)
```

```{r}
plot(crp_by_channel)
plot(crp_by_channel, type = "heatmap")
```

### `data_by_channel_condition`

For each channel, condition group, collapse over trials

```{r prepare_voltage_over_channel_and_condition_by_collapsing_trials, engine='rave', language = "R", export = "data_by_channel_condition"}
data_by_channel_condition <- prepare_data_by_channel_condition(
  aligned_array = aligned_array,
  data_placeholder = data_placeholder
)
```

Visualization:

- ERP collapsed over trials & channels, by condition
- ERP collapsed over trials by channels, per condition

Here "by" means each plot has lines by the variable, and per means different variable are in the different sub-figures. For example, "ERP collapsed over trials by channels, per condition" means the plot is ERP collapsed over trials for each combination of channels and conditions. The number of sub-figures equal to the number of conditions, and each sub-figure has numbers of lines that each line is a channel.

```{r}
# Plot data collapsed over trials & channels, by condition
plot(data_by_channel_condition,
     group_by = "channel",
     channel_annotation = "full")

# Plot data collapsed over trials by channels, per condition
plot(data_by_channel_condition,
     group_by = "condition",
     channel_annotation = "short")

# plot_by_channel_condition(
#   data_by_channel_condition = data_by_channel_condition,
#   group_by = "channel",
#   channel_annotation = "full"
# )
# 
# plot_by_channel_condition(
#   data_by_channel_condition = data_by_channel_condition,
#   group_by = "condition",
#   channel_annotation = "short"
# )
```

### Collapse channels

- By-condition plot
  - plot each trial - collapse channels

<!-- ```{rave prepare_voltage_collapsed_over_channels_per_condition, export = "data_by_trial_channel_condition"}
data_by_trial_channel_condition <- prepare_data_by_trial_channel_condition(
  aligned_array = aligned_array,
  data_placeholder = data_placeholder,
  crp_settings = crp_settings
)
# unwrap the aligned_array
aligned_array_impl <- aligned_array$`@impl`

dnames <- dimnames(aligned_array_impl)
trial_numbers <- dnames$Trial

time_points <- data_placeholder$time_points

group_data <- lapply(data_placeholder$groups, function(group) {
  # group <- data_placeholder$groups[[1]]
  sub_array <- subset(
    aligned_array_impl,
    Electrode ~ Electrode %in% analysis_electrodes_clean,
    Trial ~ match(group$trials_included, trial_numbers),
    drop = FALSE
  )
  # Drop dimnames to speed up
  dimnames(sub_array) <- NULL
  
  # Collapse over trial (the trial is sorted by stimuli names)
  voltage_by_trial <- ravetools::collapse(x = sub_array,
                                          keep = c(1L, 2L),
                                          average = TRUE)
  
  if (isTRUE(crp_settings$enabled)) {
    crp_result <- do.call(ravetools::crp, c(
      list(x = voltage_by_trial, time = time_points),
      crp_settings$args
    ))
  } else {
    crp_result <- NULL
  }
  
  # Mean and se of mean
  if (length(crp_result$bad_trials)) {
    bad_trials_index <- crp_result$bad_trials
    bad_trials <- as.integer(group$trials_included[bad_trials_index])
    mean_erp <- rowMeans(voltage_by_trial[, - bad_trials_index, drop = FALSE])
  } else {
    bad_trials <- integer(0L)
    mean_erp <- rowMeans(voltage_by_trial)
  }
  
  return(list(
    voltage = voltage_by_trial,
    mean = mean_erp,
    bad_trials = bad_trials, 
    crp_result = crp_result
  ))
  # return(voltage_by_trial)
})

data_by_trial_channel_condition <- ravepipeline::pipeline_plot_data(
  x = data_placeholder, name = "data_by_trial_channel_condition"
)

data_by_trial_channel_condition$crp_enabled <- isTRUE(crp_settings$enabled)
data_by_trial_channel_condition$data <- group_data
```

# ```{r}
# or plot(...)
plot(data_by_trial_channel_condition, type = "collapse_trial", cex = 0.9)
plot(data_by_trial_channel_condition, type = "by_trial_line", cex = 0.9)
plot(data_by_trial_channel_condition, type = "by_trial_heatmap", cex = 0.9)
<!-- ``` -->


### Spectrogram analyses

I decide to hide this part. Users can still use the `ravepipeline` infrastructure to run the analysis by loading the shared environment. However, calculating the spectrogram can be slow, hence I prefer to offloading the analysis to the interactive UI and report system, rather than making them stay in the pipeline

```
env <- pipeline$shared_env()
spectrogram <- env$calculate_spectrogram(
  repository = repository,
  condition_groups = condition_groups,
  channel = analysis_electrodes_clean[[1]]
)

# ITPC
image(
  z = spectrogram$data$itpc[, , 2],
  zlim = c(0, 1),
  x = spectrogram$time_points,
  y = spectrogram$frequencies,
  log = "y"
)

# Power
hmap <- colorRampPalette(ravebuiltins::get_heatmap_palette("BlueWhiteRed"))(101)
plim <- max(abs(range(spectrogram$data$power)))
image(
  z = spectrogram$data$power[, , 2],
  zlim = c(-1, 1) * plim,
  x = spectrogram$time_points,
  y = spectrogram$frequencies,
  col = hmap
)
```


## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-voltage_explorer.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-voltage_explorer.R")
```


Once the pipeline script `make-voltage_explorer.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
# Fixed usage, show pipeline graph
try({
  asNamespace("ravepipeline")$pipeline_dependency_graph(
    pipeline_path = ".", glimpse = TRUE)
}, silent = TRUE)
```



