---
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
    toc_depth: 3
    df_print: kable
    theme: spacelab
editor_options:
  chunk_output_type: console
params:
  electrode_mask: ~
  time_range: ~
  vertical_marks: 0
  cex: ~
  channel_annotation: ~
  trial_sort_by: ~
  plot_space: ~
  plot_space_is_percentile: ~
  crp_annotations: ~
  crp_scale_back: ~
  flip_y: ~
  discrete_colormap: ~
  continuous_colormap: ~
---

```{r setup, include=FALSE}
# require(knitr)
require(ravetools)
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = NA,
  rows.print = 10,
  fig.width = 12
)
options(rmarkdown.df_print = "paged")

# Load pipeline
pipeline <- ravepipeline::pipeline_from_path(".")

shared_env <- pipeline$shared_env()
settings <- pipeline$get_settings()

# mount inputs to global environment
list2env(settings, envir = globalenv())
list2env(as.list(shared_env), envir = globalenv())

# Evaluate to get the repository and every by-channel result. Every channel is
# analyzed; `electrode_mask` only decides what gets drawn, so this runs once for
# the whole report rather than once per electrode.
pipeline$run(
  scheduler = "none",
  type = "smart",
  names = c(
    "repository",
    "filter_freqz",
    "condition_groups_clean",
    "filtered_array",
    "aligned_array",
    "crp_settings",
    "crp_results",
    "erp_results_for_viewer",
    "data_placeholder",
    "loaded_electrodes_clean",
    "data_by_channel_condition",
    "data_crp_by_channel",
    "data_crp_param_alpha_prime",
    "data_crp_param_snr",
    "data_crp_param_expl_var"
  ),
  return_values = FALSE
)

repository <- pipeline$read("repository")
brain <- ravecore::rave_brain(repository$subject)
filter_freqz <- pipeline$read(var_names = "filter_freqz")
erp_results_for_viewer <- pipeline$read(var_names = "erp_results_for_viewer")
erp_results_for_viewer <- as.data.frame(erp_results_for_viewer)
condition_groups_clean <- pipeline$read("condition_groups_clean")
data_by_channel_condition <- pipeline$read(var_names = "data_by_channel_condition")
data_crp_by_channel <- pipeline$read(var_names = "data_crp_by_channel")
data_crp_param_alpha_prime <- pipeline$read(var_names = "data_crp_param_alpha_prime")
data_crp_param_snr <- pipeline$read(var_names = "data_crp_param_snr")
data_crp_param_expl_var <- pipeline$read(var_names = "data_crp_param_expl_var")
```

```{r resolve_report_options, include=FALSE}
# `electrode_mask` is what every `plot_data_*()` calls it: a plot-time channel
# selection, not a pipeline input. Nothing downstream of the pipeline depends on
# it, so the report never writes it back into the settings.
electrode_mask <- params$electrode_mask
if (length(electrode_mask)) {
  electrode_mask <- dipsaus::parse_svec(electrode_mask)
}
if (!length(electrode_mask)) {
  electrode_mask <- repository$electrode_list
}
# Restrict to the loaded LFP channels the caller asked for
electrode_mask <- sort(intersect(electrode_mask,
                                 pipeline$read("loaded_electrodes_clean")))

# A param left unset falls back to the user's stored preference. Reading is all
# the report may do: `use_*(value)` writes `value` into the *global* on-disk
# preference store, and a background report job has no business rewriting the
# user's settings. `fallback` stays a promise, so a preference is only read when
# it is actually needed.
param_or <- function(value, fallback) {
  if (length(value) && !all(is.na(value))) { return(value) }
  fallback
}

# Which graphics options the caller actually supplied. Recorded so the
# Parameters section below can say where each value came from.
GRAPHICS_OPTIONS <- c(
  "cex", "channel_annotation", "trial_sort_by", "plot_space",
  "plot_space_is_percentile", "crp_annotations", "crp_scale_back",
  "flip_y", "discrete_colormap", "continuous_colormap"
)
param_supplied <- vapply(GRAPHICS_OPTIONS, function(nm) {
  value <- params[[nm]]
  isTRUE(length(value) > 0 && !all(is.na(value)))
}, FALSE)

# A colormap preference stores a palette *name*, so the param is a name too.
# An unknown one warns and falls back rather than aborting the whole report.
resolve_colormap_name <- function(value, fallback, choices, what) {
  name <- as.character(param_or(value, fallback))[[1]]
  if (isTRUE(name %in% choices)) { return(name) }
  warning(sprintf(
    "Unknown %s colormap `%s`; using `%s` instead. Available: %s",
    what, name, fallback, paste(choices, collapse = ", ")
  ))
  fallback
}

time_range <- params$time_range %||% c(NA, NA)
if (length(time_range) != 2 || all(is.na(time_range))) {
  time_range <- c(NA, NA)
}
vertical_marks <- as.numeric(params$vertical_marks %||% 0)

cex <- as.numeric(param_or(params$cex, use_cex()))
channel_annotation_style <- match.arg(
  as.character(param_or(params$channel_annotation, use_channel_annotation_style())),
  choices = OPTIONS_CHAN_ANNOT
)
trial_sort_by <- match.arg(
  as.character(param_or(params$trial_sort_by, use_trial_sort_by())),
  choices = OPTIONS_TRIAL_SORT
)

# The stored spacing is a percentage in percentile mode and micro-volts
# otherwise; `resolve_plot_space()` owns that conversion and, unlike
# `use_plot_space(value)`, takes an override without persisting it.
plot_space_value <- max(0, as.numeric(param_or(params$plot_space, use_plot_space())))
plot_space_is_pct <- isTRUE(as.logical(
  param_or(params$plot_space_is_percentile, use_plot_space_is_percentile())))
by_elec_space <- resolve_plot_space(plot_space_value, plot_space_is_pct)

crp_annotations <- isTRUE(as.logical(
  param_or(params$crp_annotations, use_show_crp_decoration())))
crp_scale_back <- isTRUE(as.logical(
  param_or(params$crp_scale_back, use_crp_scale_back())))
flip_y <- isTRUE(as.logical(param_or(params$flip_y, use_flipped_y())))

discrete_colormap_name <- resolve_colormap_name(
  params$discrete_colormap, use_discrete_colormap()$name,
  names(ravepipeline::DISCRETE_COLORMAPS(preview = FALSE)), "discrete")
continuous_colormap_name <- resolve_colormap_name(
  params$continuous_colormap, use_continuous_colormap()$name,
  names(ravepipeline::CONTINUOUS_COLORMAPS(preview = FALSE)), "continuous")

discrete_colors <- ravepipeline::DISCRETE_COLORMAPS(discrete_colormap_name)
continuous_colors <- ravepipeline::CONTINUOUS_COLORMAPS(continuous_colormap_name)

# A rejected colormap param fell back to the preference, so the Parameters table
# below must not go on crediting the param it refused
param_supplied[["discrete_colormap"]] <- identical(
  discrete_colormap_name, as.character(params$discrete_colormap %||% "")[[1]])
param_supplied[["continuous_colormap"]] <- identical(
  continuous_colormap_name, as.character(params$continuous_colormap %||% "")[[1]])
```

```{r figure_helpers, include=FALSE}
# Historical report sizing: 0.3in of drawing height per stacked channel, per
# panel row. `asp` must match the `get_mfrow()` call inside the plot function
# being sized -- 4 for `plot_data_by_channel_condition_multiline()`, 3 for every
# other by-channel figure.
fig_height_by_channel <- function(asp = 3, per_channel = 0.3, max_height = 60) {
  n_rows <- get_mfrow(n = condition_groups_clean$n, mfrow = NULL, asp = asp)[[1]]
  min(max(n_rows * per_channel * length(electrode_mask), 4), max_height)
}

# Per-electrode figure heights: the overlay is a single panel, the two trial
# figures are one panel per condition group.
fig_height_electrode_overlay <- 4.5
fig_height_electrode_trial <-
  get_mfrow(n = condition_groups_clean$n, mfrow = NULL, asp = 3)[[1]] * 4

# The resolved options bound once, so the per-electrode loop and its child
# template stay readable.
plot_electrode_overlay <- function(electrode) {
  plot_data_by_channel_condition_overlay(
    x                  = data_by_channel_condition,
    electrode_mask     = electrode,
    channel_annotation = channel_annotation_style,
    cex                = cex,
    vertical_marks     = vertical_marks,
    time_range         = time_range,
    space              = by_elec_space$space,
    space_mode         = by_elec_space$space_mode,
    col                = discrete_colors,
    flip_y             = flip_y
  )
}

plot_electrode_butterfly <- function(x) {
  plot_data_by_trial_channel_condition_butterfly(
    x              = x,
    vertical_marks = vertical_marks,
    crp            = crp_annotations,
    time_range     = time_range,
    cex            = cex,
    space          = by_elec_space$space,
    space_mode     = by_elec_space$space_mode
  )
}

plot_electrode_heatmap <- function(x) {
  plot_data_by_trial_channel_condition_heatmap(
    x              = x,
    sort_by        = trial_sort_by,
    space          = by_elec_space$space,
    space_mode     = by_elec_space$space_mode,
    time_range     = time_range,
    cex            = cex,
    crp            = crp_annotations,
    col            = continuous_colors,
    vertical_marks = vertical_marks
  )
}
```

---
title: "Subject (Univariate) Voltage Analysis Report"
date: |
  Project & subject: ``r repository$subject$subject_id`` <br />
  <small><i>
    Generated by  [RAVE](https://rave.wiki) at `r format(Sys.time(), '%a %X, %b %d, %Y')`
  </i></small>
---


## Parameters

Everything needed to reproduce this report: the pipeline inputs it was run with,
the graphics options it was rendered with, the signal filters that were applied,
and the condition groups the trials were split into.

### Pipeline settings

```{r}
# `condition_groups` and `filter_configurations` are nested and get tables of
# their own below
settings_display <- settings[
  !names(settings) %in% c("condition_groups", "filter_configurations")]
settings_display <- settings_display[!vapply(
  settings_display, function(v) { inherits(v, "key_missing") }, FALSE)]
settings_display <- settings_display[order(names(settings_display))]

knitr::kable(
  caption = "Pipeline inputs (`settings.yaml`)",
  row.names = FALSE,
  data.frame(
    check.names = FALSE,
    row.names = NULL,
    Setting = names(settings_display),
    Value = vapply(settings_display, function(v) {
      v <- unlist(v)
      if (!length(v)) { return("") }
      paste(format(v, trim = TRUE), collapse = ", ")
    }, "")
  )
)
```

### Report options

```{r}
# Where each option came from: a value the caller passed to the report, or the
# user preference it fell back to
option_source <- function(name) {
  if (isTRUE(param_supplied[[name]])) { "report parameter" } else { "user preference" }
}

knitr::kable(
  caption = "Report parameters and graphics options",
  row.names = FALSE,
  data.frame(
    check.names = FALSE,
    row.names = NULL,
    Option = c("electrode_mask", "time_range", "vertical_marks", GRAPHICS_OPTIONS),
    Value = c(
      dipsaus::deparse_svec(electrode_mask),
      paste(ifelse(is.na(time_range), "auto", format(time_range)), collapse = " ~ "),
      paste(vertical_marks, collapse = ", "),
      format(cex),
      channel_annotation_style,
      trial_sort_by,
      format(plot_space_value),
      format(plot_space_is_pct),
      format(crp_annotations),
      format(crp_scale_back),
      format(flip_y),
      discrete_colormap_name,
      continuous_colormap_name
    ),
    Source = c(
      if (length(params$electrode_mask)) { "report parameter" } else { "all loaded channels" },
      if (length(params$time_range)) { "report parameter" } else { "full epoch" },
      "report parameter",
      unname(vapply(GRAPHICS_OPTIONS, option_source, ""))
    )
  )
)
```

### Signal filters

```{r}
filter_configurations <- as.list(settings$filter_configurations)

if (length(filter_configurations)) {
  knitr::kable(
    caption = "Filters applied, in order",
    row.names = FALSE,
    do.call(rbind, lapply(seq_along(filter_configurations), function(ii) {
      config <- as.list(filter_configurations[[ii]])
      type <- as.character(config$type %||% "")
      config$type <- NULL
      data.frame(
        check.names = FALSE,
        row.names = NULL,
        Step = ii,
        Type = type,
        Parameters = if (length(config)) {
          paste(sprintf("%s = %s", names(config), vapply(config, function(v) {
            paste(unlist(v), collapse = ", ")
          }, "")), collapse = "; ")
        } else { "" }
      )
    }))
  )
}
```

```{r}
# `xlim` is the pass/stop band range `get_filter_freqz()` tracked while building
# the filters -- without it the response is drawn over the full Nyquist range
# and the configured band is a sliver
if (!is.null(filter_freqz)) {
  plot(filter_freqz, xlim = filter_freqz$xlim)
  print(filter_freqz)
}
```

### Condition groups

```{r}
knitr::kable(caption = "Condition group settings", data.frame(
  Index = condition_groups_clean$group_indexes,
  Label = condition_groups_clean$group_labels,
  Trials = condition_groups_clean$n_trials,
  Conditions = vapply(condition_groups_clean$groups, function(group) {
    paste(group$conditions, collapse = ", ")
  }, "")
))
```

## Canonical response statistics

```{r, results='asis'}
# Generated from `CRP_VIEWER_METRICS`, the single source of truth for which
# metrics reach the viewer and how they are described, so this list cannot drift
# out of step with the columns below
cat(sprintf("* `%s`: %s\n", names(CRP_VIEWER_METRICS),
            unlist(CRP_VIEWER_METRICS, use.names = FALSE)), sep = "")
```

<button class="btn btn-primary btn-xs collapsed" data-toggle="collapse" data-target="#htmlwidget_container" aria-expanded="false"> Show/Hide 3D Viewer </button>

```{r}
#| layout: l-screen-insert-right
#| fig.align: center
#| fig.width: 10

if (!is.null(brain)) {

  controllers <- list()
  brain$set_electrode_values(erp_results_for_viewer)

  nms <- names(erp_results_for_viewer)
  nms <- nms[startsWith(nms, "t_proj")]
  if (length(nms)) {
    controllers[["Display Data"]] <- nms[[1]]
  }

  brain$plot(
    control_display = FALSE,
    side_display = FALSE,
    cex = 7 / 8,
    start_zoom = 7 / 8,
    width = '100%',
    height = '600px',
    controllers = controllers
  )
}


```

### Results table

```{r}
#| layout: l-screen-insert-right

# Same numbers the viewer paints on the electrodes, laid out metric-major with
# one sub-column per condition. The layout, the two-row header sketch and the
# per-metric precision all come from `shared-viewer_table.R`, which is what the
# module's own "Results Table" tab uses -- so the two cannot drift apart.
erp_tbl <- erp_results_for_viewer[
  erp_results_for_viewer$Electrode %in% electrode_mask, , drop = FALSE]

layout <- crp_viewer_table_layout(names(erp_tbl))

# A metric can be absent for some conditions (e.g. `onset` when CRP onset
# detection is disabled); fill so the header stays rectangular
for (nm in setdiff(layout$columns, names(erp_tbl))) {
  erp_tbl[[nm]] <- NA_real_
}

electrode_table <- repository$electrode_table
labels <- as.character(electrode_table$Label)[
  match(erp_tbl$Electrode, electrode_table$Electrode)]

leading <- data.frame(
  check.names = FALSE,
  stringsAsFactors = FALSE,
  Electrode = erp_tbl$Electrode,
  Label = labels
)
leading_names <- names(leading)
tbl <- cbind(leading, erp_tbl[, layout$columns, drop = FALSE])

# Precision is decided per metric group over all of its conditions pooled, so
# the conditions of one metric stay aligned instead of each column picking its
# own decimals
digits_by_group <- vapply(layout$groups, function(group) {
  crp_viewer_table_digits(unlist(tbl[, group$columns, drop = FALSE]))
}, integer(1L))

# The vertical rule between metric groups is drawn on the first column of each
# group; the header side of it comes from the container sketch
group_starts <- vapply(layout$groups, function(group) {
  group$columns[[1L]]
}, character(1L))

datatable_options <- list(
  # No `l`/`p` in `dom`: every selected electrode is listed at once, so there is
  # no page-length menu or pager to show. `scrollY` keeps that list from running
  # away with the page -- in the module this table lives in its own scrolling
  # tab, here it has to make its own.
  dom = "Bfrti",
  buttons = list(
    list(extend = "copy", text = "Copy", title = ""),
    list(extend = "csv", text = "CSV", title = "",
         filename = "voltage-explorer-crp-results")
  ),
  scrollX = TRUE,
  scrollY = "70vh",
  scrollCollapse = TRUE,
  fixedColumns = list(leftColumns = length(leading_names)),
  paging = FALSE,
  columnDefs = list(list(className = "dt-center", targets = "_all"))
)

if (length(layout$groups)) {
  dt <- DT::datatable(
    tbl,
    rownames = FALSE,
    container = crp_viewer_table_container(layout, leading_names),
    extensions = c("FixedColumns", "Buttons"),
    options = datatable_options
  )
} else {
  # No metric columns to group; a grouped header would be malformed
  dt <- DT::datatable(
    tbl,
    rownames = FALSE,
    extensions = c("FixedColumns", "Buttons"),
    options = datatable_options
  )
}

# `DT::formatRound()` takes one `digits` per call, so one call per distinct
# precision. Only metric columns are touched, so `Electrode` -- an identifier
# rather than a measurement -- stays unrounded.
for (digits in unique(digits_by_group)) {
  columns <- unlist(
    lapply(layout$groups[digits_by_group == digits], `[[`, "columns"),
    use.names = FALSE
  )
  dt <- DT::formatRound(dt, columns = columns, digits = digits)
}

if (length(group_starts)) {
  dt <- DT::formatStyle(dt, columns = group_starts,
                        `border-left` = "1px solid #adb5bd")
}
dt
```

## Mean ERP by channel

Voltage averaged over the trials of each condition group.

### Stacked traces

```{r, fig.width=12, fig.height = fig_height_by_channel(asp = 4)}
plot_data_by_channel_condition_multiline(
  x                  = data_by_channel_condition,
  electrode_mask     = electrode_mask,
  channel_annotation = channel_annotation_style,
  cex                = cex,
  vertical_marks     = vertical_marks,
  time_range         = time_range,
  space              = by_elec_space$space,
  space_mode         = by_elec_space$space_mode,
  col                = discrete_colors,
  flip_y             = flip_y
)
```

### Heat map

```{r, fig.width=12, fig.height = fig_height_by_channel(asp = 3)}
plot_data_by_channel_condition_heatmap(
  x                  = data_by_channel_condition,
  electrode_mask     = electrode_mask,
  channel_annotation = channel_annotation_style,
  cex                = cex,
  vertical_marks     = vertical_marks,
  time_range         = time_range,
  space              = by_elec_space$space,
  space_mode         = by_elec_space$space_mode,
  col                = continuous_colors,
  flip_y             = flip_y
)
```

## ERP canonical responses

The canonical shape `CRP` fitted to each channel, per condition group.

### Stacked traces

```{r, fig.width=12, fig.height = fig_height_by_channel(asp = 3)}
plot_data_crp_by_channel_multiline(
  x                  = data_crp_by_channel,
  electrode_mask     = electrode_mask,
  channel_annotation = channel_annotation_style,
  cex                = cex,
  crp                = crp_annotations,
  vertical_marks     = vertical_marks,
  time_range         = time_range,
  space              = by_elec_space$space,
  space_mode         = by_elec_space$space_mode,
  col                = discrete_colors,
  flip_y             = flip_y,
  scale_back         = crp_scale_back
)
```

### Heat map

```{r, fig.width=12, fig.height = fig_height_by_channel(asp = 3)}
plot_data_crp_by_channel_heatmap(
  x                  = data_crp_by_channel,
  electrode_mask     = electrode_mask,
  channel_annotation = channel_annotation_style,
  cex                = cex,
  crp                = crp_annotations,
  vertical_marks     = vertical_marks,
  time_range         = time_range,
  space              = by_elec_space$space,
  space_mode         = by_elec_space$space_mode,
  col                = continuous_colors,
  flip_y             = flip_y,
  scale_back         = crp_scale_back
)
```

## Trial-level CRP parameters

Each `CRP` fit parameter as a trial by channel heat map, one panel per condition
group, with the per-channel mean and its standard error alongside.

```{r, include=FALSE}
plot_crp_param <- function(x) {
  plot_data_crp_param_by_trial_channel_heatmap(
    x                  = x,
    electrode_mask     = electrode_mask,
    sort_by            = trial_sort_by,
    channel_annotation = channel_annotation_style,
    cex                = cex,
    space              = by_elec_space$space,
    space_mode         = by_elec_space$space_mode,
    col                = continuous_colors
  )
}
```

### Fitted amplitude (`al_p`)

```{r, fig.width=12, fig.height = fig_height_by_channel(asp = 3)}
plot_crp_param(data_crp_param_alpha_prime)
```

### Signal-to-noise ratio (`snr`)

```{r, fig.width=12, fig.height = fig_height_by_channel(asp = 3)}
plot_crp_param(data_crp_param_snr)
```

### Variance explained (`expl_var`)

```{r, fig.width=12, fig.height = fig_height_by_channel(asp = 3)}
plot_crp_param(data_crp_param_expl_var)
```

## Per-electrode results

```{r, message=FALSE, warning=FALSE, results='asis', fig.show='asis'}
# The pipeline already ran over every channel; per-electrode figures are a
# plot-time mask (`data_by_channel_condition`) or a cheap single-channel
# extraction (`prepare_data_by_trial_channel_condition()`) -- no pipeline re-run
# inside this loop.
aligned_array <- pipeline$read("aligned_array")
data_placeholder <- pipeline$read("data_placeholder")
crp_settings <- pipeline$read("crp_settings")

# The three figures need different heights -- the overlay is one panel, the two
# trial figures are one panel per condition group -- and a chunk option applies
# to every figure in its chunk. So each electrode is knitted as a child document
# instead, which gives every figure a chunk of its own. The chunks are left
# unlabelled so knitr's auto-labelling keeps them unique across iterations.
per_electrode_template <- c(
  "### Electrode {{electrode}} - {{label}}",
  "",
  "```{r, fig.width=12, fig.height={{h_overlay}}}",
  "plot_electrode_overlay({{electrode}})",
  "```",
  "",
  "```{r, fig.width=12, fig.height={{h_trial}}}",
  "plot_electrode_butterfly(elec_data)",
  "```",
  "",
  "```{r, fig.width=12, fig.height={{h_trial}}}",
  "plot_electrode_heatmap(elec_data)",
  "```",
  ""
)

for (electrode in electrode_mask) {
  row <- repository$electrode_table[
    repository$electrode_table$Electrode == electrode, ]

  elec_data <- prepare_data_by_trial_channel_condition(
    electrode = electrode,
    aligned_array = aligned_array,
    data_placeholder = data_placeholder,
    crp_settings = crp_settings
  )

  cat(knitr::knit_child(
    text = knitr::knit_expand(
      text = per_electrode_template,
      electrode = electrode,
      label = as.character(row$Label),
      h_overlay = fig_height_electrode_overlay,
      h_trial = fig_height_electrode_trial
    ),
    quiet = TRUE,
    envir = environment()
  ), sep = "\n")
}
```
