---
output: 
  html_document: 
    toc: true
    toc_float: 
      collapsed: true
    toc_depth: 3
    df_print: kable
    theme: spacelab
editor_options: 
  chunk_output_type: console
params:
  analysis_electrodes: ~
  time_range: ~
  crp_annotations: yes
  vertical_marks: 0
---

```{r setup, include=FALSE}
# require(knitr)
require(ravetools)
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = NA,
  rows.print = 10,
  fig.width = 12
)
options(rmarkdown.df_print = "paged")

# Load pipeline
pipeline <- ravepipeline::pipeline_from_path(".")
repository <- pipeline$run("repository")

analysis_electrodes <- params$analysis_electrodes
if (length(analysis_electrodes)) {
  analysis_electrodes <- dipsaus::parse_svec(params$analysis_electrodes)
}

if (!length(analysis_electrodes)) {
  analysis_electrodes <- repository$electrode_list
}
pipeline$set_settings(
  analysis_electrodes = dipsaus::deparse_svec(analysis_electrodes)
)

shared_env <- pipeline$shared_env()
settings <- pipeline$get_settings()
# pipeline$clean()

# mount inputs to global environment
list2env(settings, envir = globalenv())
list2env(as.list(shared_env), envir = globalenv())

# Evaluate to get the repository and omnibus_results
pipeline$run(
  scheduler = "none",
  type = "smart",
  names = c(
    "repository",
    "condition_groups_clean",
    "filtered_array",
    "crp_results",
    "erp_results_for_viewer",
    "data_placeholder",
    "analysis_electrodes_clean",
    "crp_by_channel"
  ),
  return_values = FALSE
)


repository <- pipeline$read("repository")
brain <- ravecore::rave_brain(repository$subject)
erp_results_for_viewer <- pipeline$read(var_names = "erp_results_for_viewer")
erp_results_for_viewer <- as.data.frame(erp_results_for_viewer)
analysis_electrodes <- pipeline$read("analysis_electrodes_clean")
condition_groups_clean <- pipeline$read("condition_groups_clean")
crp_by_channel <- pipeline$read(var_names = "crp_by_channel")
mfrow <- get_mfrow(n = condition_groups_clean$n, mfrow = NULL, asp = 3)

crp_fig_ratio <- mfrow[[1]] * nrow(crp_by_channel$coord_table) / 40
```

```{r, handle_params_if_missing, include=FALSE}
# `%||%` is a base R operator since 4.0
# plots_to_include <- params$plots_to_include %||% c(
#   "over_time_by_electrode",
#   "by_frequency_over_time",
#   "over_time_by_trial",
#   "over_time_by_condition"
# )
# 
time_range <- params$time_range %||% c(NA, NA)
if (length(time_range) != 2 || all(is.na(time_range))) {
  time_range <- c(NA, NA)
}
crp_annotations <- isTRUE(as.logical(params$crp_annotations))
vertical_marks <- as.numeric(params$vertical_marks %||% 0)

channel_annotation_style <- use_channel_annotation_style()
cex <- use_cex()
trial_sort_by <- use_trial_sort_by()

space <- max(0, min(use_plot_space(), 1))
if (isTRUE(use_plot_space_is_percentile())) {
  by_elec_space <- list(space = space, space_mode = "quantile")
} else {
  by_elec_space <- list(space = space, space_mode = "absolute")
}
```

---
title: "Subject (Univariate) Voltage Analysis Report"
date: |
  Project & subject: ``r repository$subject$subject_id`` <br />
  <small><i>
    Generated by  [RAVE](https://rave.wiki) at `r format(Sys.time(), '%a %X, %b %d, %Y')` 
  </i></small>
---


## Filters


```{r}
try({
  filter_freqz <- pipeline$run("filter_freqz")
  plot(filter_freqz)
  print(filter_freqz)
})
```

## Condition groups

```{r}
knitr::kable(caption = "Condition group settings", data.frame(
  Index = condition_groups_clean$group_indexes,
  Label = condition_groups_clean$group_labels,
  Trials = condition_groups_clean$n_trials,
  Conditions = vapply(condition_groups_clean$groups, function(group) {
    paste(group$conditions, collapse = ", ")
  }, "")
))
```

## Canonical response statistics

* `t_val`: statistics on whether ERP is significant
* `resp_strength`: average response strength in micro-volts compared to canonical shape
* `tau`: estimated ERP offset (in seconds)
* `var_explain`: $R^2$ canonical shape vs the total trial variation


<button class="btn btn-primary btn-xs collapsed" data-toggle="collapse" data-target="#htmlwidget_container" aria-expanded="false"> Show/Hide 3D Viewer </button>  

```{r}
#| layout: l-screen-insert-right
#| fig.align: center
#| fig.width: 10

if (!is.null(brain)) {
  
  controllers <- list()
  brain$set_electrode_values(erp_results_for_viewer)
  
  nms <- names(erp_results_for_viewer)
  nms <- nms[startsWith(nms, "t_val")]
  if (length(nms)) {
    controllers[["Display Data"]] <- nms[[1]]
  }
  
  brain$plot(
    control_display = FALSE,
    side_display = FALSE,
    cex = 7 / 8,
    start_zoom = 7 / 8,
    width = '100%',
    height = '600px',
    controllers = controllers
  )
}


```

```{r}
#| layout: l-screen-insert-right
#| rows.print: 10

nms <- names(erp_results_for_viewer)
nms <- unique(c(
  "Subject", "Electrode",
  nms[startsWith(nms, "t_val")], 
  nms[startsWith(nms, "resp_strength")], 
  nms[startsWith(nms, "tau")], 
  nms))
df <- as.data.frame(structure(
  names = nms,
  lapply(nms, function(nm) {
    if (nm %in% c("Electrode", "Subject")) {
      return(erp_results_for_viewer[[nm]])
    } else {
      x <- erp_results_for_viewer[[nm]]
      if (is.numeric(x)) {
        return(round(x, 2))
      }
      return(x)
    }
  })
))
names(df) <- nms
# Define your stats and conditions
is_grouped <- grepl("\\(", nms)
stat_name  <- sub(" \\(.*\\)$", "", nms)
condition  <- sub(".*\\((.*)\\)$", "\\1", nms)

top_row    <- list()
bottom_row <- list()
group_start_cols <- c()

border_style <- "border-left: 2px solid #aaa;"

i <- 1
while (i <= length(nms)) {
  if (!is_grouped[i]) {
    top_row[[length(top_row) + 1]] <- htmltools::tags$th(rowspan = 2, nms[i])
    i <- i + 1
  } else {
    s <- stat_name[i]
    j <- i
    while (j <= length(nms) && is_grouped[j] && stat_name[j] == s) j <- j + 1

    # border on the group header
    top_row[[length(top_row) + 1]] <- htmltools::tags$th(
      colspan = j - i, s, style = border_style
    )
    group_start_cols <- c(group_start_cols, nms[i])

    for (k in i:(j - 1)) {
      # border only on the first sub-column of each group
      bdr <- if (k == i) border_style else NULL
      bottom_row[[length(bottom_row) + 1]] <- htmltools::tags$th(
        condition[k], style = bdr
      )
    }
    i <- j
  }
}

sketch <- htmltools::withTags(table(
  thead(
    tr(top_row),
    tr(bottom_row)
  )
))

# Pre-round floats in R
df_display <- df
float_cols <- sapply(df, is.numeric) & !sapply(df, is.integer)
df_display[float_cols] <- lapply(df_display[float_cols], round, digits = 2)

DT::formatStyle(
  DT::datatable(
    df_display,
    container = sketch,
    options = list(scrollX = TRUE, columnDefs = list(
      list(targets = "_all", className = "dt-center")
    )),
    rownames = FALSE
  ),
  columns = group_start_cols,
  `border-left` = "2px solid #aaa"
)
```

## ERP canonical responses

<details>
  <summary>Multi-line plot:</summary>
  
```{r, fig.width=12, fig.height = crp_fig_ratio * 12}


# CRP canonical responses are normalized, so an absolute (uV) spacing is
# meaningless; fall back to the full quantile range in that case.
if (!isTRUE(use_plot_space_is_percentile())) {
  plot_space <- list(space = 1, space_mode = "quantile")
} else {
  space <- max(0, min(use_plot_space(), 1))
  plot_space <- list(space = space, space_mode = "quantile")
}
plot_crp_by_channel_multilines(
  crp_by_channel     = crp_by_channel,
  channel_annotation = channel_annotation_style,
  cex                = cex,
  crp                = crp_annotations,
  vertical_marks     = vertical_marks,
  time_range         = time_range,
  space              = plot_space$space,
  space_mode         = plot_space$space_mode
)
```

</details>

<details>
  <summary>Heat-map plot:</summary>
  

```{r, fig.width=12, fig.height = crp_fig_ratio * 12}
plot_crp_by_channel_heatmap(
  crp_by_channel     = crp_by_channel,
  channel_annotation = channel_annotation_style,
  cex                = cex,
  crp                = crp_annotations,
  vertical_marks     = vertical_marks,
  time_range         = time_range,
  space              = plot_space$space,
  space_mode         = plot_space$space_mode
)
```

</details>

## Per-electrode results

```{r, message=FALSE, warning=FALSE, results='asis', fig.show='asis'}
figure_root <- ravepipeline::dir_create2(file.path(pipeline$pipeline_path, "figures"))

for (electrode in analysis_electrodes) {
  row <- repository$electrode_table[
    repository$electrode_table$Electrode == electrode, ]
  pipeline$set_settings(analysis_electrodes = electrode)
  
  results <- pipeline$run(c(
    "data_by_channel_condition",
    "data_by_trial_channel_condition"
  ))
  data_by_channel_condition <- results$data_by_channel_condition
  data_by_trial_channel_condition <- results$data_by_trial_channel_condition
  
  cat(sprintf("\n\n### Electrode %d - %s\n\n", electrode, row$Label))
  
  plot_by_channel_condition(
    data_by_channel_condition,
    group_by           = "channel",
    channel_annotation = channel_annotation_style,
    cex                = cex,
    vertical_marks     = vertical_marks,
    time_range         = time_range,
    space              = by_elec_space$space,
    space_mode         = by_elec_space$space_mode,
    flip_y             = FALSE
  )
  
  plot_trials_per_condition(
    data_by_trial_channel_condition = data_by_trial_channel_condition,
    # type = "collapse_trial",
    vertical_marks = vertical_marks,
    crp = crp_annotations,
    time_range = time_range,
    cex = cex,
    space = by_elec_space$space,
    space_mode = by_elec_space$space_mode
  )
  
  plot_by_trials_per_condition_heatmap(
    data_by_trial_channel_condition = data_by_trial_channel_condition,
    sort_by        = trial_sort_by,
    space          = by_elec_space$space,
    space_mode     = by_elec_space$space_mode,
    time_range     = time_range,
    cex            = cex,
    crp            = crp_annotations,
    vertical_marks = vertical_marks
  )
}
```


