---
title: "Import Native Formats to RAVE"
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
ravepipeline::pipeline_setup_rmd("import_signals")
```

```{rave obtain_subject_instance, language = "R", export = "subject", format = "rave-subject"}
subject <- ravecore::RAVESubject$new(
  project_name = project_name,
  subject_code = subject_code,
  strict = FALSE
)
```

```{rave validate_data, language = "R", export = "validation_result"}

blocks <- import_blocks
miss_b <- blocks[!blocks%in% subject$preprocess_settings$all_blocks]

if(length(miss_b)) {
  stop("The following block folders are missing: ",
       paste(miss_b, collapse = ", "))
}

lfp_channels <- dipsaus::parse_svec(lfp_channels)
microwire_channels <- dipsaus::parse_svec(microwire_channels)
auxiliary_channels <- dipsaus::parse_svec(auxiliary_channels)
if(!length(c(lfp_channels, microwire_channels, auxiliary_channels))) {
  stop("No channel is set.")
}

lfp_sample_rate <- lfp_sample_rate
microwire_sample_rate <- microwire_sample_rate
auxiliary_sample_rate <- auxiliary_sample_rate

if(length(lfp_channels) > 0 && (!length(lfp_sample_rate) || !isTRUE(lfp_sample_rate > 1))) {
  stop("LFP sample rate is invalid")
}

if(length(microwire_channels) > 0 && (!length(microwire_sample_rate) || !isTRUE(microwire_sample_rate > 1))) {
  stop("Microwire sample rate is invalid")
}

if(length(auxiliary_channels) > 0 && (!length(auxiliary_sample_rate) || !isTRUE(auxiliary_sample_rate > 1))) {
  stop("Auxiliary sample rate is invalid")
}

format <- import_format
if(is.numeric(format) || grepl(" ", import_format)) {
  format <- ravecore::IMPORT_FORMATS[[format]]
}

clean_compose_setup(compose_setup = compose_setup, electrodes = lfp_channels)

if(isTRUE(skip_validation)) {
  ravepipeline::logger("`skip_validation` is on.", level = "warn")
  validation_result <- TRUE
} else {
  validate_channels <- function(channels) {
    if(!length(channels)) { return() }
    validation_result <- switch (
      format,
      'native_matlab' = {
        ravecore:::validate_raw_h5_mat_per_channel(
          subject = subject,
          blocks = blocks,
          electrodes = channels,
          check_content = TRUE
        )
      },
      'native_matlab2' = {
        ravecore:::validate_raw_h5_mat_per_block(
          subject = subject,
          blocks = blocks,
          electrodes = channels,
          check_content = TRUE
        )
      },
      'native_edf' = {
        ravecore:::validate_raw_edf(
          subject = subject,
          blocks = blocks,
          electrodes = channels,
          check_content = TRUE
        )
      },
      'native_brainvis' = {
        ravecore:::validate_raw_brainvision(
          subject = subject,
          blocks = blocks,
          electrodes = channels,
          check_content = TRUE
        )
      },
      'native_blackrock' = {
        ravecore:::validate_raw_nevnsx(
          subject = subject,
          blocks = blocks,
          electrodes = channels,
          check_content = TRUE
        )
      },
      {
        stop("Unknown format ", format)
      }
    )
    if(!isTRUE(validation_result$passed)) {
      reasons <- validation_result$errors
      if(!length(reasons)) {
        stop('rave_import error: unknown reason.')
      }
      msg <- sapply(seq_along(reasons), function(ii){
        nm <- names(reasons)[[ii]]
        items <- reasons[[ii]]
        paste0(ii, ' - ', nm, '\n', paste0('    ', items, collapse = '\n'))
      })
      stop('The following issues found when validating subject ',
           sQuote(subject$subject_code), ' in project ', sQuote(subject$project_name),
           '.\n', msg)
    }
    validation_result
  }
  validation_result <- list(
    lfp = validate_channels(lfp_channels),
    microwire = validate_channels(microwire_channels),
    auxiliary = validate_channels(auxiliary_channels)
  )
}

```

```{rave check_import_signals, language = "R", export = "preprocess_info", cue = "always", format = "rave-subject"}

force(validation_result)

# ensure subject path
subject$initialize_paths(include_freesurfer = FALSE)

blocks <- import_blocks
format <- import_format
if(is.numeric(format) || grepl(" ", import_format)) {
  format <- ravecore::IMPORT_FORMATS[[format]]
}

lfp_channels <- dipsaus::parse_svec(lfp_channels)
microwire_channels <- dipsaus::parse_svec(microwire_channels)
auxiliary_channels <- dipsaus::parse_svec(auxiliary_channels)

lfp_sample_rate <- lfp_sample_rate
microwire_sample_rate <- microwire_sample_rate
auxiliary_sample_rate <- auxiliary_sample_rate

lfp_unit <- NA
microwire_unit <- NA
auxiliary_unit <- NA

all_channels <- c(lfp_channels, microwire_channels, auxiliary_channels)

if(force_import) {
  preproc <- subject$preprocess_settings
  preproc$data$checklevel <- 0L
  
  existing <- preproc$electrodes
  existing <- existing[!existing %in% all_channels]
  preproc$data$electrodes <- NULL
  preproc$data$`@remove`(as.character(all_channels))
  
  if(!setequal(preproc$blocks, blocks)) {
    lapply(existing, function(e){
      preproc$data[[as.character(e)]]$data_imported <- FALSE
    })
    preproc$set_blocks(blocks)
  }
  if(length(lfp_channels)) {
    preproc$set_electrodes(lfp_channels, type = "LFP", add = TRUE)
    preproc$set_sample_rates(lfp_sample_rate, type = "LFP")
  }
  
  if(length(microwire_channels)) {
    preproc$set_electrodes(microwire_channels, type = "Spike", add = TRUE)
    preproc$set_sample_rates(microwire_sample_rate, type = "Spike")
  }
  
  if(length(auxiliary_channels)) {
    preproc$set_electrodes(auxiliary_channels, type = "Auxiliary", add = TRUE)
    preproc$set_sample_rates(auxiliary_sample_rate, type = "Auxiliary")
  }
  preproc$save()
}

# import LFP
rave_import <- switch (
  format,
  'native_matlab' = {
    ravecore:::import_from_h5_mat_per_channel
  },
  'native_matlab2' = {
    ravecore::import_from_h5_mat_per_block
  },
  'native_edf' = {
    ravecore:::import_from_edf
  },
  'native_brainvis' = {
    ravecore:::import_from_brainvis
  },
  'native_blackrock' = {
    ravecore:::import_from_nevnsx
  },
  {
    stop("Unknown format ", format)
  }
)
if(length(lfp_channels)) {
  rave_import(
    subject = subject,
    blocks = blocks, electrodes = lfp_channels,
    sample_rate = lfp_sample_rate, 
    data_type = "LFP", add = FALSE, 
    skip_validation = TRUE
  )
}

# import Microwire
if(length(microwire_channels)) {
  rave_import(
    subject = subject,
    blocks = blocks, electrodes = microwire_channels,
    sample_rate = microwire_sample_rate, 
    data_type = "Spike", add = TRUE, 
    skip_validation = TRUE
  )
}


# import auxiliary
if(length(auxiliary_channels)) {
  rave_import(
    subject = subject,
    blocks = blocks, electrodes = auxiliary_channels,
    sample_rate = auxiliary_sample_rate, 
    data_type = "Auxiliary", add = TRUE, 
    skip_validation = TRUE
  )
}


compose_params <- clean_compose_setup(compose_setup = compose_setup, electrodes = lfp_channels)

if(length(compose_params)) {
  ravepipeline::lapply_jobs(
    compose_params, function(item) {
      ravecore::compose_channel(
        subject = subject$subject_id,
        number = item$number,
        from = item$from,
        weights = item$weights,
        normalize = item$normalize,
        force = TRUE
      )
      return()
    },
    .globals = list(
      subject = subject
    ),
    callback = function(item) {
      sprintf("Composing channel|%s", item$number)
    }
  )
}

module_id <- "import_lfp_native"
data_types <- NULL
if(length(lfp_channels)) {
  data_types <- "LFP"
}
if(length(microwire_channels)) {
  data_types <- c(data_types, "Spike")
}
if(length(auxiliary_channels)) {
  data_types <- c(data_types, "Auxiliary")
}

subject$set_default(
  namespace = module_id,
  key = "import_parameters",
  value = list(
    project_name = subject$project_name,
    subject_code = subject$subject_code,
    blocks = blocks,
    electrodes = dipsaus::deparse_svec(lfp_channels),
    lfp_channels = dipsaus::deparse_svec(lfp_channels),
    microwire_channels = dipsaus::deparse_svec(microwire_channels),
    auxiliary_channels = dipsaus::deparse_svec(auxiliary_channels),
    composed_electrodes = compose_params,
    
    sample_rate = lfp_sample_rate,
    lfp_sample_rate = lfp_sample_rate,
    microwire_sample_rate = microwire_sample_rate,
    auxiliary_sample_rate = auxiliary_sample_rate,
    
    format = format,
    format_readable = names(ravecore::IMPORT_FORMATS)[ravecore::IMPORT_FORMATS == format],
    conversion = lfp_unit,
    lfp_conversion = lfp_unit,
    microwire_conversion = microwire_unit,
    auxiliary_conversion = auxiliary_unit,
    
    data_type = data_types,
    add = FALSE,
    timestamp = strftime(Sys.time(), usetz = TRUE)
  )
)

preprocess_info <- ravecore::RAVEPreprocessSettings$new(subject$subject_id, read_only = TRUE)

subject$get_electrode_table(reference_name = ".fake", simplify = FALSE)
```


## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-import_signals.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-import_signals.R")
```


Once the pipeline script `make-import_signals.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
# Fixed usage, show pipeline graph
try({
  asNamespace("ravepipeline")$pipeline_dependency_graph(
    pipeline_path = ".", glimpse = TRUE)
}, silent = TRUE)
```



