---
title: "Generate surface-based atlases from group of subjects"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
ravepipeline::pipeline_setup_rmd("generate_surface_atlas")

# ieegio::io_write_yaml(
#   con = file.path(pipeline$pipeline_path, "settings.yaml"),
#   x = list(
#     project_name = "YAEL",
#     template_name = "fsaverage",
#     value_table = "${EXTDATA-SETTINGS|value_table|csv}",
#     subject_codes = c("Precision010")
#   ),
#   sorted = TRUE
# )

# write.csv(
#   data.frame(Subject = 'Precision010'),
#   file = file.path(pipeline$pipeline_path, "data/value_table.csv")
# )

```

```{rave ensure_template_files, use_rave=TRUE, language="R", export="template_information", cue="always"}
template_root <- threeBrain::default_template_directory()
if(length(template_name) != 1) {
  stop("Input `template_name` must be a string with length one")
}
template_path <- file.path(template_root, template_name)
if(!dir.exists(template_path)) {
  # template is missing
  available_templates <- names(threeBrain::available_templates())
  if(isTRUE(template_name %in% available_templates)) {
    
    # 10 min timeout
    opt <- options(timeout = 600)
    on.exit(options(opt))
    message("No template is found... Downloading the template. This might take a while")
    threeBrain::download_template_subject(subject_code = template_name)
  }
}

template_information <- list(
  name = template_name,
  path = normalizePath(template_path, winslash = "/")
)
```

```{rave find_meta_from_value_file, use_rave=TRUE, language="R", export="value_table_meta"}
if(!is.data.frame(value_table)) {
  stop("Unable to parse the value table. Please provide a comma-separated value (csv) file with column 'Subject' in it (case-sensitive).")
}
value_table_meta <- extract_meta_value_table(value_table, project_name)
```

```{rave validate_inputs, language="R", export="cleaned_inputs"}
project <- raveio::as_rave_project(project_name)
all_subjects <- project$subjects()

from_subjects <- value_table_meta$subjects
from_subjects <- from_subjects[from_subjects %in% all_subjects]

# check all subjects to make sure they have freesurfer paths
has_surfaces <- vapply(from_subjects, function(subject) {
  subject <- raveio::RAVESubject$new(project_name = project$name, subject_code = subject, strict = FALSE)
  brain <- raveio::rave_brain(subject)
  if(is.null(brain)) { return(FALSE) }
  if(!length(brain$surface_types)) { return(FALSE) }
  TRUE
}, FUN.VALUE = FALSE, USE.NAMES = FALSE)



cleaned_inputs <- list(
  project_name = project_name,
  template = template_information,
  subject_codes = from_subjects,
  has_surfaces = has_surfaces
)
```

```{rave map_to_template, language="R", export="mapped_results", cue="always"}
suppressWarnings({
  raveio::with_future_parallel({
    
    flip_hemisphere <- mapping_params$flip_hemisphere
    
    mapped_results <- raveio::lapply_async(
      subject_codes, function(subject_code) {
        res <- map_to_template(
          subject = raveio::RAVESubject$new(
            project_name = cleaned_inputs$project_name,
            subject_code = subject_code), 
          method = mapping_method,
          template = cleaned_inputs$template$name,
          volumetric_transform = "affine",
          interpolator = mapping_params$interpolator,
          save_to = NULL,
          flip_hemisphere = isTRUE(subject_code %in% flip_hemisphere),
          n_segments = c(mapping_params$width, mapping_params$height)
        )
        res$mapped_table$Subject <- subject_code
        res$mapped_table
      },
      callback = function(subject_code) {
        sprintf("Mapping subject|%s", subject_code)
      }
    )
  })
  
  mapped_results <- data.table::rbindlist(mapped_results)
})

```

```{rave generate_atlas, language="R", export="mapped_atlas"}
if(!isTRUE(value_name %in% names(value_table))) {
  stop("Invalid value name [", paste(value_name, collapse = ""),
       "] for generating atlases.")
}
mapped_atlas <- generate_atlas(
  mapped_results = mapped_results,
  value_table = value_table,
  template_name = cleaned_inputs$template$name,
  value_name = value_name,
  value_type = value_type,
  mapping_threshold = mapping_threshold
)
mapped_atlas
```

```{rave save_group_atlas, language="R", export="save_atlas", cue="always"}
if(length(atlas_name) != 1 || 
   is.na(atlas_name) || 
   !nzchar(atlas_name)) {
  # atlas_name is unset, use the value name itself
  atlas_name <- value_name
}
atlas_name <- gsub("[^0-9A-Za-z_+-]", "_", atlas_name)

label_path <- file.path(
  threeBrain::default_template_directory(),
  mapped_atlas$template_name, "label")

file_ext <- mapped_atlas$file_ext
atlas_left <- mapped_atlas$atlas_left
atlas_right <- mapped_atlas$atlas_right

if(inherits(atlas_left, "ieegio_surface_contains_measurements")) {
  file_type <- "measurements"
} else {
  file_type <- "annotations"
}

file_right <- file.path(
  label_path,
  sprintf("rh.%s.%s", atlas_name, file_ext)
)

file_left <- file.path(
  label_path,
  sprintf("lh.%s.%s", atlas_name, file_ext)
)

ieegio::write_surface(
  x = atlas_right,
  format = 'freesurfer',
  type = file_type,
  con = file_right
)

ieegio::write_surface(
  x = atlas_left,
  format = 'freesurfer',
  type = file_type,
  con = file_left
)

save_atlas <- list(
  path_left = normalizePath(file_left, winslash = "/"),
  path_right = normalizePath(file_right, winslash = "/")
)
```

## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-generate_surface_atlas.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-generate_surface_atlas.R")
```


Once the pipeline script `make-generate_surface_atlas.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
# Fixed usage, show pipeline graph
try({
  asNamespace("ravepipeline")$pipeline_dependency_graph(
    pipeline_path = ".", glimpse = TRUE)
}, silent = TRUE)
```



