---
title: "RAVE Pipeline Markdown Template"
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
ravepipeline::pipeline_setup_rmd("connectivity_viewer")
```

```{rave get_template_details, language = "R", export = "template_details", cue = "always", collapse=FALSE}
template_details <- list('selected_template' = selected_template,
                         'selected_surfaces' = surface_types
                         )
```



## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-connectivity_viewer.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-connectivity_viewer.R")
```

Once the pipeline script `make-connectivity_viewer.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
# Fixed usage, show pipeline graph
try({
  asNamespace("ravepipeline")$pipeline_dependency_graph(
    pipeline_path = ".", glimpse = TRUE)
}, silent = TRUE)
```



