---
title: "RAVE Pipeline Markdown Template"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
ravepipeline::pipeline_setup_rmd("group_3d_viewer")
```

```{rave ensure_template_brain, language = "R", export = "template_info", cue = "always"}
template_root <- threeBrain::default_template_directory()
template_path <- file.path(template_root, template_name)
if(!dir.exists(template_path)) {
  oldopt <- options(timeout = 3600)
  on.exit({ options(oldopt) })
  threeBrain::download_template_subject(subject_code = template_name)
}
template_path <- normalizePath(template_path, winslash = "/", mustWork = TRUE)
template_brain <- threeBrain::threeBrain(path = template_path, subject_code = template_name)

# Find all available volumes, surfaces, annotations
volumes <- sort(list.files(
  file.path(template_path, "mri"),
  pattern = "\\.(mgz|nii|nii.gz)$",
  recursive = FALSE,
  include.dirs = FALSE,
  full.names = FALSE,
  all.files = FALSE,
  ignore.case = TRUE
))
volumes <- gsub("\\.(mgz|nii|nii.gz)$", "", volumes, ignore.case = TRUE)
surfaces <- sort(template_brain$available_surfaces)
annotations <- list.files(
  file.path(template_path, "label"),
  pattern = "\\.(annot|curv|sulc)$",
  recursive = FALSE,
  include.dirs = FALSE,
  full.names = FALSE,
  all.files = FALSE,
  ignore.case = TRUE
)
annotations <- gsub("\\.(annot|curv|sulc)$", "", annotations, ignore.case = TRUE)
annotations <- gsub("^[lr]h\\.", "", annotations, ignore.case = TRUE)
annotations <- sprintf("label/%s", sort(unique(annotations)))
template_info <- list(
  name = template_name,
  path = template_path,
  volumes = volumes,
  surfaces = surfaces,
  annotations = annotations
)
```


```{rave filter_subject_codes, language = "R", export = "subject_codes_filtered"}
if(length(project_name) != 1) {
  stop("Invalid RAVE project name. The `project_name` input must have length of one")
}
project <- ravecore::as_rave_project(project_name)
all_subject_codes <- project$subjects()
if(!length(all_subject_codes)) {
  warning(sprintf("No subject found under the project `%s`", project_name))
}
subject_codes <- unlist(subject_codes)
subject_codes <- subject_codes[subject_codes %in% all_subject_codes]
subject_codes_filtered <- sort(unique(subject_codes))
```

```{rave checking_mapping_capabilities, language = "R", export = "mapping_capabilities", cue = "always"}
mapping_capabilities <- data.table::rbindlist(lapply(subject_codes_filtered, function(subject_code) {
  c(
    list(Subject = subject_code),
    mapping_capability(project_name, subject_code)
  )
}))
```

```{rave get_mapped_brain_list, language = "R", export = "brain_list", cue = "always", format = "user-defined-r"}
force(mapping_capabilities)
brain_list <- lapply(subject_codes_filtered, function(subject_code) {
  capability <- mapping_capabilities[mapping_capabilities$Subject == subject_code, ]
  brain <- tryCatch(
    {
      brain <- get_mapped_brain(
        project_name = project_name,
        subject_code = subject_code,
        mapping_method = mapping_method,
        capability = capability,
        use_cache = use_cache
      )
      
      raw_table <- brain$electrodes$raw_table
      
      if(
        is.data.frame(raw_table) && nrow(raw_table) > 0 &&
        "LabelPrefix" %in% names(raw_table)) {
        
        brain$set_electrode_values(data.frame(
          Electrode = raw_table$Electrode,
          LabelPrefix = raw_table$LabelPrefix
        ))
        
      }
      brain
    }, error = function(e) {
      NULL
    }
  )
  brain
})
brain_list <- brain_list[!vapply(brain_list, is.null, FALSE)]
```

```{rave generate_template_brain, language = "R", export = "template", format = "user-defined-r"}
radius <- electrode_radius
if(length(radius) != 1 || !is.numeric(radius) || !isTRUE(radius > 0) || !is.finite(radius)) {
  radius <- 0
}

if(radius > 0) {
  brain_list2 <- lapply(brain_list, function(brain) {
    raw_table <- brain$electrodes$raw_table
    if(is.data.frame(raw_table) && nrow(raw_table) > 0) {
      raw_table$Radius <- radius
      brain$set_electrodes(raw_table, priority = "sphere")
    }
    brain
  })
} else {
  brain_list2 <- brain_list
}


template <- threeBrain::merge_brain(
  .list = brain_list2,
  template_subject = template_info$name
  # template_surface_types = NULL
  # template_atlas_types = ,
  # template_annotation_types = 
  # electrode_priority = "sphere"
)
```

## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-group_3d_viewer.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-group_3d_viewer.R")
```


Once the pipeline script `make-group_3d_viewer.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
# Fixed usage, show pipeline graph
try({
  asNamespace("ravepipeline")$pipeline_dependency_graph(
    pipeline_path = ".", glimpse = TRUE)
}, silent = TRUE)
```



