---
title: "Import Native Formats to RAVE"
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
ravepipeline::pipeline_setup_rmd("import_lfp_native")

# DIPSAUS DEBUG START
# pipeline <- ravepipeline::pipeline(
#   pipeline_name = "import_lfp_native", 
#   paths = file.path(rstudioapi::getActiveProject(), "modules"))
```

```{rave obtain_subject_instance, language = "R", export = "subject", format = "rave-subject"}
subject <- raveio::RAVESubject$new(
  project_name = import_setup__project_name,
  subject_code = import_setup__subject_code,
  strict = FALSE
)
```

```{rave validate_data, language = "R", export = "validation_result"}

blocks <- import_blocks__session_block
miss_b <- blocks[!blocks%in% subject$preprocess_settings$all_blocks]

if(length(miss_b)) {
  stop("The following block folders are missing: ",
       paste(miss_b, collapse = ", "))
}

lfp_channels <- dipsaus::parse_svec(import_channels__lfp_channels)
microwire_channels <- dipsaus::parse_svec(import_channels__microwire_channels)
auxiliary_channels <- dipsaus::parse_svec(import_channels__auxiliary_channels)
if(!length(c(lfp_channels, microwire_channels, auxiliary_channels))) {
  stop("No channel is set.")
}

lfp_sample_rate <- import_channels__lfp_sample_rate
microwire_sample_rate <- import_channels__microwire_sample_rate
auxiliary_sample_rate <- import_channels__auxiliary_sample_rate

if(length(lfp_channels) > 0 && !length(lfp_sample_rate) || !isTRUE(lfp_sample_rate > 1)) {
  stop("LFP sample rate is invalid")
}

if(length(microwire_channels) > 0 && !length(microwire_sample_rate) || !isTRUE(microwire_sample_rate > 1)) {
  stop("Microwire sample rate is invalid")
}

if(length(auxiliary_channels) > 0 && !length(auxiliary_sample_rate) || !isTRUE(auxiliary_sample_rate > 1)) {
  stop("Auxiliary sample rate is invalid")
}

format <- import_blocks__format
if(!is.numeric(format)) {
  format <- which(startsWith(names(raveio::IMPORT_FORMATS), trimws(format)))
}

clean_compose_setup(compose_setup = compose_setup, electrodes = lfp_channels)

if(isTRUE(skip_validation)) {
  ravedash::logger("`skip_validation` is on.", level = "warn")
  validation_result <- TRUE
} else {
  validate_channels <- function(channels) {
    if(!length(channels)) { return() }
    validation_result <- raveio::validate_raw_file(
      subject_code = subject$subject_code,
      blocks = blocks, electrodes = channels,
      format = format
    )
    if(!validation_result) {
      reasons <- attr(validation_result, 'reason')
      if(!is.list(reasons) || !length(reasons)){ stop('rave_import error: unknown reason.') }
      msg <- sapply(seq_along(reasons), function(ii){
        nm <- names(reasons)[[ii]]
        items <- reasons[[ii]]
        paste0(ii, ' - ', nm, '\n', paste0('    ', items, collapse = '\n'))
      })
      stop('The following issues found when validating subject ',
           sQuote(subject$subject_code), ' in project ', sQuote(subject$project_name),
           '.\n', msg, call. = bquote(raveio::validate_raw_file(
        subject_code = .(subject$subject_code),
        blocks = .(blocks), electrodes = .(channels),
        format = .(format)
      )))
    }
    validation_result
  }
  validation_result <- list(
    lfp = validate_channels(lfp_channels),
    microwire = validate_channels(microwire_channels),
    auxiliary = validate_channels(auxiliary_channels)
  )
}

```

```{rave check_import_signals, language = "R", export = "preprocess_info", cue = "always", format = "rave-subject"}

force(validation_result)

# ensure subject path
subject$initialize_paths(include_freesurfer = FALSE)

blocks <- import_blocks__session_block
format <- import_blocks__format
if(!is.numeric(format)) {
  format <- which(startsWith(names(raveio::IMPORT_FORMATS), trimws(format)))
}

lfp_channels <- dipsaus::parse_svec(import_channels__lfp_channels)
microwire_channels <- dipsaus::parse_svec(import_channels__microwire_channels)
auxiliary_channels <- dipsaus::parse_svec(import_channels__auxiliary_channels)

lfp_sample_rate <- import_channels__lfp_sample_rate
microwire_sample_rate <- import_channels__microwire_sample_rate
auxiliary_sample_rate <- import_channels__auxiliary_sample_rate

lfp_unit <- import_channels__lfp_unit
microwire_unit <- import_channels__microwire_unit
auxiliary_unit <- import_channels__auxiliary_unit


if(length(lfp_unit) != 1 || is.na(lfp_unit) ||
   lfp_unit == "NA" || !isTRUE(lfp_unit %in% c("V", "mV", "uV"))) {
  lfp_unit <- NA
}

if(length(microwire_unit) != 1 || is.na(microwire_unit) ||
   microwire_unit == "NA" || !isTRUE(microwire_unit %in% c("V", "mV", "uV"))) {
  microwire_unit <- NA
}

if(length(auxiliary_unit) != 1 || is.na(auxiliary_unit) ||
   auxiliary_unit == "NA" || !isTRUE(auxiliary_unit %in% c("V", "mV", "uV"))) {
  auxiliary_unit <- NA
}

all_channels <- c(lfp_channels, microwire_channels, auxiliary_channels)

if(force_import) {
  preproc <- subject$preprocess_settings
  preproc$data$checklevel <- 0L
  
  existing <- preproc$electrodes
  existing <- existing[!existing %in% all_channels]
  preproc$data$electrodes <- NULL
  preproc$data$`@remove`(as.character(all_channels))
  
  if(!setequal(preproc$blocks, blocks)) {
    lapply(existing, function(e){
      preproc$data[[as.character(e)]]$data_imported <- FALSE
    })
    preproc$set_blocks(blocks)
  }
  preproc$set_electrodes(lfp_channels, type = "LFP", add = TRUE)
  preproc$set_sample_rates(lfp_sample_rate, type = "LFP")
  
  preproc$set_electrodes(microwire_channels, type = "Spike", add = TRUE)
  preproc$set_sample_rates(microwire_sample_rate, type = "Spike")
  
  preproc$set_electrodes(auxiliary_channels, type = "Unknown", add = TRUE)
  preproc$set_sample_rates(auxiliary_sample_rate, type = "Unknown")
  preproc$save()
}

# import LFP
if(length(lfp_channels)) {
  raveio::rave_import(
    project_name = subject$project_name,
    subject_code = subject$subject_code,
    blocks = blocks, electrodes = lfp_channels,
    sample_rate = lfp_sample_rate, format = format,
    conversion = lfp_unit,
    data_type = "LFP", add = FALSE, 
    skip_validation = TRUE
  )
}

# import Microwire
if(length(microwire_channels)) {
  raveio::rave_import(
    project_name = subject$project_name,
    subject_code = subject$subject_code,
    blocks = blocks, electrodes = microwire_channels,
    sample_rate = microwire_sample_rate, format = format,
    conversion = microwire_unit,
    data_type = "Spike", add = TRUE, 
    skip_validation = TRUE
  )
}


# import auxiliary
if(length(auxiliary_channels)) {
  raveio::rave_import(
    project_name = subject$project_name,
    subject_code = subject$subject_code,
    blocks = blocks, electrodes = auxiliary_channels,
    sample_rate = auxiliary_sample_rate, format = format,
    conversion = auxiliary_unit,
    data_type = "Unknown", add = TRUE, 
    skip_validation = TRUE
  )
}


compose_params <- clean_compose_setup(compose_setup = compose_setup, electrodes = lfp_channels)

if(length(compose_params)) {
  raveio::lapply_async(compose_params, function(item) {
    raveio::compose_channel(
      subject = subject$subject_id,
      number = item$number,
      from = item$from,
      weights = item$weights,
      normalize = item$normalize,
      force = TRUE
    )
  })
}

module_id <- "import_lfp_native"
data_types <- NULL
if(length(lfp_channels)) {
  data_types <- "LFP"
}
if(length(microwire_channels)) {
  data_types <- c(data_types, "Spike")
}
if(length(lfp_channels)) {
  data_types <- c(data_types, "Unknown")
}

subject$set_default(
  namespace = module_id,
  key = "import_parameters",
  value = list(
    project_name = subject$project_name,
    subject_code = subject$subject_code,
    blocks = blocks,
    electrodes = dipsaus::deparse_svec(lfp_channels),
    lfp_channels = dipsaus::deparse_svec(lfp_channels),
    microwire_channels = dipsaus::deparse_svec(microwire_channels),
    auxiliary_channels = dipsaus::deparse_svec(auxiliary_channels),
    composed_electrodes = compose_params,
    
    sample_rate = lfp_sample_rate,
    lfp_sample_rate = lfp_sample_rate,
    microwire_sample_rate = microwire_sample_rate,
    auxiliary_sample_rate = auxiliary_sample_rate,
    
    format = format,
    format_readable = names(raveio::IMPORT_FORMATS)[[format]],
    conversion = lfp_unit,
    lfp_conversion = lfp_unit,
    microwire_conversion = microwire_unit,
    auxiliary_conversion = auxiliary_unit,
    
    data_type = data_types,
    add = FALSE,
    timestamp = strftime(Sys.time(), usetz = TRUE)
  )
)

preprocess_info <- raveio::RAVEPreprocessSettings$new(subject$subject_id, read_only = TRUE)

subject$get_electrode_table(reference_name = ".fake", simplify = FALSE)
```



## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-import_lfp_native.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-import_lfp_native.R")
```


Once the pipeline script `make-import_lfp_native.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)


```{r visualize, echo=FALSE}
Sys.setenv("RAVE_PIPELINE" = normalizePath("."))
ravepipeline::pipeline_visualize()
```








