---
title: "RAVE Pipeline Markdown Template"
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
ravepipeline::pipeline_setup_rmd("electrode_localization")

# setting debug=TRUE to make sure some errors are ignored
options("raveio.debug" = TRUE)
```

# Load and prepare data for electrode localization

Load `FreeSurfer` [look-up table](https://surfer.nmr.mgh.harvard.edu/fswiki/FsTutorial/AnatomicalROI/FreeSurferColorLUT), used to calculate the DKT atlases for each contact, provided that `FreeSurfer` `recon-all` has been applied.

```{rave load_FreeSurfer_LUT, export = "fslut", cue = "never"}
fslut <- load_freesurfer_lookup_table()
```

Load subject object from given RAVE project name and subject code

```{rave load_subject, language = "R", export = "subject", format = "rave-subject", cue = "always"}
subject <- ravecore::RAVESubject$new(
  project_name = project_name, 
  subject_code = subject_code,
  strict = FALSE
)
```

Look for images in subject's raw folder, under `rave-imaging/coregistration` for file names that are potentially `CT`, so the users can choose from these candidates. This target is built for module UI.

```{rave find_CT_Nifti_files, language = "R", export = "ct_candidates"}
ct_candidates <- get_image_candidates_from_coregistration_folder(subject)
```

Given electrode localization plan, initialize and/or prepare a localization table `electrodes__unsaved.csv`, which is later saved to subject's meta folder. 

The input `localization_plan` is a list of electrode surgical labels, dimension, type, and hemisphere, for e.g.:

``` r
list(
  
  # first electrode
  list(
    
    # surgical label: left DBS lead
    label = "LDBS",
    
    # using channel 1-8
    dimension = "1-8",
    
    # electrode types, using `names(threeBrain::list_electrode_prototypes())`
    # to query available types; if none is found, use "iEEG"
    type = "DBS-BSC-DB-2202",
    
    # auto if undecided to save time, used to infer the FreeSurfer labels, 
    # if the contact is too medial
    hemisphere = "auto",
  ), 
  
  # second electrode
  list(
    label = "RDBS",
    dimension = "9-16",
    type = "DBS-BSC-DB-2202",
    hemisphere = "auto",
  )
  
)
```

Function `make_localization_plan_list` translates `localization_plan` into a list of tables, where each table has $n\times p$ dimensions, where `n` is the number of contacts and `p` is the built-in columns used by RAVE

```{rave check_localization_plan, export = "plan_list", cue = "always"}
plan_list <- make_localization_plan_list(subject = subject, localization_plan = localization_plan, write_table = TRUE)
```

For surface electrodes, we ensure that pial-envelope `pial-outer-smoothed` surface is available

```{rave check_load_pial_envelop, language = "R", export = "pial_envelope", cue = "always"}
pial_envelope <- ensure_pial_envelope(subject = subject)
```

Now load the brain with prototypes, such that when the viewer is generated, all the electrode geometry prototypes are available 

```{rave load_brain_and_generate_pial_envelope, language = "R", export = "brain", cue = "always"}
# make sure the pial envelope runs before loading the brain
force(pial_envelope)
brain <- load_brain_with_electrode_prototypes(subject = subject, plan_list = plan_list)
```

Collect localization data 

```{rave Loading_brain_and_CT_if_exists, language = "R", export = "localize_data", cue = "always"}
localize_data <- collect_localization_data(
  subject = subject,
  path_mri = path_mri,
  path_ct = path_ct,
  path_transform = path_transform,
  transform_space = transform_space
)
```

```{rave generate_indicator, language = "R", export = "ct_exists", cue = "always"}
ct_exists <- isTRUE(!is.null(localize_data$ct_header) && is.list(localize_data$ct_header))
```

Using the localization data to calculate the transform from CT to MR image and generate the 3D viewer.

```{rave generate_localization_viewer, language = "R", export = "viewer", cue = "always"}
force(ct_exists)
viewer <- brain$localize(
  ct_path = localize_data$ct_path, 
  transform_space = localize_data$transform_space,
  transform_matrix = localize_data$transform_matrix,
  mri_path = localize_data$mri_path
)
```

# Stage and save the localization

Temporarily save (stage) the localization to avoid data loss.

```{rave merge_localization_list, export = "localization_result_initial", cue = "always"}
localization_result_initial <- stage_localization(
  subject = subject, brain = brain, 
  localization_list = localization_list
)
```

Generate the final electrode table, rename the `electrodes__unsaved.csv` to `electrodes.csv`, which is recognized by RAVE.

To make the pipeline simpler, `localization_result_final` does not call `localization_result_initial`, but you should always evaluate `localization_result_initial` first.

```{rave get_finalized_table, export = "localization_result_final", cue="always"}
# Make sure you stage the localization first so that
# electrodes__unsaved.csv and corresponding electrode geometry prototypes
# are saved
force(localization_result_initial)
localization_result_final <- save_localization(
  subject = subject,
  brain = brain,
  localize_data = localize_data
)
```

# Post-processing

Make sure the electrodes are saved (run `localization_result_final`) first

### Post-processing using `ANTs`

Calculate non-linear MNI coordinates. This optional target requires `Python` for RAVE be configured via `ravemanager::configure_python()`, and run `ravecore::cmd_run_yael_preprocess(...)` first. To calculate non-linear mapping from T1 to MNI templates, run the following command or choose `YAEL+recon-all` in imaging preprocessing module.

``` r
ravecore::cmd_run_yael_preprocess(
  subject,
  t1w_path = path_mri,
  normalize_template = "mni_icbm152_nlin_asym_09b",
  run_recon_all = FALSE,
  verbose = TRUE
)
```

```{rave burn_electrodes_to_t1, export = "burn_electrodes_to_t1", cue = "always"}
electrode_table <- localization_result_final$electrode_table
if(isTRUE(as.list(postprocess_opts)[["burn_electrodes_to_t1"]])) {
  localization_path <- file.path(subject$imaging_path, "localization")
  if(!dir.exists(localization_path)) {
    dir.create(localization_path, showWarnings = FALSE, recursive = TRUE)
  }
  # Burn T1
  t1_path <- localize_data$mri_path
  pal <- threeBrain:::DEFAULT_COLOR_DISCRETE
  label_prefix <- electrode_table$LabelPrefix
  label_prefix_levels <- unique(label_prefix)
  n_levels <- length(label_prefix_levels)
  if(length(pal) < n_levels) {
    pal <- grDevices::colorRampPalette(colors = pal)(n_levels)
  } else {
    pal <- pal[seq_len(n_levels)]
  }
  col <- as.integer(factor(label_prefix, levels = label_prefix_levels))
  col_str <- pal[col]
  radius <- as.numeric(electrode_table$Radius)
  if(!length(radius)) {
    radius <- rep(1, nrow(electrode_table))
  }
  scanner_ras <- as.matrix(electrode_table[, c("T1R", "T1A", "T1S")])
  burn <- ieegio::burn_volume(
    image = t1_path,
    ras_position = scanner_ras,
    col = col_str,
    radius = radius,
    blank_underlay = TRUE, 
    preview = NULL
  )
  # sub-OCD5_ses-preop_space-MNI152NLin2009aAsym_desc-preproc_transform-deformable_T1w
  # sub-OCD5_from-T1w_to-MNI152NLin2009aAsym_desc-affine+SyN_ants0.mat
  fname <- sprintf("sub-%s_space-T1w_desc-electrodeBurntInOverlay_T1w.nii.gz", subject$subject_code)
  ieegio::write_volume(burn, file.path(localization_path, fname))
  
  burn <- ieegio::burn_volume(
    image = t1_path,
    ras_position = scanner_ras,
    col = col_str,
    radius = radius,
    blank_underlay = FALSE, 
    preview = NULL
  )
  # sub-OCD5_ses-preop_space-MNI152NLin2009aAsym_desc-preproc_transform-deformable_T1w
  # sub-OCD5_from-T1w_to-MNI152NLin2009aAsym_desc-affine+SyN_ants0.mat
  fname <- sprintf("sub-%s_space-T1w_desc-electrodeBurntIn_T1w.nii.gz", subject$subject_code)
  ieegio::write_volume(burn, file.path(localization_path, fname))
  burn_electrodes_to_t1 <- fname
} else {
  burn_electrodes_to_t1 <- NULL
}
```

```{rave nonlinear_volumetric_mapping, export = "nonlinear_volumetric_mapping", cue = "always"}
if(isTRUE(as.list(postprocess_opts)[["nonlinear_volumetric_mapping"]])) {
  # YAEL post process
  electrode_table <- subject$get_electrode_table()
  
  is_debug <- getOption("raveio.debug", FALSE)
  
  if(!is.data.frame(electrode_table)) {
    stop("Invalid electrode table. Please save the electrode localization results first.")
  }
  
  if(!rpyANTs::ants_available()) {
    stop("ANTs is not configured for RAVE. Python environment must be configured through `ravemanager::configure_python()` first.")
  }
  
  if(!all(c("T1R", "T1A", "T1S") %in% names(electrode_table))) {
    brain <- ravecore::rave_brain(subject)
    if(is.null(brain)) {
      stop("The electrode table is missing [`T1R`, `T1A`, `T1S`] columns (they are T1 scanner space in RAS coordinate system.)")
    }
    
    tkr_ras <- as.matrix(electrode_table[, c("Coord_x", "Coord_y", "Coord_z")])
    t1_ras <- brain$electrodes$apply_transform_points(
      positions = tkr_ras,
      from = "tkrRAS", to = "scannerRAS"
    )
    valids <- rowSums(tkr_ras ^ 2) > 0  
    
    # Make sure "T1R", "T1A", "T1S" are set
    t1_ras[!valids, ] <- 0
    electrode_table$T1R <- t1_ras[, 1]
    electrode_table$T1A <- t1_ras[, 2]
    electrode_table$T1S <- t1_ras[, 3]
  } else {
    t1_ras <- as.matrix(electrode_table[, c("T1R", "T1A", "T1S")])
    valids <- rowSums(t1_ras ^ 2) > 0  
  }
  
  
  
  if(any(valids)) {
    yael_process <- ravecore::YAELProcess$new(subject = subject)
    # get template mapping
    mapping <- NULL
    mni152 <- NULL
    template_name <- NULL
    for(template_name in c(
      "mni_icbm152_nlin_asym_09b",
      "mni_icbm152_nlin_asym_09a",
      "mni_icbm152_nlin_asym_09c"
    )) {
      mapping <- yael_process$get_template_mapping(template_name = template_name)
      if(!is.null(mapping)) {
        break
      }
    }
    
    if(is.null(mapping)) {
      if( !is_debug ) {
        stop("Unable to find any non-linear mapping files. Please check help documentation of `?ravecore::cmd_run_yael_preprocess` on how to normalize to template in RAVE.")
      }
    } else {
      mni152 <- yael_process$transform_points_to_template(
        native_ras = t1_ras, template_name = template_name
      )
      mni305 <- cbind(mni152, 1) %*% t(solve(ravecore::MNI305_to_MNI152))
      mni152[!valids, ] <- 0
      mni305[!valids, ] <- 0
      electrode_table$MNI305_x <- mni305[, 1]
      electrode_table$MNI305_y <- mni305[, 2]
      electrode_table$MNI305_z <- mni305[, 3]
    
      electrode_table$MNI152_x <- mni152[, 1]
      electrode_table$MNI152_y <- mni152[, 2]
      electrode_table$MNI152_z <- mni152[, 3]
    }
  }
  
  nonlinear_volumetric_mapping <- electrode_table[, c(
    "Electrode", 
    "T1R", "T1A", "T1S", 
    "MNI152_x", "MNI152_y", "MNI152_z", 
    "MNI305_x", "MNI305_y", "MNI305_z"
  )]
   
} else {
  nonlinear_volumetric_mapping <- NULL
}
```


### Post-processing by calculating the template mapping via surface registration

```{rave postprocess_surface_mapping, export = "postprocess_surface_mapping", cue="always"}
if(isTRUE(as.list(postprocess_opts)[["postprocess_surface_mapping"]])) {
  electrode_table <- subject$get_electrode_table()
  
  if(!is.data.frame(electrode_table)) {
    stop("Invalid electrode table. Please save the electrode localization results first.")
  }
  
  if(!all(c("T1R", "T1A", "T1S") %in% names(electrode_table))) {
    brain <- ravecore::rave_brain(subject)
    if(is.null(brain)) {
      stop("The electrode table is missing [`T1R`, `T1A`, `T1S`] columns (they are T1 scanner space in RAS coordinate system.)")
    }
    
    tkr_ras <- as.matrix(electrode_table[, c("Coord_x", "Coord_y", "Coord_z")])
    t1_ras <- brain$electrodes$apply_transform_points(
      positions = tkr_ras,
      from = "tkrRAS", to = "scannerRAS"
    )
    valids <- rowSums(tkr_ras ^ 2) > 0  
    
    # Make sure "T1R", "T1A", "T1S" are set
    t1_ras[!valids, ] <- 0
    electrode_table$T1R <- t1_ras[, 1]
    electrode_table$T1A <- t1_ras[, 2]
    electrode_table$T1S <- t1_ras[, 3]
  } else {
    t1_ras <- as.matrix(electrode_table[, c("T1R", "T1A", "T1S")])
    valids <- rowSums(t1_ras ^ 2) > 0  
  }
  
  surface_mapping <- ravecore::transform_point_to_template(
    subject = subject,
    positions = t1_ras,
    space = "scannerRAS",
    mapping_method = "surface",
    flip_hemisphere = FALSE,
    verbose = TRUE,
    project_surface = postprocess_surface_target
  )
  surface_mapping[!valids, ] <- 0
  surface_mapping$Electrode <- electrode_table$Electrode
  postprocess_surface_mapping <- surface_mapping
} else {
  postprocess_surface_mapping <- NULL
}
```

## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-electrode_localization.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-electrode_localization.R")
```


Once the pipeline script `make-electrode_localization.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
Sys.setenv("RAVE_PIPELINE" = normalizePath("."))
ravepipeline::pipeline_visualize()
```







