---
title: "RAVE Pipeline Markdown Template"
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
raveio::pipeline_setup_rmd("electrode_localization")
```


```{rave load_FreeSurfer_LUT, export = "fslut", cue = "never"}
fslut_path <- system.file("palettes", "datacube2", "FreeSurferColorLUT.json", package = "threeBrain")
cmap <- threeBrain::load_colormap(fslut_path)

fslut <- list(
  cmap = cmap,
  labels = sapply(cmap$map, '[[', "Label")
)
```

```{rave load_subject, language = "R", export = "subject", format = "rave-subject", cue = "always"}
subject <- raveio::RAVESubject$new(
  project_name = project_name, 
  subject_code = subject_code,
  strict = FALSE
)
```


```{rave find_CT_Nifti_files, language = "R", export = "ct_candidates"}
fs_path <- subject$freesurfer_path

# nii/nii.gz files in fs_path/../coregistration, or fs_path/coregistration
if(length(fs_path) != 1 || is.na(fs_path) || !dir.exists(fs_path)) {
  stop("Cannot find surface/volume reconstruction folder.")
}

f1 <- list.files(file.path(fs_path, "coregistration"), pattern = "nii(?:\\.gz)?$", 
                 recursive = FALSE, ignore.case = TRUE, include.dirs = FALSE,
                 full.names = FALSE, all.files = FALSE)
f2 <- list.files(file.path(fs_path, "..", "coregistration"), pattern = "nii(?:\\.gz)?$", 
                 recursive = FALSE, ignore.case = TRUE, include.dirs = FALSE,
                 full.names = FALSE, all.files = FALSE)
files <- c(f1, f2)
files[duplicated(files)] <- sprintf("%s (2)", files[duplicated(files)])

ct_candidates <- structure(files, paths = list(
  f1 = f1, f2 = f2
))
```

The following code block only run once only when starting a new localization

```{rave check_localization_plan, export = "plan_list", cue = "always"}
plan_list <- list()

# check if number of electrodes is consistent with the plan
plans <- dipsaus::fastmap2()
electrodes <- sort(subject$preprocess_settings$electrodes)

lapply(summarize_plan_list(localization_plan), function(item) {
  if(!length(item)) { return() }
  if(!isTRUE(item$n > 0)) { return() }
  label <- toupper(as.character(item$label))
  part1 <- plans[[label]]
  if(length(part1)) {
    if(!identical(part1$type, item$type)) {
      stop(sprintf("There exist multiple groups with the same group label [%s] (group labels are case-insensitive) but different electrode types [%s, %s]. I cannot determine which electrode prototype for the localization. Please check and correct.", label, part1$type, item$type))
    }
    part1$channels <- sprintf("%s,%s", part1$channels, item$channels)
    part1$n <- part1$n + item$n
    item <- part1
  } 
  plans[[label]] <- list(
    n = item$n,
    channels = item$channels,
    type = item$type,
    label = label,
    hemisphere = item$hemisphere,
    dimension = item$dimension
  )
})

plan_table <- lapply(names(plans), function(nm) {
  item <- plans[[nm]]
  proto <- get_prototype(item$type)
  channs <- parse_svec(item$channels, sort = FALSE, unique = FALSE, na_rm = FALSE)
  
  unplug <- is.na(channs)
  n_unplug <- sum(unplug)
  n_chans <- length(channs)
  if(n_chans == n_unplug) { return() }
  if(!is.null(proto)) {
    if(n_chans > proto$n_channels) {
      stop(sprintf("Electrode group [%s] (prototype: %s) has maximum of %d channels by design. However, you have entered %d channels (including %d unplugged channels). Please check & reduce the number of channels.", item$label, item$type, proto$n_channels, n_chans, n_unplug))
    }
  }
  corder <- seq_along(channs)[!unplug]
  channs <- channs[!unplug]
  
  if(item$type %in% raveio::LOCATION_TYPES) {
    ltype <- item$type
    pname <- ""
  } else {
    ltype <- raveio::LOCATION_TYPES[[1]]
    pname <- item$type
  }
  data.frame(
    Electrode = channs,
    Label = sprintf("%s%d", item$label, corder),
    LabelPrefix = item$label,
    Dimension = item$dimension,
    LocationType = ltype,
    Hemisphere = item$hemisphere,
    Prototype = pname,
    ContactOrder = corder
  )
  
})


plan_table <- drop_nulls(plan_table)

if(length(plan_table)) {
  plan_table <- do.call('rbind', unname(plan_table))
  
  if(!nrow(plan_table)) { stop("No valid electrodes to localize.") }
  
  count <- table(plan_table$Electrode)
  count <- names(count)[ count > 1 ]
  
  if(length(count)) {
    stop(sprintf("Electrode contact [%s] has duplicated entries. Please remove and continue.", deparse_svec(as.integer(count))))
  }
  plan_table <- plan_table[order(plan_table$Electrode), ]
  rownames(plan_table) <- NULL
  
  n_planned <- nrow(plan_table)
  if( length(electrodes) > 0 ) {
    if(length(electrodes) != n_planned ) {
      stop(sprintf("The electrode planned (n=%d, for localization) has inconsistent length with registered channel size (n=%d) from the signal pipelines.", n_planned, length(electrodes)))
    }
    
    plan_table$Electrode <- electrodes
  }
  
  # Load existing electrodes_unsaved.csv or electrodes.csv, generate plan table
  files <- file.path(subject$meta_path, c("electrodes_unsaved.csv", "electrodes.csv"))
  files <- files[file.exists(files)]
  
  try({
    if(length(files)) {
      files <- files[[1]]
      electrode_table <- raveio::safe_read_csv(files)
      tname1 <- c("Electrode", "Coord_x", "Coord_y", "Coord_z")
      tname2 <- c(
        "Electrode", "Coord_x", "Coord_y", "Coord_z", "Radius", 
        "MNI305_x", "MNI305_y", "MNI305_z", 
        "FSIndex", "FSLabel", 
        "FSLabel_aparc_a2009s_aseg", "FSLabel_aparc_aseg", 
        "FSLabel_aparc_DKTatlas_aseg", "FSLabel_aseg", 
        "OrigCoord_x", "OrigCoord_y", "OrigCoord_z", "SurfaceElectrode", 
        "DistanceShifted", "DistanceToPial", 
        "Sphere_x", "Sphere_y", "Sphere_z", "Interpolation"
      )
      if(all(tname1 %in% names(electrode_table))) {
        tname2 <- tname2[tname2 %in% names(electrode_table)]
        electrode_table <- electrode_table[, tname2]
        
        # check if there are electrodes missing
        missing_electrodes <- as.integer(electrode_table$Electrode)
        missing_electrodes <- missing_electrodes[!missing_electrodes %in% as.integer(plan_table$Electrode)]
        
        if(length(missing_electrodes)) {
          stop("Detected channel ", dipsaus::deparse_svec(missing_electrodes), 
               " from RAVE data. Please include them in the electrode plan.")
        }
        plan_table <- merge(electrode_table, plan_table, by = "Electrode", all.y = TRUE)
      }
    }
  }, silent = TRUE)
  
  # "Coord_x", "Coord_y", "Coord_z", 
  # "MNI305_x", "MNI305_y", "MNI305_z", 
  # "Sphere_x", "Sphere_y", "Sphere_z"
  # "OrigCoord_x", "OrigCoord_y", "OrigCoord_z", 
  # "DistanceShifted", "DistanceToPial", 
  
  plan_table$Coord_x %?<-% 0
  plan_table$Coord_y %?<-% 0
  plan_table$Coord_z %?<-% 0
  
  plan_table$Interpolation %?<-% "default"
  plan_table$Prototype %?<-% ""
  
  plan_table$MNI305_x %?<-% 0
  plan_table$MNI305_y %?<-% 0
  plan_table$MNI305_z %?<-% 0
  
  plan_table$Sphere_x %?<-% 0
  plan_table$Sphere_y %?<-% 0
  plan_table$Sphere_z %?<-% 0
  
  plan_table$OrigCoord_x %?<-% plan_table$Coord_x
  plan_table$OrigCoord_y %?<-% plan_table$Coord_y
  plan_table$OrigCoord_z %?<-% plan_table$Coord_z
  
  # make sure no NA is in Coord_xyz
  has_NA <- is.na(plan_table$Coord_x) | is.na(plan_table$Coord_y) | is.na(plan_table$Coord_z)
  if(any(has_NA)) {
    plan_table$Coord_x[has_NA] <- 0
    plan_table$Coord_y[has_NA] <- 0
    plan_table$Coord_z[has_NA] <- 0
  }
  
  has_NA_MNI <- has_NA | is.na(plan_table$MNI305_x) | is.na(plan_table$MNI305_y) | is.na(plan_table$MNI305_z)
  if(any(has_NA_MNI)) {
    plan_table$MNI305_x[has_NA_MNI] <- 0
    plan_table$MNI305_y[has_NA_MNI] <- 0
    plan_table$MNI305_z[has_NA_MNI] <- 0
  }
  
  has_NA_sphere <- has_NA | is.na(plan_table$Sphere_x) | is.na(plan_table$Sphere_y) | is.na(plan_table$Sphere_z)
  if(any(has_NA_sphere)) {
    plan_table$Sphere_x[has_NA_sphere] <- 0
    plan_table$Sphere_y[has_NA_sphere] <- 0
    plan_table$Sphere_z[has_NA_sphere] <- 0
    
    plan_table$OrigCoord_x[has_NA_sphere] <- 0
    plan_table$OrigCoord_y[has_NA_sphere] <- 0
    plan_table$OrigCoord_z[has_NA_sphere] <- 0
    
    plan_table$DistanceShifted[has_NA_sphere] <- 0
    plan_table$DistanceToPial[has_NA_sphere] <- 0
  }
  
  # "Radius", 
  default_radius <- local({
    is_grid <- grepl("^(G$|Grid)", plan_table$LabelPrefix)
    is_mini <- grepl("mini$", plan_table$LabelPrefix)
    r <- rep(1, nrow(plan_table))
    r[is_grid] <- 2
    r[is_mini] <- 0.5
    r
  })
  
  plan_table$Radius %?<-% default_radius
  has_NA <- is.na(plan_table$Radius) | !is.numeric(plan_table$Radius)
  if(any(has_NA)) {
    plan_table$Radius[has_NA] <- default_radius[has_NA]
  }
  
  
  # "SurfaceElectrode", 
  is_surface <- plan_table$LocationType %in% c("ECoG")
  plan_table$SurfaceElectrode %?<-% is_surface
  has_NA <- is.na(plan_table$SurfaceElectrode)
  if( any(has_NA) ) {
    plan_table$SurfaceElectrode[has_NA] <- is_surface[has_NA]
  }
  
  plan_table$SurfaceType %?<-% "pial"
  has_NA <- is.na(plan_table$SurfaceType)
  if( any(has_NA) ) {
    plan_table$SurfaceType[has_NA] <- "pial"
  }
  
  # "FSIndex", "FSLabel", 
  # "FSLabel_aparc_a2009s_aseg", "FSLabel_aparc_aseg",
  # "FSLabel_aparc_DKTatlas_aseg", "FSLabel_aseg",
  plan_table$FSIndex %?<-% 0
  plan_table$FSLabel %?<-% "Unknown"
  has_NA <- is.na(plan_table$FSIndex) | is.na(plan_table$FSLabel)
  if( any(has_NA) ) {
    plan_table$FSIndex[has_NA] <- 0L
    plan_table$FSLabel[has_NA] <- "Unknown"
  }
  
  etypes <- subject$preprocess_settings$electrode_types
  if(!length(etypes)) {
    etypes <- ifelse(is.na(plan_table$LocationType) | plan_table$LocationType %in% c("EEG", "Others"), "Unknown", "LFP")
  }
  plan_table$SignalType <- etypes
  
  plan_list <- split(plan_table, plan_table$LabelPrefix)
  
  # save to "electrodes_unsaved.csv"
  raveio::dir_create2(subject$meta_path)
  utils::write.csv(
    plan_table,
    file = file.path(subject$meta_path, "electrodes_unsaved.csv"),
    row.names = FALSE
  )
}
```

```{rave check_load_pial_envelop, language = "R", export = "pial_envelope", cue = "always"}

pial_envelope <- 0
tryCatch({
  fs_path <- subject$freesurfer_path
  if(!is.na(fs_path) && length(fs_path) == 1 && file.exists(fs_path)) {
    
    # check if pial-outer-smoothed exist
    lh_envelope_path <- file.path(fs_path, "surf", "lh.pial-outer-smoothed")
    rh_envelope_path <- file.path(fs_path, "surf", "rh.pial-outer-smoothed")
    
    lh_pial_path <- file.path(fs_path, "surf", "lh.pial.T1")
    rh_pial_path <- file.path(fs_path, "surf", "rh.pial.T1")
    
    if(!file.exists(lh_envelope_path) || !file.exists(rh_envelope_path)) {
      
      if(!file.exists(lh_pial_path)) { lh_pial_path <- file.path(fs_path, "surf", "lh.pial") }
      if(!file.exists(rh_pial_path)) { rh_pial_path <- file.path(fs_path, "surf", "rh.pial") }
      
      if( file.exists(lh_pial_path) ) {
        threeBrain::generate_smooth_envelope(
          surface_path = lh_pial_path,
          save_as = lh_envelope_path, inflate = 3, 
          verbose = TRUE, save_format = "bin")
        pial_envelope <- 1
      }
      if( file.exists(rh_pial_path) ) {
        threeBrain::generate_smooth_envelope(
          surface_path = rh_pial_path,
          save_as = rh_envelope_path, inflate = 3, 
          verbose = TRUE, save_format = "bin")
        pial_envelope <- pial_envelope + 1
      }
      
    } else {
      pial_envelope <- 2
    }
    
  }
}, error = function(e) { warning(e) })

```

```{rave load_brain_and_generate_pial_envelope, language = "R", export = "brain", cue = "always"}
force(pial_envelope)
brain <- tryCatch({
  threeBrain::threeBrain(path = subject$freesurfer_path, 
                         subject_code = subject$subject_code)
}, error = function(e) {
  threeBrain::freesurfer_brain2(
    fs_subject_folder = subject$freesurfer_path,
    subject_name = subject$subject_code, 
    use_141 = FALSE
  )
})
geom_def_path <- file.path(subject$meta_path, "geometry_unsaved.json")
geom_defs <- list()
if(file.exists(geom_def_path)) {
  tryCatch({
    geom_defs <- raveio::load_json(geom_def_path)
  }, error = function(e) {})
}

if(!is.null(brain)) {
  # Add electrode geometry prototypes
  lapply(plan_list, function(sub) {
    if(is.data.frame(sub) && nrow(sub)) {
      proto <- brain$electrodes$add_geometry(
        label_prefix = sub$LabelPrefix[[1]], 
        prototype_name = sub$Prototype[[1]]
      )
      if(!is.null(proto)) {
        unsaved_def <- geom_defs[[ proto$name ]]
        if(length(unsaved_def) == 1 && is.character(unsaved_def)) {
          proto$from_json( unsaved_def )
        }
        # set channel mapping
        proto$set_contact_channels(sub$Electrode, sub$ContactOrder)
      }
    }
  })
}
brain
```


```{rave Loading_brain_and_CT_if_exists, language = "R", export = "localize_data", cue = "always"}
force(subject)

resolve_path <- function(path) {
  if(length(path) != 1) {
    stop("Cannot resolve path: ", paste(format(path), collapse = "\n"))
  }
  if(startsWith(path, "{")) {
    s <- strsplit(path, "/|\\\\")[[1]]
    s[[1]] <- raveio::glue(s[[1]])
    s <- do.call(file.path, as.list(s))
    path <- normalizePath(s, mustWork = TRUE)
  } else {
    path <- normalizePath(path, mustWork = TRUE)
  }
  path
}

has_ct <- FALSE
ct_path <- character(0L)
mri_path <- character(0L)
mri_data <- NULL
transform_matrix <- NULL
if(length(path_ct)) {
  ct_path <- resolve_path(path_ct)
  has_ct <- TRUE
  subject$set_default("path_ct", path_ct, namespace = "electrode_localization")
  ct_header <- threeBrain:::read_nii2(ct_path, head_only = TRUE)
  
  # check if method is MRI
  transform_space <- tolower(transform_space)
  if(transform_space %in% c("fsl")) {
    mri_path <- resolve_path(path_mri)
    mri_data <- threeBrain:::read_nii2(mri_path, head_only = TRUE)
  }
  subject$set_default("path_mri", path_mri, namespace = "electrode_localization")
  
  if(transform_space %in% c("fsl", "ijk2ras")) {  
    transform_matrix <- as.matrix(read.table(resolve_path(path_transform)))
    dimnames(transform_matrix) <- NULL
    
    if(length(transform_matrix) != 16L || !is.numeric(transform_matrix)) {
      stop("Invalid transform matrix. Must be a 4x4 matrix.")
    }
    subject$set_default("path_transform", path_transform, namespace = "electrode_localization")
  } else {
    transform_space <- "resampled"
  }
  
} else {
  subject$set_default("path_ct", NULL, namespace = "electrode_localization")
  ct_header <- NULL
  transform_space <- "no_ct"
}

subject$set_default("transform_space", transform_space, namespace = "electrode_localization")

localize_data <- list(
  transform_space = transform_space,
  ct_header = ct_header,
  ct_path = ct_path,
  mri_path = mri_path,
  mri_data = mri_data,
  transform_matrix = transform_matrix
)
```

```{rave generate_indicator, language = "R", export = "ct_exists", cue = "always"}
ct_exists <- isTRUE(!is.null(localize_data$ct_header) && is.list(localize_data$ct_header))
```

```{rave generate_localization_viewer, language = "R", export = "viewer", cue = "always"}
force(ct_exists)
viewer <- brain$localize(
  ct_path = localize_data$ct_path, 
  transform_space = localize_data$transform_space,
  transform_matrix = localize_data$transform_matrix,
  mri_path = localize_data$mri_path
)
```


```{rave merge_localization_list, export = "localization_result_initial"}
localization_result_initial <- NULL

prototype_list <- dipsaus::fastmap2()

re <- lapply(localization_list, function(item) {
  
  if(!is.data.frame(item) || !nrow(item)) {
    return()
  }
  prototype_def <- attr(item, "prototype")
  prototype <- NULL
  prototype_name <- ""
  label_prefix <- item$LabelPrefix[[1]]
  if(!is.null(prototype_def)) {
    if(!length(item$Prototype) && length(prototype_def$type)) {
      # when saved in pipeline, the prototype name is prototype's name
      # itself, without postfix `_labelprefix`
      item$Prototype <- prototype_def$type
    }
    prototype <- brain$electrodes$add_geometry(
      label_prefix = label_prefix, 
      prototype_name = item$Prototype[[1]]
    )
    prototype_name <- prototype$name
    prototype_def$name <- prototype$name
    prototype$from_list(prototype_def)
    if(length(item$ContactOrder)) {
      prototype$set_contact_channels(item$Electrode, item$ContactOrder)
    }
    prototype_list[[ prototype_name ]] <- prototype$as_json(flattern = TRUE)
  } else {
    item$Prototype %?<-% ""
  }
  
  item$FSIndex %?<-% 0
  item$FSLabel %?<-% "Unknown"
  item$FSLabel_aparc_a2009s_aseg %?<-% "Unknown"
  item$FSLabel_aparc_aseg %?<-% "Unknown"
  item$FSLabel_aparc_DKTatlas_aseg %?<-% "Unknown"
  item$FSLabel_aseg %?<-% "Unknown"
  item$Radius %?<-% 1
  item$Sphere_x %?<-% 0
  item$Sphere_y %?<-% 0
  item$Sphere_z %?<-% 0
  item$DistanceShifted %?<-% NA
  item$DistanceToPial %?<-% NA
  item$SurfaceElectrode %?<-% FALSE
  item$Interpolation %?<-% "default"
  
  # check if the geometry exists
  # proto_dir <- file.path(brain$base_path, "RAVE", "geometry")
  if(!is.null(prototype)) {
    # In the final step we save to subject folder
    # prototype$as_json( file.path(proto_dir, sprintf("%s.json", prototype$name)) )
    # get contact center positions
    
    contact_tkrras <- t(prototype$get_contact_positions(
      channels = item$Electrode, apply_transform = TRUE))
    # contact_vox <- solve(brain$Torig) %*% rbind(contact_tkrras, 1)
    # contact_t1ras <- brain$Norig %*% contact_vox
    # contact_mni305 <- brain$xfm %*% contact_t1ras
    # contact_mni152 <- raveio::MNI305_to_MNI152 %*% contact_mni305
    
    contact_tkrras[is.na(contact_tkrras)] <- 0
    # contact_vox[is.na(contact_vox)] <- 0
    # contact_t1ras[is.na(contact_t1ras)] <- 0
    # contact_mni305[is.na(contact_mni305)] <- 0
    # contact_mni152[is.na(contact_mni152)] <- 0
    
    item$Coord_x <- contact_tkrras[1,]
    item$Coord_y <- contact_tkrras[2,]
    item$Coord_z <- contact_tkrras[3,]
    
    item$OrigCoord_x <- contact_tkrras[1,]
    item$OrigCoord_y <- contact_tkrras[2,]
    item$OrigCoord_z <- contact_tkrras[3,]
    
    # item$MNI305_x <- contact_mni305[1, ]
    # item$MNI305_y <- contact_mni305[2, ]
    # item$MNI305_z <- contact_mni305[3, ]
    
  }
  
  item$OrigCoord_x %?<-% item$Coord_x
  item$OrigCoord_y %?<-% item$Coord_y
  item$OrigCoord_z %?<-% item$Coord_z
  
  
  tbl <- data.frame(
    Electrode = item$Electrode,
    Coord_x = item$Coord_x, Coord_y = item$Coord_y, Coord_z = item$Coord_z,
    Label = item$Label, LabelPrefix = item$LabelPrefix,
    Prototype = item$Prototype,
    ContactOrder = item$ContactOrder,
    Dimension = item$Dimension, 
    Interpolation = item$Interpolation,
    LocationType = item$LocationType, Radius = item$Radius, 
    Hemisphere = item$Hemisphere,
    MNI305_x = item$MNI305_x, MNI305_y = item$MNI305_y, MNI305_z = item$MNI305_z,
    FSIndex = item$FSIndex, 
    FSLabel = item$FSLabel,
    FSLabel_aparc_a2009s_aseg = item$FSLabel_aparc_a2009s_aseg,
    FSLabel_aparc_aseg = item$FSLabel_aparc_aseg,
    FSLabel_aparc_DKTatlas_aseg = item$FSLabel_aparc_DKTatlas_aseg,
    FSLabel_aseg = item$FSLabel_aseg,
    
    OrigCoord_x = item$OrigCoord_x, 
    OrigCoord_y = item$OrigCoord_y, 
    OrigCoord_z = item$OrigCoord_z,
    
    SurfaceElectrode = item$SurfaceElectrode, 
    DistanceShifted = item$DistanceShifted, 
    DistanceToPial = item$DistanceToPial,
    SurfaceType = "pial",
    VertexNumber = -1,
    
    Sphere_x = item$Sphere_x, 
    Sphere_y = item$Sphere_y, 
    Sphere_z = item$Sphere_z
  )
  if(!nrow(tbl)) { return(NULL) }
  tbl
})
re <- do.call("rbind", drop_nulls(re))

if(length(re) && nrow(re)) {
  rownames(re) <- NULL
  re <- re[order(re$Electrode), ]
  
  # Calculate T1, MNI152
  empty_sel <- (re$Coord_x)^2 + (re$Coord_y)^2 + (re$Coord_z)^2
  empty_sel <- is.na(empty_sel) | empty_sel == 0
  tkrRAS <- rbind(re$Coord_x, re$Coord_y, re$Coord_z, 1)
  mr_voxel <- solve(brain$Torig) %*% tkrRAS
  t1 <- brain$Norig %*% mr_voxel
  mni305 <- brain$xfm %*% brain$Norig %*% solve(brain$Torig) %*% tkrRAS
  mni152 <- raveio:::MNI305_to_MNI152 %*% mni305
  
  mni305[, empty_sel] <- 0
  mni152[, empty_sel] <- 0
  t1[, empty_sel] <- 0
  mr_voxel[, empty_sel] <- 0
  
  re$MNI305_x <- mni305[1, ]
  re$MNI305_y <- mni305[2, ]
  re$MNI305_z <- mni305[3, ]
  re$T1R <- t1[1, ]
  re$T1A <- t1[2, ]
  re$T1S <- t1[3, ]
  re$MNI152_x <- mni152[1, ]
  re$MNI152_y <- mni152[2, ]
  re$MNI152_z <- mni152[3, ]
  re$MRVoxel_I <- round(mr_voxel[1, ])
  re$MRVoxel_J <- round(mr_voxel[2, ])
  re$MRVoxel_K <- round(mr_voxel[3, ])
  
  # save to electrodes_unsaved.csv
  raveio::dir_create2(subject$meta_path)
  utils::write.csv(
    x = re,
    file.path(subject$meta_path, "electrodes_unsaved.csv"),
    row.names = FALSE
  )
  
  # save to "geometry_unsaved.json"
  prototype_list <- as.list(prototype_list)
  raveio::save_json(
    x = prototype_list,
    con = file.path(subject$meta_path, "geometry_unsaved.json"),
    serialize = TRUE
  )
  
  localization_result_initial <- list(
    electrode_table = re,
    prototype_list = prototype_list
  )
}
```

Make sure you run target `localization_result_initial` first

```{rave get_finalized_table, export = "localization_result_final", cue="always"}
localization_result_final <- list()
src <- file.path(subject$meta_path, "electrodes_unsaved.csv")
prot <- file.path(subject$meta_path, "geometry_unsaved.json")
if(file.exists(prot)) {
  proto_defs <- raveio::load_json(prot)
  localization_result_final$prototype_definitions <- proto_defs
  
  if(length(proto_defs)) {
    geometry_dir <- raveio::dir_create2(file.path(subject$freesurfer_path, "RAVE", "geometry"))
    # save to brain
    for(nm in names(proto_defs)) {
      target <- file.path(geometry_dir, sprintf("%s.json", nm))
      writeLines(proto_defs[[nm]], target)
    }
  }
  
}
if(file.exists(src)) {
  localization_result_final$electrode_table <- utils::read.csv(src)
  
  try({
    if( isTRUE(localize_data$transform_space %in% c('fsl', 'ijk2ras', 'resampled')) ) {
      electrode_table <- localization_result_final$electrode_table
      scan_ras <- rbind(electrode_table$T1R, electrode_table$T1A, electrode_table$T1S, 1)
      
      switch(
        localize_data$transform_space,
        'fsl' = {
          ct_ijk2fsl <- localize_data$ct_header$get_IJK_to_FSL()
          ct_ijk2ras <- localize_data$ct_header$get_IJK_to_RAS()$matrix
          mr_ijk2fsl <- localize_data$mri_data$get_IJK_to_FSL()
          mr_ijk2ras <- localize_data$mri_data$get_IJK_to_RAS()$matrix
          
          # CT vox -> CT fsl -> MR fsl -> MR vox -> MR ras
          ct_ijk_to_mr_ras <- mr_ijk2ras %*% solve(mr_ijk2fsl) %*% localize_data$transform_matrix %*% ct_ijk2fsl
          ct_ijk <- solve(ct_ijk_to_mr_ras) %*% scan_ras
          ct_ras <- ct_ijk2ras %*% ct_ijk
        },
        'ijk2ras' = {
          ct_ijk2ras <- localize_data$ct_header$get_IJK_to_RAS()$matrix
          ct_ijk2mr_ras <- localize_data$transform_matrix
          ct_ijk <- solve(ct_ijk2mr_ras) %*% scan_ras
          ct_ras <- ct_ijk2ras %*% ct_ijk
        },
        {
          ct_ijk2ras <- localize_data$ct_header$get_IJK_to_RAS()$matrix
          ct_ijk <- solve(ct_ijk2ras) %*% scan_ras
          ct_ras <- scan_ras
        }
      )
      
      localization_result_final$ct_table <- data.frame(
        Electrode = electrode_table$Electrode,
        CTVoxel_I = ct_ijk[1, ],
        CTVoxel_J = ct_ijk[2, ],
        CTVoxel_K = ct_ijk[3, ],
        CT_R = ct_ras[1, ],
        CT_A = ct_ras[2, ],
        CT_S = ct_ras[3, ]
      )
    }
  })
}
```



## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-electrode_localization.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-electrode_localization.R")
```


Once the pipeline script `make-electrode_localization.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
Sys.setenv("RAVE_PIPELINE" = normalizePath("."))
raveio::pipeline_visualize()
```







