---
title: "Anatomical Slices with Electrodes"
description: | 
  <small><i>
    An automated report generated by 
    <a target="_blank" href="https://doi.org/10.1523/ENEURO.0328-23.2023">YAEL</a>
    via 
    <a target="_blank" href="https://rave.wiki">RAVE</a> 
    on `r strftime(Sys.Date(), '%b %d, %Y')`
  </i></small>
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: flatly
    code_folding: hide
    self_contained: true
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  eval = TRUE,
  echo = TRUE,
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)

# For debug, set current environment
# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
```



*Click on the `Show` button to reveal preparation scripts.*

```{r initial_setup}
#| results: 'hide'
# This code block sets up the engine environment
# Please do not remove me
pipeline <- ravepipeline::pipeline_from_path(".")
subject_code <- pipeline$get_settings("subject_code")
project_name <- pipeline$get_settings("project_name")
subject <- ravecore::RAVESubject$new(project_name = project_name,
                                     subject_code = subject_code,
                                     strict = FALSE)
brain <- ravecore::rave_brain(subject, include_electrodes = TRUE)
electrode_table <- subject$get_electrode_table()
brain$set_electrode_values(electrode_table)

cnames <- c(
  "Electrode", "Label", "T1R", "T1A", "T1S", "FSIndex", "FSLabel", 
  "MNI152_x", "MNI152_y", "MNI152_z", "Coord_x", "Coord_y", "Coord_z", 
  "FSLabel_aparc_a2009s_aseg", "FSLabel_aparc_aseg", 
  "FSLabel_aparc_DKTatlas_aseg", "FSLabel_aseg", "LabelPrefix"
)
cnames <- cnames[cnames %in% names(electrode_table)]
electrode_table <- as.data.frame(electrode_table)[, cnames]

# rounding digits
cnames2 <- c(
  "T1R", "T1A", "T1S", 
  "MNI152_x", "MNI152_y", "MNI152_z", 
  "Coord_x", "Coord_y", "Coord_z"
)
cnames2 <- cnames2[cnames2 %in% cnames]
if(length(cnames2)) {
  for(nm in cnames2) {
    electrode_table[[nm]] <- round(electrode_table[[nm]], digits = 1)
  }
}

# Obtain the original MRI, avoid using FreeSurfer's default
mri_paths <- c(
  file.path(subject$imaging_path, "fs", "mri", "rave_slices"),
  file.path(subject$imaging_path, "fs", "mri", "orig", "001"),
  file.path(subject$imaging_path, "coregistration", "MRI_reference")
)
mri_paths <- as.vector(rbind(
  sprintf("%s.nii.gz", mri_paths),
  sprintf("%s.nii", mri_paths),
  sprintf("%s.mgz", mri_paths)
))

mri_paths <- mri_paths[file.exists(mri_paths)]
# if(length(mri_paths)) {
#   brain$volumes$T1$object$group$group_data$volume_data$absolute_path <- mri_paths[[1]]
# }
volume <- threeBrain::read_volume(
  brain$volumes$T1$object$group$group_data$volume_data$absolute_path)
```

::: {.hidden}

```{r custom_toc_block, results='asis', echo=FALSE}
htmltools::div(
  id = "custom-toc",
  htmltools::tags$ul(
    htmltools::tagList(lapply(seq_len(nrow(electrode_table)), function(ii) {
      row <- electrode_table[ii, ]
      htmltools::tags$li(
        htmltools::a(
          href = sprintf('#electrode-slice-%d', row$Electrode),
          sprintf("Electrode %d - %s", row$Electrode, row$Label)
        )
      )
    }))
  )
)
```

:::

# Subject ID: ``r subject$subject_id``


## Electrode table

```{r table_print, layout="l-screen-insert-right"}
rmarkdown::paged_table(
  electrode_table,
  options = list(
    rows.print = 20,
    rownames.print = FALSE
  )
)
```

## Anatomical slices

```{r slice_view, results='asis', out.width="100%", fig.width=12, fig.height=4.5, layout="l-screen-insert-right"}
dummy_output <- lapply(seq_len(nrow(electrode_table)), function(ii) {
  row <- electrode_table[ii, ]
  ras <- c(row$T1R, row$T1A, row$T1S)
  
  tmp <- sum(c(row$Coord_x, row$Coord_y, row$Coord_z, 0)^2)
  is_hidden <- isTRUE(is.na(tmp) || tmp == 0)
  
  if(is_hidden) {
    cat(sprintf("\n\n### Electrode %d - %s (hidden) {#electrode-slice-%d}\n\n", 
              row$Electrode, row$Label, row$Electrode))
    return()
  }
  
  cat(sprintf("\n\n### Electrode %d - %s {#electrode-slice-%d}\n\n", 
              row$Electrode, row$Label, row$Electrode))
  nms <- names(row)
  nms <- nms[startsWith(nms, "FS")]
  if(length(nms)) {
    summary <- htmltools::tags$ul(
      class = "ul-compact",
      lapply(nms, function(nm) {
        htmltools::tags$li(sprintf("`%s`: %s\n", nm, row[[nm]]))
      })
    )
    print(summary)
  }
  cat("\n")
  
  brain$plot_electrodes_on_slices(
    row$Electrode, elec_table = row,
    title_position = "top", verbose = FALSE,
    zoom = 3, volume = volume, adjust_brightness = FALSE)
})
```


<!--
brain$plot(controllers = list("Display Data" = "LabelPrefix"), 
           side_display = FALSE, control_display = FALSE,
           background = "#1a1a1a")
-->



## Citations

The module depends on the following work. Please cite our YAEL paper for electrode localization pipelines and RAVE paper for 3D visualization.

```{r, results='asis', echo = FALSE}
print(pipeline$description$Citations, style = "html")
```


<script>
document.addEventListener("DOMContentLoaded", function () {
  let count = 0;
  const insert_custom_toc = () => {
    const custom_toc = document.getElementById("custom-toc");
    const toc = document.querySelector("d-article.d-article-with-toc #TOC");
    if(!custom_toc) { return; }
    if(toc) {
      toc.appendChild(custom_toc);
      return;
    }
    if(count > 10) { return; }
    count++;
    console.log(toc);
    setTimeout(insert_custom_toc, 500);
  };
  insert_custom_toc();
});
</script>
